### 2017-10-05 article.tex
Stub

\documentclass{article}

% \includegraphics
\usepackage{ifluatex}
\ifluatex
  \usepackage{pdftexcmds}
  \makeatletter
  \let\pdfstrcmp\pdf@strcmp
  \let\pdffilemoddate\pdf@filemoddate
  \makeatother
\fi
\usepackage{svg}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{tkz-graph}
\usepackage{pgf}
\usetikzlibrary{arrows,automata}

\usepackage{scalerel}
\usepackage{stackengine,wasysym}

\usepackage{todonotes}

\title{The error when inferring phylogenies with incipient species by a Birth-Death model}
% \subtitle{Should protracted speciation be incorporated in phylogenetic tree construction methods?}

\author{Richel Bilderbeek}

\input{functions.tex}

\begin{document}

\maketitle

\begin{abstract}
  \input{abstract.tex}
\end{abstract}

\input{introduction.tex}

\input{methods.tex}

\input{results.tex}

\input{discussion.tex}

\input{acknowledgements.tex}

\bibliographystyle{plain}
\bibliography{article}

\listoftodos

\end{document}

### 2017-10-05 main.tex
Start of article

\documentclass{bioinfo}
\copyrightyear{2017} \pubyear{2017}

\access{Advance Access Publication Date: Day Month Year}
\appnotes{Manuscript Category}

\begin{document}
\firstpage{1}

\subtitle{Subject Section}

\title[beastscriptr]{beastscriptr: BEAUti for R}
\author[Sample \textit{et~al}.]{Rich\`el J.C. Bilderbeek\,$^{\text{\sfb 1,}*}$, Co-Author\,$^{\text{\sfb 2}}$ and Co-Author\,$^{\text{\sfb 2,}*}$}
\address{$^{\text{\sf 1}}$TR\^ES, Groningen Institute for Evolutionary Life Sciences, Groningen, 9747 AG, The Netherlands and \\
$^{\text{\sf 2}}$Department, Institution, City, Post Code,
Country.}

\corresp{$^\ast$To whom correspondence should be addressed.}

\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

\editor{Associate Editor: XXXXXXX}

\abstract{\textbf{Motivation:} Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text
Text Text Text Text Text.\\
\textbf{Results:} Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text\\
\textbf{Availability:} Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text Text  Text\\
\textbf{Contact:} \href{name@bio.com}{name@bio.com}\\
\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}
online.}

\maketitle

\section{Introduction}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text. Figure~\ref{fig:01}
shows that the above method  Text Text Text Text  Text Text Text
Text Text Text  Text Text.  \citep{Bag01} wants to know about
{\ldots}{\ldots} text follows.
\begin{equation}
\sum \text{\it x}+ \text{\it y} =\text{\it Z}\label{eq:01}\vspace*{-10pt}
\end{equation}

%\enlargethispage{12pt}

\section{Approach}

Equation~(\ref{eq:01}) Text Text Text Text Text Text  Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
.....

\begin{methods}
\section{Methods}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text
text\vspace*{1pt}

\begin{itemize}
\item for bulleted list, use itemize
\item for bulleted list, use itemize
\item for bulleted list, use itemize\vspace*{1pt}
\end{itemize}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text Text Text Text Text Text Text Text Text Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text\vadjust{\newpage}.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text Text Text Text Text Text Text Text Text Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\subsection{This is subheading}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text
text. Text Text Text Text Text Text  Text Text Text Text Text Text
Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\subsubsection{This is subsubheading}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text\break
text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text
textText Text Text Text Text Text  Text Text Text Text Text Text
Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\enlargethispage{6pt}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\begin{table}[!t]
\processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}\toprule head1 &
head2 & head3 & head4\\\midrule
row1 & row1 & row1 & row1\\
row2 & row2 & row2 & row2\\
row3 & row3 & row3 & row3\\
row4 & row4 & row4 & row4\\\botrule
\end{tabular}}{This is a footnote}
\end{table}

\end{methods}

\begin{figure}[!tpb]%figure1
\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{235pt} \vbox to 100pt{\vfill\hbox to
235pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
\end{minipage}}
%\centerline{\includegraphics{fig01.eps}}
\caption{Caption, caption.}\label{fig:01}
\end{figure}

%\begin{figure}[!tpb]%figure2
%%\centerline{\includegraphics{fig02.eps}}
%\caption{Caption, caption.}\label{fig:02}
%\end{figure}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\subsection{Test1}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\section{Discussion}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text.

Table~\ref{Tab:01} shows that Text Text Text Text Text  Text Text
Text Text Text Text. Figure~2\vphantom{\ref{fig:02}} shows that
the above method Text Text. Text Text Text  Text Text Text Text
Text Text. Figure~2\vphantom{\ref{fig:02}} shows that the above
method Text Text. Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     please remove the " % " symbol from \centerline{\includegraphics{fig01.eps}}
%     as it may ignore the figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

(Table~\ref{Tab:01}) Text Text Text Text Text Text  Text Text Text
Text Text Text Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\begin{enumerate}
\item this is item, use enumerate
\item this is item, use enumerate
\item this is item, use enumerate
\end{enumerate}

Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows\vadjust{\pagebreak} that the
above method  Text Text Text Text Text Text Text Text Text Text
Text Text.  \citealp{Boffelli03} might want to know about text
text text text Text Text Text Text Text Text  Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text\break Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text\vspace*{-10pt}

\section*{Acknowledgements}

Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text
text text text\vspace*{-12pt}

\section*{Funding}

This work has been supported by the... Text Text  Text Text.\vspace*{-12pt}

%\bibliographystyle{natbib}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{bioinformatics}
%
%\bibliographystyle{plain}
%
%\bibliography{Document}

\begin{thebibliography}{}

\bibitem[Bofelli {\it et~al}., 2000]{Boffelli03}
Bofelli,F., Name2, Name3 (2003) Article title, {\it Journal Name}, {\bf 199}, 133-154.

\bibitem[Bag {\it et~al}., 2001]{Bag01}
Bag,M., Name2, Name3 (2001) Article title, {\it Journal Name}, {\bf 99}, 33-54.

\bibitem[Yoo \textit{et~al}., 2003]{Yoo03}
Yoo,M.S. \textit{et~al}. (2003) Oxidative stress regulated genes
in nigral dopaminergic neurnol cell: correlation with the known
pathology in Parkinson's disease. \textit{Brain Res. Mol. Brain
Res.}, \textbf{110}(Suppl. 1), 76--84.

\bibitem[Lehmann, 1986]{Leh86}
Lehmann,E.L. (1986) Chapter title. \textit{Book Title}. Vol.~1, 2nd edn. Springer-Verlag, New York.

\bibitem[Crenshaw and Jones, 2003]{Cre03}
Crenshaw, B.,III, and Jones, W.B.,Jr (2003) The future of clinical
cancer management: one tumor, one chip. \textit{Bioinformatics},
doi:10.1093/bioinformatics/btn000.

\bibitem[Auhtor \textit{et~al}. (2000)]{Aut00}
Auhtor,A.B. \textit{et~al}. (2000) Chapter title. In Smith, A.C.
(ed.), \textit{Book Title}, 2nd edn. Publisher, Location, Vol. 1, pp.
???--???.

\bibitem[Bardet, 1920]{Bar20}
Bardet, G. (1920) Sur un syndrome d'obesite infantile avec
polydactylie et retinite pigmentaire (contribution a l'etude des
formes cliniques de l'obesite hypophysaire). PhD Thesis, name of
institution, Paris, France.

\end{thebibliography}
\end{document}

### 2017-10-05 main.tex
First version abstract

@@
 
-\subtitle{Subject Section}
+\subtitle{APPLICATIONS NOTES}
 
@@
 
-\abstract{\textbf{Motivation:} Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text
-Text Text Text Text Text.\\
-\textbf{Results:} Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text
-Text Text Text Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text\\
-\textbf{Availability:} Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text
-Text Text Text Text Text Text Text Text Text Text Text Text Text Text  Text\\
+\abstract{\textbf{Motivation:} BEAST2 is a popular Bayesian phylogenetics tool.
+The program BEAUti allows for a user-friendly way to create the
+input files that BEAST2 needs. This is convenient to get started, yet
+does not facilitate the scripted use of BEAST2. 
+beastscriptr is an R package that can create BEAST2 input files from an R
+function call.\\
+\textbf{Results:} beastscriptr has only parts of the functionality of BEAUti, yet
+can be extended easily. beastcriptr, on the other hand, does allow for specifying
+to use phylogenies of fixed crown age.\\
+\textbf{Availability:} The package is free and is available from the official R package archive at 
+http://cran.r-project.org/src/contrib/PACKAGES.html\#beastscriptr. 
+beastscriptr is licensed under the GNU General Public License.
 \textbf{Contact:} \href{name@bio.com}{name@bio.com}\\
@@
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text. Figure~\ref{fig:01}
-shows that the above method  Text Text Text Text  Text Text Text
-Text Text Text  Text Text.  \citep{Bag01} wants to know about
-{\ldots}{\ldots} text follows.
-\begin{equation}
-\sum \text{\it x}+ \text{\it y} =\text{\it Z}\label{eq:01}\vspace*{-10pt}
-\end{equation}
-
-%\enlargethispage{12pt}
+My intro
 
@@
 
-Equation~(\ref{eq:01}) Text Text Text Text Text Text  Text Text
-Text Text Text Text Text Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-.....
+My approach
 

### 2017-10-05 main.tex
First sketch

@@
 
-My intro
+BEAST2 \cite{bouckaert2014beast} is a popular Bayesian phylogenetics tool.
+The program BEAUti \cite{drummond2012bayesian} allows for a user-friendly 
+way to create the
+input files that BEAST2 needs. This is convenient to get started, yet
+does not facilitate the scripted use of BEAST2. 
+beastscriptr is an R package that can create BEAST2 input files from an R
+function call.
 
@@
 
-My approach
+The goal of the R package beastscriptr was to mimic the functionality of BEAUti.
+Where BEAUti creates a BEAST2 XML input file by a graphical user interface,
+beastscriptr would do the same from one R function call.
 
@@
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text
-text\vspace*{1pt}
+By creating BEAST2 input files in BEAUti, the files beastscriptr should
+create were determined. BEAUti already has many options, already
+before taking all possible plug-ins into account. beastscriptr 
+gradually grew in mimicking the basic functionality of BEAUti.
 
-\begin{itemize}
-\item for bulleted list, use itemize
-\item for bulleted list, use itemize
-\item for bulleted list, use itemize\vspace*{1pt}
-\end{itemize}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
-Text Text Text Text Text Text Text Text Text Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text\vadjust{\newpage}.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
-Text Text Text Text Text Text Text Text Text Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-
-\subsection{This is subheading}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text
-text. Text Text Text Text Text Text  Text Text Text Text Text Text
-Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-
-\subsubsection{This is subsubheading}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text\break
-text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text
-textText Text Text Text Text Text  Text Text Text Text Text Text
-Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-
-\enlargethispage{6pt}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-\begin{table}[!t]
-\processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}\toprule head1 &
-head2 & head3 & head4\\\midrule
-row1 & row1 & row1 & row1\\
-row2 & row2 & row2 & row2\\
-row3 & row3 & row3 & row3\\
-row4 & row4 & row4 & row4\\\botrule
-\end{tabular}}{This is a footnote}
-\end{table}
+beastscriptr has a novel functionality not built into BEAUti yet:
+it allows for using phylogenies of a fixed crown age.
 
@@
 
-\begin{figure}[!tpb]%figure1
-\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{235pt} \vbox to 100pt{\vfill\hbox to
-235pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
-\end{minipage}}
-%\centerline{\includegraphics{fig01.eps}}
-\caption{Caption, caption.}\label{fig:01}
-\end{figure}
-
-%\begin{figure}[!tpb]%figure2
-%%\centerline{\includegraphics{fig02.eps}}
-%\caption{Caption, caption.}\label{fig:02}
-%\end{figure}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-\subsection{Test1}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text.
-
-Table~\ref{Tab:01} shows that Text Text Text Text Text  Text Text
-Text Text Text Text. Figure~2\vphantom{\ref{fig:02}} shows that
-the above method Text Text. Text Text Text  Text Text Text Text
-Text Text. Figure~2\vphantom{\ref{fig:02}} shows that the above
-method Text Text. Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
-Text.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%     please remove the " % " symbol from \centerline{\includegraphics{fig01.eps}}
-%     as it may ignore the figures.
-%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+beastscriptr does not support the full functionality of BEAUti. Considering
+the size, age and number of plugins, this would be close to impossible.
+To compensate for this, an extensible software architecture is used.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-(Table~\ref{Tab:01}) Text Text Text Text Text Text  Text Text Text
-Text Text Text Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
+beastscriptr allow for using BEAST2 from a scripted input file.
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgements}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{enumerate}
-\item this is item, use enumerate
-\item this is item, use enumerate
-\item this is item, use enumerate
-\end{enumerate}
+We would like to thank the Center for Information Technology of the University of Groningen for their support
+and for providing access to the Peregrine high performance computing cluster.
 
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows\vadjust{\pagebreak} that the
-above method  Text Text Text Text Text Text Text Text Text Text
-Text Text.  \citealp{Boffelli03} might want to know about text
-text text text Text Text Text Text Text Text  Text Text Text Text
-Text Text Text Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text\break Text.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Funding}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text\vspace*{-10pt}
+This work has been supported by the VICI of Rampal S. Etienne.
 
-\section*{Acknowledgements}
-
-Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text
-text text text\vspace*{-12pt}
-
-\section*{Funding}
-
-This work has been supported by the... Text Text  Text Text.\vspace*{-12pt}
-
-%\bibliographystyle{natbib}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliographystyle{natbib}
 %\bibliographystyle{achemnat}
@@
 %
-%\bibliographystyle{plain}
+\bibliographystyle{plain}
 %
-%\bibliography{Document}
+\bibliography{document}
 
@@
 
-\bibitem[Bofelli {\it et~al}., 2000]{Boffelli03}
-Bofelli,F., Name2, Name3 (2003) Article title, {\it Journal Name}, {\bf 199}, 133-154.
+\end{thebibliography}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\bibitem[Bag {\it et~al}., 2001]{Bag01}
-Bag,M., Name2, Name3 (2001) Article title, {\it Journal Name}, {\bf 99}, 33-54.
-
-\bibitem[Yoo \textit{et~al}., 2003]{Yoo03}
-Yoo,M.S. \textit{et~al}. (2003) Oxidative stress regulated genes
-in nigral dopaminergic neurnol cell: correlation with the known
-pathology in Parkinson's disease. \textit{Brain Res. Mol. Brain
-Res.}, \textbf{110}(Suppl. 1), 76--84.
-
-\bibitem[Lehmann, 1986]{Leh86}
-Lehmann,E.L. (1986) Chapter title. \textit{Book Title}. Vol.~1, 2nd edn. Springer-Verlag, New York.
-
-\bibitem[Crenshaw and Jones, 2003]{Cre03}
-Crenshaw, B.,III, and Jones, W.B.,Jr (2003) The future of clinical
-cancer management: one tumor, one chip. \textit{Bioinformatics},
-doi:10.1093/bioinformatics/btn000.
-
-\bibitem[Auhtor \textit{et~al}. (2000)]{Aut00}
-Auhtor,A.B. \textit{et~al}. (2000) Chapter title. In Smith, A.C.
-(ed.), \textit{Book Title}, 2nd edn. Publisher, Location, Vol. 1, pp.
-???--???.
-
-\bibitem[Bardet, 1920]{Bar20}
-Bardet, G. (1920) Sur un syndrome d'obesite infantile avec
-polydactylie et retinite pigmentaire (contribution a l'etude des
-formes cliniques de l'obesite hypophysaire). PhD Thesis, name of
-institution, Paris, France.
-
-\end{thebibliography}
 \end{document}

### 2017-10-05 main.tex
Discussion

@@
 
+beastscriptr has minimal support for calling BEAST2 from within R and does
+so for testing purposes.
+
+beastscript has minimal support for parsing and interpreting BEAST2 output files,
+for that the RBeast package is recommended.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-beastscriptr allow for using BEAST2 from a scripted input file.
+beastscriptr successfully creates valid BEAST2 input files. Unlike BEAUti,
+beascriptr allows for setting a fixed crown age.
 

### 2017-10-09 prevstyle/main.tex
Change to new style

--- 2017-10-05 main.tex
@@
 beastscriptr is licensed under the GNU General Public License.
-\textbf{Contact:} \href{name@bio.com}{name@bio.com}\\
+\textbf{Contact:} \href{r.j.c.bilderbeek@rug.nl}{r.j.c.bilderbeek@rug.nl}\\
 \textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}
@@
 BEAST2 \cite{bouckaert2014beast} is a popular Bayesian phylogenetics tool.
-The program BEAUti \cite{drummond2012bayesian} allows for a user-friendly 
-way to create the
+BEAST2 is bundled with the program called BEAUti \cite{drummond2012bayesian},
+which  allows for a user-friendly way to create the
 input files that BEAST2 needs. This is convenient to get started, yet
-does not facilitate the scripted use of BEAST2. 
-beastscriptr is an R package that can create BEAST2 input files from an R
-function call.
+does not allow for the scripted use of BEAST2. beastscriptr is an R package 
+that can create BEAST2 input files from an R function call.
 
@@
 
-The goal of the R package beastscriptr was to mimic the functionality of BEAUti.
-Where BEAUti creates a BEAST2 XML input file by a graphical user interface,
-beastscriptr would do the same from one R function call.
+The goal of the R package beastscriptr is to create the 
+same BEAST2 input files that BEAUti creates, but from one R function call 
+instead.
 
@@
 
-By creating BEAST2 input files in BEAUti, the files beastscriptr should
-create were determined. BEAUti already has many options, already
-before taking all possible plug-ins into account. beastscriptr 
-gradually grew in mimicking the basic functionality of BEAUti.
+By creating BEAST2 input files in BEAUti, 
+the desired output of beastscriptr was determined. 
+The functionality of BEAUti is added gradually (and is still growing).
 
@@
 
-This work has been supported by the VICI of Rampal S. Etienne.
+???This work has been supported by the VICI of Rampal S. Etienne.
 

### 2017-10-09 main.tex
Different layout

@@
-\documentclass{bioinfo}
-\copyrightyear{2017} \pubyear{2017}
+\documentclass{article}
 
-\access{Advance Access Publication Date: Day Month Year}
-\appnotes{Manuscript Category}
+\usepackage{listings}
+
+\title{beastscriptr: BEAUti for R}
+\author{Rich\`el J.C. Bilderbeek}
 
 \begin{document}
-\firstpage{1}
 
-\subtitle{APPLICATIONS NOTES}
+\maketitle
 
-\title[beastscriptr]{beastscriptr: BEAUti for R}
-\author[Sample \textit{et~al}.]{Rich\`el J.C. Bilderbeek\,$^{\text{\sfb 1,}*}$, Co-Author\,$^{\text{\sfb 2}}$ and Co-Author\,$^{\text{\sfb 2,}*}$}
-\address{$^{\text{\sf 1}}$TR\^ES, Groningen Institute for Evolutionary Life Sciences, Groningen, 9747 AG, The Netherlands and \\
-$^{\text{\sf 2}}$Department, Institution, City, Post Code,
-Country.}
-
-\corresp{$^\ast$To whom correspondence should be addressed.}
-
-\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}
-
-\editor{Associate Editor: XXXXXXX}
-
-\abstract{\textbf{Motivation:} BEAST2 is a popular Bayesian phylogenetics tool.
+\abstract{
+  \textbf{Motivation:} BEAST2 is a popular Bayesian phylogenetics tool.
   The program BEAUti allows for a user-friendly way to create the
@@
   beastscriptr is licensed under the GNU General Public License.
-\textbf{Contact:} \href{name@bio.com}{name@bio.com}\\
-\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}
-online.}
+  \textbf{Key-words:} computational biology, evolution, phylogeny, BEAST2, R
 
-\maketitle
+}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 BEAST2 \cite{bouckaert2014beast} is a popular Bayesian phylogenetics tool.
-The program BEAUti \cite{drummond2012bayesian} allows for a user-friendly 
-way to create the
+BEAST2 is bundled with the program called BEAUti \cite{drummond2012bayesian},
+which  allows for a user-friendly way to create the
 input files that BEAST2 needs. This is convenient to get started, yet
-does not facilitate the scripted use of BEAST2. 
-beastscriptr is an R package that can create BEAST2 input files from an R
-function call.
+does not allow for the scripted use of BEAST2. beastscriptr is an R package 
+that can create BEAST2 input files from an R function call.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Descriptions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Examples}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{beastscriptr development and other resources}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Citation of beastscriptr}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Scientists using beastscriptr in a published paper should cite this
+article. Users can additionally cite the beastscriptr package 
+directly. Citation information can be obtained by typing:
+
+\begin{lstlisting}[language=R]
+> citation("beastscriptr")
+\end{lstlisting}
+
+from within R.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgements}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We would like to thank the Center for Information Technology of the University of Groningen for their support
+and for providing access to the Peregrine high performance computing cluster.
+
+\appendix
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Approach}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The goal of the R package beastscriptr was to mimic the functionality of BEAUti.
-Where BEAUti creates a BEAST2 XML input file by a graphical user interface,
-beastscriptr would do the same from one R function call.
+The goal of the R package beastscriptr is to create the 
+same BEAST2 input files that BEAUti creates, but from one R function call 
+instead.
 
-\begin{methods}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Methods}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-By creating BEAST2 input files in BEAUti, the files beastscriptr should
-create were determined. BEAUti already has many options, already
-before taking all possible plug-ins into account. beastscriptr 
-gradually grew in mimicking the basic functionality of BEAUti.
+By creating BEAST2 input files in BEAUti, 
+the desired output of beastscriptr was determined. 
+The functionality of BEAUti is added gradually (and is still growing).
 
@@
 it allows for using phylogenies of a fixed crown age.
-
-\end{methods}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgements}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We would like to thank the Center for Information Technology of the University of Groningen for their support
-and for providing access to the Peregrine high performance computing cluster.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Funding}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This work has been supported by the VICI of Rampal S. Etienne.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{natbib}

### 2017-10-09 article.tex
Bibliography works

@@
 
-% \includegraphics
-\usepackage{ifluatex}
-\ifluatex
-  \usepackage{pdftexcmds}
-  \makeatletter
-  \let\pdfstrcmp\pdf@strcmp
-  \let\pdffilemoddate\pdf@filemoddate
-  \makeatother
-\fi
-\usepackage{svg}
-\usepackage{hyperref}
-\usepackage{amsmath}
-\usepackage{tikz}
-\usepackage{tkz-graph}
-\usepackage{pgf}
-\usetikzlibrary{arrows,automata}
-
-\usepackage{scalerel}
-\usepackage{stackengine,wasysym}
-
+\usepackage{listings}
 \usepackage{todonotes}
 
-\title{The error when inferring phylogenies with incipient species by a Birth-Death model}
-% \subtitle{Should protracted speciation be incorporated in phylogenetic tree construction methods?}
-
-\author{Richel Bilderbeek}
-
-\input{functions.tex}
+\title{beastscriptr: BEAUti for R}
+\author{Rich\`el J.C. Bilderbeek}
 
@@
 \begin{abstract}
-  \input{abstract.tex}
+  \textbf{Motivation:} BEAST2 is a popular Bayesian phylogenetics tool.
+  The program BEAUti allows for a user-friendly way to create the
+  input files that BEAST2 needs. This is convenient to get started, yet
+  does not facilitate the scripted use of BEAST2. 
+  beastscriptr is an R package that can create BEAST2 input files from an R
+  function call.\\
+  \textbf{Results:} beastscriptr has only parts of the functionality of BEAUti, yet
+  can be extended easily. beastcriptr, on the other hand, does allow for specifying
+  to use phylogenies of fixed crown age.\\
+  \textbf{Availability:} The package is free and is available from the official R package archive at 
+  http://cran.r-project.org/src/contrib/PACKAGES.html\#beastscriptr. 
+  beastscriptr is licensed under the GNU General Public License.
+  \textbf{Key-words:} computational biology, evolution, phylogeny, BEAST2, R
 \end{abstract}
 
-\input{introduction.tex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\input{methods.tex}
+BEAST2 \cite{bouckaert2014beast} is a popular Bayesian phylogenetics tool.
+BEAST2 is bundled with the program called BEAUti \cite{drummond2012bayesian},
+which  allows for a user-friendly way to create the
+input files that BEAST2 needs. This is convenient to get started, yet
+does not allow for the scripted use of BEAST2. beastscriptr is an R package 
+that can create BEAST2 input files from an R function call.
 
-\input{results.tex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Descriptions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\input{discussion.tex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Examples}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\input{acknowledgements.tex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{beastscriptr development and other resources}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Citation of beastscriptr}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Scientists using beastscriptr in a published paper should cite this
+article. Users can additionally cite the beastscriptr package 
+directly. Citation information can be obtained by typing:
+
+\begin{lstlisting}[language=R]
+> citation("beastscriptr")
+\end{lstlisting}
+
+from within R.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgements}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We would like to thank the Center for Information Technology of the University of Groningen for their support
+and for providing access to the Peregrine high performance computing cluster.
+
+\appendix
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Approach}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The goal of the R package beastscriptr is to create the 
+same BEAST2 input files that BEAUti creates, but from one R function call 
+instead.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Methods}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+By creating BEAST2 input files in BEAUti, 
+the desired output of beastscriptr was determined. 
+The functionality of BEAUti is added gradually (and is still growing).
+
+beastscriptr has a novel functionality not built into BEAUti yet:
+it allows for using phylogenies of a fixed crown age.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+beastscriptr does not support the full functionality of BEAUti. Considering
+the size, age and number of plugins, this would be close to impossible.
+To compensate for this, an extensible software architecture is used.
+
+beastscriptr has minimal support for calling BEAST2 from within R and does
+so for testing purposes.
+
+beastscript has minimal support for parsing and interpreting BEAST2 output files,
+for that the RBeast package is recommended.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+beastscriptr successfully creates valid BEAST2 input files. Unlike BEAUti,
+beascriptr allows for setting a fixed crown age.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{plain}
@@
 
-\listoftodos
+\begin{thebibliography}{}
+
+\end{thebibliography}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-10-09 article.tex
Figure 1

@@
 \usepackage{todonotes}
+\usepackage{verbatim}
+\usepackage{tikz}
+\usepackage{tkz-graph}
+\usepackage{pgf}
+\usetikzlibrary{arrows,automata}
+
+% \newcommand*\beastscriptr{\verb;beastscriptr;}
 
@@
 \author{Rich\`el J.C. Bilderbeek}
+
+% \newcommand*\filename[1]{${#1}$}
+% \newcommand*\myfilename[1]{\verb;{#1};}
 
@@
 \begin{abstract}
-  \textbf{Motivation:} BEAST2 is a popular Bayesian phylogenetics tool.
-  The program BEAUti allows for a user-friendly way to create the
-  input files that BEAST2 needs. This is convenient to get started, yet
-  does not facilitate the scripted use of BEAST2. 
-  beastscriptr is an R package that can create BEAST2 input files from an R
-  function call.\\
-  \textbf{Results:} beastscriptr has only parts of the functionality of BEAUti, yet
-  can be extended easily. beastcriptr, on the other hand, does allow for specifying
-  to use phylogenies of fixed crown age.\\
-  \textbf{Availability:} The package is free and is available from the official R package archive at 
-  http://cran.r-project.org/src/contrib/PACKAGES.html\#beastscriptr. 
-  beastscriptr is licensed under the GNU General Public License.
-  \textbf{Key-words:} computational biology, evolution, phylogeny, BEAST2, R
+  \textbf{1. }
+  Here, I present a package, \verb;beastscriptr;, for the R programming language. \\
+  \textbf{2. }
+    \verb;beastscriptr; allows for scripted use of the BEAST2 phylogenetics tool, 
+    by creating BEAST2 input files from an R function call. \\
+  \textbf{3. }
+    I describe \verb;beastscriptr; usage, the novel functionality it provides
+    compared to BEAUti, and give some minimal examples. \\
+  \textbf{4. }
+    As \verb;beastscriptr; is free, libre, open-source and designed to be extended, 
+    I conclude by describing the current development of the package \\
 \end{abstract}
+
+% Key-words: computational biology, evolution, phylogeny, BEAST2, R
 
@@
 which  allows for a user-friendly way to create the
-input files that BEAST2 needs. This is convenient to get started, yet
-does not allow for the scripted use of BEAST2. beastscriptr is an R package 
-that can create BEAST2 input files from an R function call.
+input files that BEAST2 needs. BEAUti is convenient to get started, yet
+does not allow for the scripted use of BEAST2. For creating BEAST2 input
+files from a script, beastscriptr is the R package facilitating this:
+it creates a BEAST2 input files from an R function call.
+
+%\begin{figure}
+%  \centering
+%  \includegraphics[]{BeautiSiteModel.png}
+%  \caption{BEAUti}
+%  \label{figure:beauti}
+%\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+  \centering
+  \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=6cm, semithick]   
+  \tikzstyle{every state}=[]
+  \node[state] (A) [rectangle] {
+    \includegraphics[width=0.2\textwidth]{alignment.png}
+    \includegraphics[width=0.2\textwidth]{thought_cloud.png}
+  };   
+  \node[state] (E) [below of=A, rectangle] {
+    \includegraphics[height=0.1\textheight]{xml.png}
+  };   
+  \node[state] (F) [rectangle, below of=E] {\includegraphics[width=0.3\textwidth]{DensiTreeExample2.jpg}};
+  \path (A) edge [anchor = east] node {\includegraphics[height=0.15\textheight]{beastscriptr_logo.png}} (E)
+        (A) edge [anchor = west] node {\includegraphics[height=0.15\textheight]{BeautiSiteModel.png}} (E)
+        (E) edge [] node {\includegraphics[width=0.2\textwidth]{Beast2LogoRat.png}} (F); 
+  \end{tikzpicture}
+
+  \caption{
+    Workflow
+  }
+  \label{fig:beauti}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+The goal of the R package \verb;beastscriptr; is to create the 
+same BEAST2 input files that BEAUti creates, but from one R function call 
+instead.
+
+By creating BEAST2 input files in BEAUti, 
+the desired output of beastscriptr was determined. 
+The functionality of BEAUti is added gradually (and is still growing).
+
+\verb;beastscriptr; has only parts of the functionality of BEAUti, yet
+can be extended easily. beastcriptr, on the other hand, does allow for specifying
+to use phylogenies of fixed crown age.
+
+\verb;beastscriptr; has a novel functionality not built into BEAUti yet:
+it allows for using phylogenies of a fixed crown age.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+As in BEAUti, to create a BEAST2 input file, 
+one needs an alignment, model priors and MCMC parameters.
+When the alignment is stored in the file alignment.fasta,
+the desired tree prior is a constant-rate Birth-Death 
+model \cite{nee1994reconstructed} and the MCMC chain needs to run 1M 
+states, beastscriptr can create a file 
+(called \verb;birth_death.xml;) from R 
+as such:
+
+\begin{lstlisting}[language=R]
+beast_scriptr(
+  input_fasta_filename = "alignment.fasta",
+  mcmc_chainlength = 10000000,
+  tree_prior = "birth_death",
+  output_xml_filename = "birth_death.xml"
+)
+\end{lstlisting}
+
+The created file \verb;birth_death.xml; can then be used by BEAST2.
+
+Novel about beastscriptr is that it allows for specifying a fixed crown age:
+
+\begin{lstlisting}[language=R]
+beast_scriptr(
+  input_fasta_filename = "alignment.fasta",
+  mcmc_chainlength = 10000000,
+  tree_prior = "birth_death",
+  output_xml_filename = "birth_death_fixed_15.xml"
+  fixed_crown_age = TRUE,
+  initial_phylogeny = beastscriptr::fasta_to_phylo(
+    input_fasta_filename, crown_age = 15)
+)
+\end{lstlisting}
+
+In this example, a random phylogeny is created from the FASTA file, but
+one could also use a more informed initial phylogeny with the desired crown age.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+beastscriptr successfully creates valid BEAST2 input files. Unlike BEAUti,
+beascriptr allows for setting a fixed crown age.
+
+beastscriptr does not support the full functionality of BEAUti. Considering
+the size, age and number of plugins, this would be close to impossible.
+To compensate for this, an extensible software architecture is used.
+
+beastscriptr has minimal support for calling BEAST2 from within R and does
+so for testing purposes.
+
+beastscript has minimal support for parsing and interpreting BEAST2 output files,
+for that the RBeast package is recommended.
+
+The package is free and is available from the official R package archive at 
+http://cran.r-project.org/src/contrib/PACKAGES.html\#beastscriptr. 
+beastscriptr is licensed under the GNU General Public License.
 
@@
 
-\appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Approach}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The goal of the R package beastscriptr is to create the 
-same BEAST2 input files that BEAUti creates, but from one R function call 
-instead.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Methods}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-By creating BEAST2 input files in BEAUti, 
-the desired output of beastscriptr was determined. 
-The functionality of BEAUti is added gradually (and is still growing).
-
-beastscriptr has a novel functionality not built into BEAUti yet:
-it allows for using phylogenies of a fixed crown age.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-beastscriptr does not support the full functionality of BEAUti. Considering
-the size, age and number of plugins, this would be close to impossible.
-To compensate for this, an extensible software architecture is used.
-
-beastscriptr has minimal support for calling BEAST2 from within R and does
-so for testing purposes.
-
-beastscript has minimal support for parsing and interpreting BEAST2 output files,
-for that the RBeast package is recommended.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-beastscriptr successfully creates valid BEAST2 input files. Unlike BEAUti,
-beascriptr allows for setting a fixed crown age.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-10-26 article.tex
EOD

@@
 % \newcommand*\myfilename[1]{\verb;{#1};}
+
+% Style of code
+% From http://r.789695.n4.nabble.com/How-to-nicely-display-R-code-with-the-LaTeX-package-listings-tp4648110.html
+\usepackage{fancyvrb} 
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+\lstdefinestyle{mystyle}{
+  language=R,% set programming language
+  basicstyle=\ttfamily\small,% basic font style
+  commentstyle=\color{gray},% comment style
+  numbers=left,% display line numbers on the left side
+  numberstyle=\scriptsize,% use small line numbers
+  numbersep=10pt,% space between line numbers and code
+  tabsize=2,% sizes of tabs
+  showstringspaces=false,% do not replace spaces in strings by a certain character
+  captionpos=b,% positioning of the caption below
+  breaklines=true,% automatic line breaking
+  escapeinside={(*}{*)},% escaping to LaTeX
+  fancyvrb=true,% verbatim code is typset by listings
+  extendedchars=false,% prohibit extended chars (chars of codes 128--255)
+  literate={"}{{\texttt{"}}}1{<-}{{$\bm\leftarrow$}}1{<<-}{{$\bm\twoheadleftarrow$}}1
+  {~}{{$\bm\sim$}}1{<=}{{$\bm\le$}}1{>=}{{$\bm\ge$}}1{!=}{{$\bm\neq$}}1{^}{{$^{\bm\wedge}$}}1,% item to replace, text, length of chars
+  alsoletter={.<-},% becomes a letter
+  alsoother={$},% becomes other
+  otherkeywords={!=, ~, $, \&, \%/\%, \%*\%, \%\%, <-, <<-, /},% other keywords
+  deletekeywords={c}% remove keywords 
+}
+\lstset{style=mystyle}
 
@@
   \caption{
-    Workflow
+    Workflow. From an alignment and priors, one creates a BEAST2 XML input file. This
+    can be done using beastscript and BEAUti. The XML file created is run by BEAST2
+    to create a posterior.
   }
-  \label{fig:beauti}
+  \label{fig:workflow}
 \end{figure}
@@
 As in BEAUti, to create a BEAST2 input file, 
-one needs an alignment, model priors and MCMC parameters.
-When the alignment is stored in the file alignment.fasta,
-the desired tree prior is a constant-rate Birth-Death 
-model \cite{nee1994reconstructed} and the MCMC chain needs to run 1M 
-states, beastscriptr can create a file 
-(called \verb;birth_death.xml;) from R 
-as such:
+one needs an alignment and model settings.
+With those settings at their default, \verb;beastscriptr; is easy to use:
+Create a BEAST2 input file with name \verb;beast2.xml; from 
+a FASTA file with name \verb;alignment.fas; is done like this:
 
-\begin{lstlisting}[language=R]
-beast_scriptr(
-  input_fasta_filename = "alignment.fasta",
-  mcmc_chainlength = 10000000,
-  tree_prior = "birth_death",
-  output_xml_filename = "birth_death.xml"
+\begin{lstlisting}[language=R, caption=Simplest example]
+library(beastscriptr)
+create_beast2_input_file(
+  "alignment.fas",
+  "beast2.xml"
 )
@@
 
-The created file \verb;birth_death.xml; can then be used by BEAST2.
+The created file \verb;beast2.xml; can then be used by BEAST2.
 
@@
 
-\begin{lstlisting}[language=R]
-beast_scriptr(
-  input_fasta_filename = "alignment.fasta",
-  mcmc_chainlength = 10000000,
-  tree_prior = "birth_death",
-  output_xml_filename = "birth_death_fixed_15.xml"
+\begin{lstlisting}[language=R, caption=Example with fixed crown age]
+create_beast2_input_file(
+  "alignment.fas",
+  "beast2.xml"
   fixed_crown_age = TRUE,
   initial_phylogeny = beastscriptr::fasta_to_phylo(
-    input_fasta_filename, crown_age = 15)
+    fasta_filename = "alignment.fas", 
+    crown_age = 15
+  )
 )

### 2017-12-19 article.tex
beastscriptr is beautier

@@
 
-% \newcommand*\beastscriptr{\verb;beastscriptr;}
+% \newcommand*\beautier{\verb;beautier;}
 
-\title{beastscriptr: BEAUti for R}
+\title{beautier: BEAUti for R}
 \author{Rich\`el J.C. Bilderbeek}
@@
   \textbf{1. }
-  Here, I present a package, \verb;beastscriptr;, for the R programming language. \\
+  Here, I present a package, \verb;beautier;, for the R programming language. \\
   \textbf{2. }
-    \verb;beastscriptr; allows for scripted use of the BEAST2 phylogenetics tool, 
+    \verb;beautier; allows for scripted use of the BEAST2 phylogenetics tool, 
     by creating BEAST2 input files from an R function call. \\
   \textbf{3. }
-    I describe \verb;beastscriptr; usage, the novel functionality it provides
+    I describe \verb;beautier; usage, the novel functionality it provides
     compared to BEAUti, and give some minimal examples. \\
   \textbf{4. }
-    As \verb;beastscriptr; is free, libre, open-source and designed to be extended, 
+    As \verb;beautier; is free, libre, open-source and designed to be extended, 
     I conclude by describing the current development of the package \\
@@
 does not allow for the scripted use of BEAST2. For creating BEAST2 input
-files from a script, beastscriptr is the R package facilitating this:
+files from a script, beautier is the R package facilitating this:
 it creates a BEAST2 input files from an R function call.
@@
   \node[state] (F) [rectangle, below of=E] {\includegraphics[width=0.3\textwidth]{DensiTreeExample2.jpg}};
-  \path (A) edge [anchor = east] node {\includegraphics[height=0.15\textheight]{beastscriptr_logo.png}} (E)
+  \path (A) edge [anchor = east] node {\includegraphics[height=0.15\textheight]{beautier_logo.png}} (E)
         (A) edge [anchor = west] node {\includegraphics[height=0.15\textheight]{BeautiSiteModel.png}} (E)
@@
 
-The goal of the R package \verb;beastscriptr; is to create the 
+The goal of the R package \verb;beautier; is to create the 
 same BEAST2 input files that BEAUti creates, but from one R function call 
@@
 By creating BEAST2 input files in BEAUti, 
-the desired output of beastscriptr was determined. 
+the desired output of beautier was determined. 
 The functionality of BEAUti is added gradually (and is still growing).
 
-\verb;beastscriptr; has only parts of the functionality of BEAUti, yet
+\verb;beautier; has only parts of the functionality of BEAUti, yet
 can be extended easily. beastcriptr, on the other hand, does allow for specifying
@@
 
-\verb;beastscriptr; has a novel functionality not built into BEAUti yet:
+\verb;beautier; has a novel functionality not built into BEAUti yet:
 it allows for using phylogenies of a fixed crown age.
@@
 one needs an alignment and model settings.
-With those settings at their default, \verb;beastscriptr; is easy to use:
+With those settings at their default, \verb;beautier; is easy to use:
 Create a BEAST2 input file with name \verb;beast2.xml; from 
@@
 \begin{lstlisting}[language=R, caption=Simplest example]
-library(beastscriptr)
+library(beautier)
 create_beast2_input_file(
@@
 
-Novel about beastscriptr is that it allows for specifying a fixed crown age:
+Novel about beautier is that it allows for specifying a fixed crown age:
 
@@
   fixed_crown_age = TRUE,
-  initial_phylogeny = beastscriptr::fasta_to_phylo(
+  initial_phylogeny = beautier::fasta_to_phylo(
     fasta_filename = "alignment.fas", 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{beastscriptr development and other resources}
+\section{beautier development and other resources}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-beastscriptr successfully creates valid BEAST2 input files. Unlike BEAUti,
+beautier successfully creates valid BEAST2 input files. Unlike BEAUti,
 beascriptr allows for setting a fixed crown age.
 
-beastscriptr does not support the full functionality of BEAUti. Considering
+beautier does not support the full functionality of BEAUti. Considering
 the size, age and number of plugins, this would be close to impossible.
@@
 
-beastscriptr has minimal support for calling BEAST2 from within R and does
+beautier has minimal support for calling BEAST2 from within R and does
 so for testing purposes.
@@
 The package is free and is available from the official R package archive at 
-http://cran.r-project.org/src/contrib/PACKAGES.html\#beastscriptr. 
-beastscriptr is licensed under the GNU General Public License.
+http://cran.r-project.org/src/contrib/PACKAGES.html\#beautier. 
+beautier is licensed under the GNU General Public License.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Citation of beastscriptr}
+\section{Citation of beautier}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Scientists using beastscriptr in a published paper should cite this
-article. Users can additionally cite the beastscriptr package 
+Scientists using beautier in a published paper should cite this
+article. Users can additionally cite the beautier package 
 directly. Citation information can be obtained by typing:
@@
 \begin{lstlisting}[language=R]
-> citation("beastscriptr")
+> citation("beautier")
 \end{lstlisting}

### 2017-12-19 article.tex
beautier in verbatim

@@
 does not allow for the scripted use of BEAST2. For creating BEAST2 input
-files from a script, beautier is the R package facilitating this:
+files from a script, \verb;beautier; is the R package facilitating this:
 it creates a BEAST2 input files from an R function call.
@@
 By creating BEAST2 input files in BEAUti, 
-the desired output of beautier was determined. 
+the desired output of \verb;beautier; was determined. 
 The functionality of BEAUti is added gradually (and is still growing).
@@
 
-Novel about beautier is that it allows for specifying a fixed crown age:
+Novel about \verb;beautier; is that it allows for specifying a fixed crown age:
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{beautier development and other resources}
+\section{\verb;beautier; development and other resources}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-beautier successfully creates valid BEAST2 input files. Unlike BEAUti,
+\verb;beautier; successfully creates valid BEAST2 input files. Unlike BEAUti,
 beascriptr allows for setting a fixed crown age.
 
-beautier does not support the full functionality of BEAUti. Considering
+\verb;beautier; does not support the full functionality of BEAUti. Considering
 the size, age and number of plugins, this would be close to impossible.
@@
 
-beautier has minimal support for calling BEAST2 from within R and does
+\verb;beautier; has minimal support for calling BEAST2 from within R and does
 so for testing purposes.
 
-beastscript has minimal support for parsing and interpreting BEAST2 output files,
-for that the RBeast package is recommended.
+\verb;beautier; has minimal support for parsing and interpreting BEAST2 output files,
+for that the \verb;RBeast; package is recommended.
 
@@
 http://cran.r-project.org/src/contrib/PACKAGES.html\#beautier. 
-beautier is licensed under the GNU General Public License.
+\verb;beautier; is licensed under the GNU General Public License.
 
@@
 
-Scientists using beautier in a published paper should cite this
-article. Users can additionally cite the beautier package 
+Scientists using \verb;beautier; in a published paper should cite this
+article. Users can additionally cite the \verb;beautier; package 
 directly. Citation information can be obtained by typing:

### 2017-12-20 article.tex
beautier in verbatim
First go

@@
   \textbf{1. }
-  Here, I present a package, \verb;beautier;, for the R programming language. \\
+  Here, I present a package, \verb;beautier;, 'BEAUti for R', for the R programming language. \\
   \textbf{2. }
@@
 BEAST2 \cite{bouckaert2014beast} is a popular Bayesian phylogenetics tool.
-BEAST2 is bundled with the program called BEAUti \cite{drummond2012bayesian},
-which  allows for a user-friendly way to create the
-input files that BEAST2 needs. BEAUti is convenient to get started, yet
-does not allow for the scripted use of BEAST2. For creating BEAST2 input
-files from a script, \verb;beautier; is the R package facilitating this:
-it creates a BEAST2 input files from an R function call.
+BEAST2 is bundled with the program called BEAUti \cite{drummond2012bayesian}.
+BEAUti has a user-friendly graphical user interface to create BEAST2 input files,
+but does not allow for the scripted use of BEAST2. '
+\verb;beautier; does allow for scripted use of BEAST2 from an R function call.
+An additional novelty is that \verb;beautier; allows to specify a fixed crown age.
 
@@
 
-The goal of the R package \verb;beautier; is to create the 
-same BEAST2 input files that BEAUti creates, but from one R function call 
-instead.
+\verb;beautier; is written in the R programming language \cite{R}.
+\verb;beautier; creates the BEAST2 input files from an R function call.
+
+\verb;beautier;'s main function is \verb;create_beast2_input_file;, which creates
+an BEAST2 input file.
+
+\verb;create_beast2_input_file; needs at least the name of a FASTA file containing a DNA alignment
+and a name for the to-be-created output file. This interface follows BEAUti's default settings.
+Per alignment, a site model, clock model and tree priors can be chosen.
+Multiple alignments can be used, each with its own (unlinked) site model, clock model and tree prior.
+
+\begin{table}[]
+\centering
+\begin{tabular}{ | l | l | }
+\hline
+\textbf{Name} & \textbf{Description} \\
+\hline
+\verb;create_beast2_input_file; & Creates a BEAST2 input file \\
+\hline
+\verb;create_gamma_site_model; & Create a gamma site model \\
+\verb;create_gtr_site_model; & Create a GTR site model \\
+\verb;create_hky_site_model; & Create an HKY site model \\
+\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
+\verb;create_tn93_site_model; & Create a TN93 site model \\
+\hline
+\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
+\verb;create_strict_clock_model; & Create a strict clock model \\
+\hline
+\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
+\verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
+\verb;create_ccp_tree_prior; & Create a coalescent constant-population tree prior \\
+\verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
+\verb;create_yule_tree_prior; & Create a Yule tree prior \\
+\hline
+\verb;create_beta_distr; & Create a beta distribution \\
+\verb;create_exp_distr; & Create an exponential distribution \\
+\verb;create_gamma_distr; & Create a gamma distribution \\
+\verb;create_inv_gamma_distr; & Create an inverse gamma distribution \\
+\verb;create_laplace_distr; & Create a Laplace distribution \\
+\verb;create_log_normal_distr; & Create a log-normal distribution \\
+\verb;create_normal_distr; & Create a normal distribution \\
+\verb;create_one_div_x_distr; & Create a 1/X distribution \\
+\verb;create_poisson_distr; & Create a Poisson distribution \\
+\verb;create_uniform_distr; & Create a uniform distribution \\
+\hline
+\end{tabular}
+\caption{beautier's functions}
+\label{tab:functions}
+\end{table}
 
@@
 \verb;beautier; has only parts of the functionality of BEAUti, yet
-can be extended easily. beastcriptr, on the other hand, does allow for specifying
+can be extended easily. \verb;beautier; , on the other hand, does allow for specifying
 to use phylogenies of fixed crown age.
@@
 
-As in BEAUti, to create a BEAST2 input file, 
-one needs an alignment and model settings.
-With those settings at their default, \verb;beautier; is easy to use:
-Create a BEAST2 input file with name \verb;beast2.xml; from 
-a FASTA file with name \verb;alignment.fas; is done like this:
+In R, a package's function need to be loaded in the global namespace first:
 
-\begin{lstlisting}[language=R, caption=Simplest example]
+\begin{lstlisting}[language=R, caption=Loading, label=lst:loading_beautier, floatplacement=H]
+library(beautier)
+\end{lstlisting}
+
+BEAUti, and likewise \verb;beautier;, need at least a FASTA filename
+and an XML output filename. In BEAUti, this is achieved by loading a FASTA file (resulting
+in figure \ref{fig:simplest_beauti_usage}), then saving an output file using a common
+save file dialog. In \verb;beautier;, the same is achieved by listing \ref{lst:simplest_example}:
+
+\begin{lstlisting}[language=R, caption=Simplest example, label=lst:simplest_example, floatplacement=H]
 library(beautier)
@@
 
-The created file \verb;beast2.xml; can then be used by BEAST2.
+\begin{figure}
+  \centering
+  \includegraphics[]{all_default.png}
+  \caption{Simplest BEAUti usage}
+  \label{fig:simplest_beauti_usage}
+\end{figure}
 
-Novel about \verb;beautier; is that it allows for specifying a fixed crown age:
+This code will create a BEAST2 file with name '\verb;beast2.xml;',
+using a FASTA file with name \verb;alignment.fas;, using the same default settings as BEAUti.
+The default settings are, among others, to use a Jukes-Cantor site model, a strict clock,
+and a Yule birth tree prior. Listing \ref{lis:simplest_example_explicit} shows how
+to explicitly pick these settings:
 
-\begin{lstlisting}[language=R, caption=Example with fixed crown age]
+\begin{lstlisting}[language=R, caption=Simplest example with explicit defaults, label=lst:simplest_example_explicit, floatplacement=H]
+library(beautier)
+create_beast2_input_file(
+  input_fasta_filenames = "alignment.fas",
+  output_xml_filename = "beast2.xml",
+  site_models = create_jc69_site_model(),
+  clock_models = create_strict_clock_model(),
+  tree_priors = create_yule_tree_prior()
+)
+\end{lstlisting}
+
+The argument names \verb;input_fasta_filenames;, \verb;site_models;, \verb;clock_models; and \verb;tree_priors; are plural, as each of these
+can be (a list of) one or more elements. Each of these arguments must have the same number of elements, so that each alignment has its
+own site model, clock model and tree prior. An example of using a different site model, clock model and tree prior is shown by listing \ref{lis:all_different}:
+
+\begin{lstlisting}[language=R, caption=Example with different site model and clock model and tree prior, label=lst:all_different, floatplacement=H]
+library(beautier)
+create_beast2_input_file(
+  input_fasta_filenames = "alignment.fas",
+  output_xml_filename = "beast2.xml",
+  site_models = create_hky_site_model(),
+  clock_models = create_rln_clock_model(),
+  tree_priors = create_bd_tree_prior()
+)
+\end{lstlisting}
+
+This code uses an HKY site model, a relaxed log-normal clock model and a birth-death tree prior.
+Table \ref{tab:functions} shows an overview of all functions to create site models, clock models and tree priors.
+
+\verb;beautier; creates site models, clock models and tree priors with the same default distrbutions as BEAUti.
+For example, a Yule tree prior assumes that birth rate likelihoods follow a uniform distribution, from minus infinity
+to infinity. This assumption entails that negative and positive birth rates are just as likely, where a negative birth rate is biologically impossible. 
+One may prefer to have an exponential distribution instead, as this would state that birth rates are always positive, and
+higher values are less likely than lower values. To do so \verb;beautier; is shown by listing \ref{lis:diff_distr}:
+
+\begin{lstlisting}[language=R, caption=Example with Yule tree prior with different birth rate distribution, label=lst:diff_distr, floatplacement=H]
+library(beautier)
+create_beast2_input_file(
+  input_fasta_filenames = "alignment.fas",
+  output_xml_filename = "beast2.xml",
+  tree_priors = create_yule_tree_prior(
+    birth_rate_distr = create_exp_distr()    
+  )
+)
+\end{lstlisting}
+
+Novel about \verb;beautier; is that it allows for specifying a fixed crown age. 
+By default, a phylogeny's crown age is jointly estimated with the other parameters.
+Setting a fixed crown age is not yet possible in BEAUti directly, but it is documented how to 
+manually edit the XML file to allow for a fixed crown age. Listing \ref{lst:fixed_crown_age} shows how to specify a fixed crown age is \verb;beautier;:
+
+\begin{lstlisting}[language=R, caption=Example with fixed crown age, label=lst:fixed_crown_age, floatplacement=H]
 create_beast2_input_file(
@@
   fixed_crown_age = TRUE,
-  initial_phylogeny = beautier::fasta_to_phylo(
+  initial_phylogeny = fasta_to_phylo(
     fasta_filename = "alignment.fas", 
@@
 
-In this example, a random phylogeny is created from the FASTA file, but
-one could also use a more informed initial phylogeny with the desired crown age.
+This code shows that setting \verb;fixed_crown_age; to true is insufficient. An
+initial phylogeny of the desired (fixed) crown age needs to be supplied. In this
+example, a random phylogeny is constructed from the FASTA filename. Supplying an 
+informed phylogeny will make the MCMC algorithm start at a likelier initial state.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\verb;beautier; development and other resources}
+\section{beautier development and other resources}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \verb;beautier; successfully creates valid BEAST2 input files. Unlike BEAUti,
-beascriptr allows for setting a fixed crown age.
+\verb;beautier; allows for setting a fixed crown age.
 
@@
 \verb;beautier; has minimal support for calling BEAST2 from within R and does
-so for testing purposes.
+so for testing purposes only.
 

### 2017-12-20 article.tex
First go

@@
 \usepackage{listings}
+\usepackage{hyperref}
 \usepackage{todonotes}
@@
 
+\verb;beautier; does not support the full functionality of BEAUti. Considering
+the size, age and number of plugins, this would be close to impossible.
+To compensate for this, an extensible software architecture is used.
+
+\verb;beautier; has minimal support for calling BEAST2 from within R and does
+so for testing purposes only.
+
+\verb;beautier; has minimal support for parsing and interpreting BEAST2 output files,
+for that the \verb;RBeast; \cite{RBeast} package is recommended.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\verb;beautier; successfully creates valid BEAST2 input files. Unlike BEAUti,
-\verb;beautier; allows for setting a fixed crown age.
+\verb;beautier; is free, libre and open source software available from the official R package archive at 
+\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#beautier}.  
+\verb;beautier; is licensed under the GNU General Public License.
 
-\verb;beautier; does not support the full functionality of BEAUti. Considering
-the size, age and number of plugins, this would be close to impossible.
-To compensate for this, an extensible software architecture is used.
+\verb;beautier;'s development takes place on GitHub \cite{github}. 
+GitHub is a website that hosts (among others) software and facilites its development.
+Using GitHub is a good practice for computational scientists \cite{perez2016ten} 
+and improves transparency \cite{gorgolewski2016practical}.
 
-\verb;beautier; has minimal support for calling BEAST2 from within R and does
-so for testing purposes only.
+\verb;beautier;'s quality is assured by Travis CI \cite{travis}. Travis CI is
+a continuous integration service, that runs a script upon a (suggested)
+change in \verb;beautier;'s code. The \verb;beautier; script checks if the
+package can be build, runs all unit and intergration tests, 
+measures code coverage, coding style and good practices.
 
-\verb;beautier; has minimal support for parsing and interpreting BEAST2 output files,
-for that the \verb;RBeast; package is recommended.
+Unit and integration tests check the intergrity of \verb;beatier;. All functions
+are tested for producing the correct output and desired error handling. 
+Travis CI uses the testing facilities of the \verb;testthat; \cite{testthat} package.
 
-The package is free and is available from the official R package archive at 
-http://cran.r-project.org/src/contrib/PACKAGES.html\#beautier. 
-\verb;beautier; is licensed under the GNU General Public License.
+Code coverage is the percentage of code that is executed in tests. 
+Code coverage correlates with code quality \cite{del1995correlation}. 
+Travis CI uses the \verb;covr; \cite{covr} package to measure code coverage. 
+\verb;beautier; has a 100\% code coverage.
+
+Coding style is the way statements are laid out, for example the placement of 
+curly brackets. \verb;beautier; follows Hadley Wickham's style guide. 
+Travis CI uses the \verb;lintr; \cite{lintr} package to comfirm this coding style
+is used.
+
+Good practices are miscellaneous things considered good practices. An example
+of a good practice is (next to high code coverage and consistent coding style) 
+to have short functions with a low cyclomatic complexity. Travis CI uses 
+the \verb;goodpractice; \cite{goodpractice} package to comfirm all good practices
+are followed.
+
+\verb;beautier; is dependent on multiple packages, which are 
+\verb;APE; \cite{APE}, 
+\verb;devtools; \cite{devtools},
+\verb;geiger; \cite{GEIGER},
+\verb;ggplot2; \cite{ggplot2},
+\verb;knitr; \cite{knitr},
+\verb;phangorn; \cite{phangorn},
+\verb;RBeast; \cite{RBeast},
+\verb;rmarkdown; \cite{rmarkdown},
+\verb;seqinr; \cite{seqinr},
+\verb;stringr; \cite{stringr},
+\verb;testit; \cite{testit} and 
+\verb;TreeSim; \cite{TreeSim}.
+
+\verb;beautier;'s documentation is extensive, yet concise. All funnctions are documented
+in the package's internal documentation. For quick use, each exported function shows a minimal example. 
+For easy exploration, each exported function's documentation links to related functions.
+Additionally, \verb;beautier; has a vignette that demonstrates in a longer form how
+to use it. The integrity of this documentation is tested each time the package is built by Travis CI.
+The documentation on the GitHub helps to get started, with a dozen examples 
+of a BEAUti screenshot and the equivalent \verb;beautier; code.
+
+\verb;beautier;'s GitHub facilitates feature requests and guidelines how to do so.
+New code can be submitted using GitHub's infrastructure (a 'Pull Request'). New
+code will be tested by Travis CI to follow the same quality standards and only accepted
+when there are no
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgements}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We would like to thank the Center for Information Technology of the University of Groningen for their support
-and for providing access to the Peregrine high performance computing cluster.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{plain}

### 2017-12-20 article.tex
Improved references

@@
 \verb;create_hky_site_model; & Create an HKY site model \\
-\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
+\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \cite{cantor1969mammalian} \\
 \verb;create_tn93_site_model; & Create a TN93 site model \\
@@
 \verb;beautier; has only parts of the functionality of BEAUti, yet
-can be extended easily. \verb;beautier; , on the other hand, does allow for specifying
+can be extended easily. \verb;beautier;, on the other hand, does allow for specifying
 to use phylogenies of fixed crown age.
@@
 using a FASTA file with name \verb;alignment.fas;, using the same default settings as BEAUti.
-The default settings are, among others, to use a Jukes-Cantor site model, a strict clock,
-and a Yule birth tree prior. Listing \ref{lis:simplest_example_explicit} shows how
+The default settings are, among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
+a strict clock, and a Yule birth tree prior. Listing \ref{lis:simplest_example_explicit} shows how
 to explicitly pick these settings:
@@
 Coding style is the way statements are laid out, for example the placement of 
-curly brackets. \verb;beautier; follows Hadley Wickham's style guide. 
+curly brackets. \verb;beautier; follows Hadley Wickham's style guide \cite{style_guide}. 
 Travis CI uses the \verb;lintr; \cite{lintr} package to comfirm this coding style

### 2017-12-20 article.tex
Improved references

@@
 \verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
-\verb;create_yule_tree_prior; & Create a Yule tree prior \\
+\verb;create_yule_tree_prior; & Create a Yule tree prior \cite{yule} \\
 \hline
@@
 The default settings are, among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
-a strict clock, and a Yule birth tree prior. Listing \ref{lis:simplest_example_explicit} shows how
+a strict clock, and a Yule birth tree prior \cite{yule1925mathematical}. Listing \ref{lis:simplest_example_explicit} shows how
 to explicitly pick these settings:

### 2017-12-20 article.tex
Figure as wide as text

@@
 \hline
-\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
+\verb;create_bd_tree_prior; & Create a birth-death tree prior \cite{kendall1948generalized} \\
 \verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
@@
   \centering
-  \includegraphics[]{all_default.png}
+  \includegraphics[width=\textwidth]{all_default.png}
   \caption{Simplest BEAUti usage}
@@
 The default settings are, among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
-a strict clock, and a Yule birth tree prior \cite{yule1925mathematical}. Listing \ref{lis:simplest_example_explicit} shows how
+a strict clock, and a Yule birth tree prior \cite{yule}. Listing \ref{lis:simplest_example_explicit} shows how
 to explicitly pick these settings:
@@
 
-This code uses an HKY site model, a relaxed log-normal clock model and a birth-death tree prior.
+This code uses an HKY site model, a relaxed log-normal clock model and a birth-death tree prior \cite{kendall1948generalized}.
 Table \ref{tab:functions} shows an overview of all functions to create site models, clock models and tree priors.

### 2017-12-22 article.tex
How to build article (for @rsetienne)
EOD

@@
 
-BEAST2 \cite{bouckaert2014beast} is a popular Bayesian phylogenetics tool.
-BEAST2 is bundled with the program called BEAUti \cite{drummond2012bayesian}.
-BEAUti has a user-friendly graphical user interface to create BEAST2 input files,
-but does not allow for the scripted use of BEAST2. '
-\verb;beautier; does allow for scripted use of BEAST2 from an R function call.
-An additional novelty is that \verb;beautier; allows to specify a fixed crown age.
+BEAST2 \cite{bouckaert2014beast} is a Bayesian phylogenetics tool.
+BEAST2 creates a posterior of jointly-estimated phylonies and model
+parameters, from a DNA, RNA or amino acid alignment. BEAST2 can be run
+from the command line. To run BEAST2 from the command-line, 
+an XML configuration file is needed, that contains the alignment and model parameters.
 
-%\begin{figure}
-%  \centering
-%  \includegraphics[]{BeautiSiteModel.png}
-%  \caption{BEAUti}
-%  \label{figure:beauti}
-%\end{figure}
+BEAST2 is bundled with BEAUti \cite{drummond2012bayesian}. 
+BEAUti is a program to create a BEAST2 XML configuration file, 
+with a user-friendly graphical user interface.
+BEAUti's purpose is to help new BEAST2 users getting started.
+To do so, BEAUti starts with reasonable default settings. To
+create a minimal BEAST2 configuration file, BEAUti only needs one alignment file.
+BEAUti cannot be used from within shell scripts.
+
+\verb;beautier;, 'BEAUti for R', allows for creating BEAST2 configuration files 
+from an R function call. The interface of \verb;beautier; mimics BEAUti. This
+familiar interface helps experienced BEAST2 users to create configuration'
+files from shell scripts.
+
+BEAUti does not allow yet that an inferred phylogeny's crown age is fixed.
+In an emperical context, a phylogeny's crown age is one of the estimated
+parameters. For theoretical work, a fixed and known crown age can result
+in a cleaner analysis. \verb;beautier; allows to specify a fixed crown age.
 
@@
         (A) edge [anchor = west] node {\includegraphics[height=0.15\textheight]{BeautiSiteModel.png}} (E)
-        (E) edge [] node {\includegraphics[width=0.2\textwidth]{Beast2LogoRat.png}} (F); 
+        (E) edge [] node {\includegraphics[width=0.2\textwidth]{beast_logo.png}} (F); 
   \end{tikzpicture}
@@
     Workflow. From an alignment and priors, one creates a BEAST2 XML input file. This
-    can be done using beastscript and BEAUti. The XML file created is run by BEAST2
+    can be done using beautier or BEAUti. The created configuration file is run by BEAST2
     to create a posterior.
@@
 \hline
-\verb;create_gamma_site_model; & Create a gamma site model \\
 \verb;create_gtr_site_model; & Create a GTR site model \\
@@
 
-By creating BEAST2 input files in BEAUti, 
-the desired output of \verb;beautier; was determined. 
-The functionality of BEAUti is added gradually (and is still growing).
+In total, \verb;beautier; has 59 exported functions to create
+a BEAST2 configuration file. \verb;beautier; is an alternative for a majority of BEAUti use cases.
+\verb;beautier;s future extensions (also: road map) can be found on its GitHub.
 
-\verb;beautier; has only parts of the functionality of BEAUti, yet
-can be extended easily. \verb;beautier;, on the other hand, does allow for specifying
+\verb;beautier;, on the other hand, does allow for specifying
 to use phylogenies of fixed crown age.
@@
 \verb;beautier; has minimal support for parsing and interpreting BEAST2 output files,
-for that the \verb;RBeast; \cite{RBeast} package is recommended.
+for that the \verb;beastier; \cite{beastier} package is recommended.
 

### 2017-12-22 article.tex
Rewrite

@@
 \definecolor{codepurple}{rgb}{0.58,0,0.82}
-\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+\definecolor{backcolor}{rgb}{0.95,0.95,0.92}
 \lstdefinestyle{mystyle}{
@@
   \textbf{1. }
-  Here, I present a package, \verb;beautier;, 'BEAUti for R', for the R programming language. \\
+  Here, we present a package, \verb;beautier;, 'BEAUti for R', for the R programming language. \\
   \textbf{2. }
@@
 BEAST2 \cite{bouckaert2014beast} is a Bayesian phylogenetics tool.
-BEAST2 creates a posterior of jointly-estimated phylonies and model
+BEAST2 creates a posterior of jointly estimated phylonies and model
 parameters, from a DNA, RNA or amino acid alignment. BEAST2 can be run
@@
 \verb;beautier; is written in the R programming language \cite{R}.
-\verb;beautier; creates the BEAST2 input files from an R function call.
+\verb;beautier; creates the BEAST2 input files from an R function call,
+in a similar way that BEAUti does.
 
 \verb;beautier;'s main function is \verb;create_beast2_input_file;, which creates
-an BEAST2 input file.
-
-\verb;create_beast2_input_file; needs at least the name of a FASTA file containing a DNA alignment
+an BEAST2 input file. \verb;create_beast2_input_file; needs at least the name of a FASTA file containing a DNA alignment
 and a name for the to-be-created output file. This interface follows BEAUti's default settings.
@@
 a BEAST2 configuration file. \verb;beautier; is an alternative for a majority of BEAUti use cases.
-\verb;beautier;s future extensions (also: road map) can be found on its GitHub.
-
-\verb;beautier;, on the other hand, does allow for specifying
-to use phylogenies of fixed crown age.
-
-\verb;beautier; has a novel functionality not built into BEAUti yet:
-it allows for using phylogenies of a fixed crown age.
-
 \verb;beautier; does not support the full functionality of BEAUti. Considering
@@
 To compensate for this, an extensible software architecture is used.
+\verb;beautier;s future extensions can be found on its GitHub.
 
-\verb;beautier; has minimal support for calling BEAST2 from within R and does
-so for testing purposes only.
+BEAUti assumes that a phylogeny has a crown age that needs to be jointly estimated
+with the phylogeny and other parameters. BEAUti does not allow for fixing
+a phylogeny's crown age. Before \verb;beautier;, one needs to manually edit the BEAST2 
+XML configuration file, which is prone to errors. \verb;beautier;, allow easy
+fixing of phylogenies' crown ages.
 
-\verb;beautier; has minimal support for parsing and interpreting BEAST2 output files,
+\verb;beautier; has only internal support for calling BEAST2 from within R and does
+so for testing purposes only. \verb;beautier; has minimal support for parsing and interpreting BEAST2 output files,
 for that the \verb;beastier; \cite{beastier} package is recommended.
@@
   "beast2.xml"
-  fixed_crown_age = TRUE,
-  initial_phylogeny = fasta_to_phylo(
+  fixed_crown_ages = TRUE,
+  initial_phylogenies = fasta_to_phylo(
     fasta_filename = "alignment.fas", 
@@
 \verb;phangorn; \cite{phangorn},
-\verb;RBeast; \cite{RBeast},
+\verb;beastier; \cite{beastier},
 \verb;rmarkdown; \cite{rmarkdown},
@@
 
-\verb;beautier;'s documentation is extensive, yet concise. All funnctions are documented
+\verb;beautier;'s documentation is extensive, yet concise. All functions are documented
 in the package's internal documentation. For quick use, each exported function shows a minimal example. 

### 2017-12-22 article.tex
Before sending out

@@
 \title{beautier: BEAUti for R}
-\author{Rich\`el J.C. Bilderbeek}
+\author{Rich\`el J.C. Bilderbeek, Rampal S. Etienne}
 
@@
 BEAUti does not allow yet that an inferred phylogeny's crown age is fixed.
-In an emperical context, a phylogeny's crown age is one of the estimated
+In an empirical context, a phylogeny's crown age is one of the estimated
 parameters. For theoretical work, a fixed and known crown age can result
@@
 
-\verb;beautier; creates site models, clock models and tree priors with the same default distrbutions as BEAUti.
+\verb;beautier; creates site models, clock models and tree priors with the same default distributions as BEAUti.
 For example, a Yule tree prior assumes that birth rate likelihoods follow a uniform distribution, from minus infinity
@@
 \verb;beautier;'s development takes place on GitHub \cite{github}. 
-GitHub is a website that hosts (among others) software and facilites its development.
+GitHub is a website that hosts (among others) software and facilitates its development.
 Using GitHub is a good practice for computational scientists \cite{perez2016ten} 
@@
 change in \verb;beautier;'s code. The \verb;beautier; script checks if the
-package can be build, runs all unit and intergration tests, 
+package can be build, runs all unit and integration tests, 
 measures code coverage, coding style and good practices.
 
-Unit and integration tests check the intergrity of \verb;beatier;. All functions
+Unit and integration tests check the integrity of \verb;beatier;. All functions
 are tested for producing the correct output and desired error handling. 
@@
 curly brackets. \verb;beautier; follows Hadley Wickham's style guide \cite{style_guide}. 
-Travis CI uses the \verb;lintr; \cite{lintr} package to comfirm this coding style
+Travis CI uses the \verb;lintr; \cite{lintr} package to confirm this coding style
 is used.

### 2017-12-23 article.tex
Use beauter v1.12.1 interface

@@
 Setting a fixed crown age is not yet possible in BEAUti directly, but it is documented how to 
-manually edit the XML file to allow for a fixed crown age. Listing \ref{lst:fixed_crown_age} shows how to specify a fixed crown age is \verb;beautier;:
+manually edit the XML file to allow for a fixed crown age. Listing \ref{lst:fixed_crown_age} shows how to specify a fixed crown age with \verb;beautier;:
 
@@
   "beast2.xml"
-  fixed_crown_ages = TRUE,
-  initial_phylogenies = fasta_to_phylo(
-    fasta_filename = "alignment.fas", 
   crown_age = 15
 )
-)
 \end{lstlisting}
-
-This code shows that setting \verb;fixed_crown_age; to true is insufficient. An
-initial phylogeny of the desired (fixed) crown age needs to be supplied. In this
-example, a random phylogeny is constructed from the FASTA filename. Supplying an 
-informed phylogeny will make the MCMC algorithm start at a likelier initial state.
 

### 2017-12-29 article.tex
EOD

@@
   "beast2.xml"
-  crown_age = 15
+  posterior_crown_age = 15
 )

### 2018-01-16 article.tex
Use new logo
Add lumier logo, rewrote part of text

@@
   \textbf{3. }
-    I describe \verb;beautier; usage, the novel functionality it provides
+    We describe \verb;beautier; usage, the novel functionality it provides
     compared to BEAUti, and give some minimal examples. \\
@@
     As \verb;beautier; is free, libre, open-source and designed to be extended, 
-    I conclude by describing the current development of the package \\
+    We conclude by describing the current development of the package \\
 \end{abstract}
@@
 
+Phylogenies are a commonly used tool to explore evolutionary hypotheses.
+Not only can phylogenies tell us how species relate to each other, also relevant parameters like
+extinction and speciation rates can be estimated from them.
+
 BEAST2 \cite{bouckaert2014beast} is a Bayesian phylogenetics tool.
-BEAST2 creates a posterior of jointly estimated phylonies and model
-parameters, from a DNA, RNA or amino acid alignment. BEAST2 can be run
-from the command line. To run BEAST2 from the command-line, 
-an XML configuration file is needed, that contains the alignment and model parameters.
+BEAST2 creates a posterior of jointly-estimated phylonies and model
+parameters, from a DNA, RNA or amino acid alignment. BEAST2 is a 
+console application, that needs a configuration file containing alignments and model parameters.
 
-BEAST2 is bundled with BEAUti \cite{drummond2012bayesian}. 
+BEAST2 is bundled with the BEAUti \cite{drummond2012bayesian}. 
 BEAUti is a program to create a BEAST2 XML configuration file, 
-with a user-friendly graphical user interface.
-BEAUti's purpose is to help new BEAST2 users getting started.
-To do so, BEAUti starts with reasonable default settings. To
-create a minimal BEAST2 configuration file, BEAUti only needs one alignment file.
-BEAUti cannot be used from within shell scripts.
+using a user-friendly graphical user interface, with helpful and reasonable 
+default settings. BEAUti replaces the manual editing of the BEAST2 XML
+files.
 
-\verb;beautier;, 'BEAUti for R', allows for creating BEAST2 configuration files 
-from an R function call. The interface of \verb;beautier; mimics BEAUti. This
-familiar interface helps experienced BEAST2 users to create configuration'
-files from shell scripts.
+BEAUti cannot be called from a command-line script, which is not a problem in all cases.
+For example, the BEAST book \cite{drummond2015bayesian} encourages to first infer a posterior
+from simpler models first, then exploring if adding complexity changes the inferred results.
+This can easily be done manually using BEAUti. 
+For bigger theoretical explorations (for example, using thousands of simulated alignments), this approach
+becomes inviable.
 
-BEAUti does not allow yet that an inferred phylogeny's crown age is fixed.
-In an empirical context, a phylogeny's crown age is one of the estimated
-parameters. For theoretical work, a fixed and known crown age can result
-in a cleaner analysis. \verb;beautier; allows to specify a fixed crown age.
+Here, we present \verb;beautier;, 'BEAUti for R', which 
+creates BEAST2 configuration files from an R function call. 
+The interface of \verb;beautier; mimics BEAUti and is easy to use. This
+familiar interface helps both beginner and experienced BEAST2 users 
+to create configuration files from shell scripts.
 
@@
   };   
-  \node[state] (F) [rectangle, below of=E] {\includegraphics[width=0.3\textwidth]{DensiTreeExample2.jpg}};
+  \node[state] (F) [rectangle, below of=E] {
+    \includegraphics[width=0.3\textwidth]{DensiTreeExample2.jpg}
+    \includegraphics[width=0.6\textwidth]{ParameterEstimates.png}
+  };
   \path (A) edge [anchor = east] node {\includegraphics[height=0.15\textheight]{beautier_logo.png}} (E)
         (A) edge [anchor = west] node {\includegraphics[height=0.15\textheight]{BeautiSiteModel.png}} (E)
-        (E) edge [] node {\includegraphics[width=0.2\textwidth]{beast_logo.png}} (F); 
+        (E) edge [anchor = east] node {\includegraphics[width=0.25\textwidth]{lumier_logo_big.png}} (F) 
+        (E) edge [anchor = west] node {\includegraphics[width=0.2\textwidth]{beast_logo.png}} (F); 
   \end{tikzpicture}
@@
     Workflow. From an alignment and priors, one creates a BEAST2 XML input file. This
-    can be done using beautier or BEAUti. The created configuration file is run by BEAST2
-    to create a posterior.
+    can be done using beautier or BEAUti. The created configuration file is run by lumier or BEAST2
+    to create a posterior of phylogenies and model parameter estimates.
   }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Descriptions}
+\section{Description}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \hline
-\verb;create_gtr_site_model; & Create a GTR site model \\
-\verb;create_hky_site_model; & Create an HKY site model \\
+\verb;create_gtr_site_model; & Create a GTR site model \cite{tavare1986some} \\
+\verb;create_hky_site_model; & Create an HKY site model \cite{hasegawa1985dating} \\
 \verb;create_jc69_site_model; & Create a Jukes-Cantor site model \cite{cantor1969mammalian} \\
-\verb;create_tn93_site_model; & Create a TN93 site model \\
+\verb;create_tn93_site_model; & Create a TN93 site model \cite{tamura1993estimation} \\
 \hline
-\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
-\verb;create_strict_clock_model; & Create a strict clock model \\
+\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \cite{drummond2006relaxed} \\
+\verb;create_strict_clock_model; & Create a strict clock model \cite{sarich1967immunological} \\
 \hline
@@
 \verb;beautier; does not support the full functionality of BEAUti. Considering
-the size, age and number of plugins, this would be close to impossible.
+BEAUti's flexibility and number of plugins, this would be a Herculean effort.
 To compensate for this, an extensible software architecture is used.
@@
 
-BEAUti assumes that a phylogeny has a crown age that needs to be jointly estimated
+BEAUti assumes that a phylogeny has a crown age that needs to be jointly-estimated
 with the phylogeny and other parameters. BEAUti does not allow for fixing
 a phylogeny's crown age. Before \verb;beautier;, one needs to manually edit the BEAST2 
-XML configuration file, which is prone to errors. \verb;beautier;, allow easy
-fixing of phylogenies' crown ages.
+XML configuration file, which is prone to errors. \verb;beautier;, allows easy
+fixing of phylogenies' crown ages. For theoretical work, a fixed and known crown age can result
+in a cleaner analysis.
 
-\verb;beautier; has only internal support for calling BEAST2 from within R and does
-so for testing purposes only. \verb;beautier; has minimal support for parsing and interpreting BEAST2 output files,
-for that the \verb;beastier; \cite{beastier} package is recommended.
+\verb;beastier; and \verb;lumier; are related packages, used in testing. 
+\verb;lumier; calls BEAST2 from within R. \verb;lumier; is used to confirm that the XML files 
+created by \verb;beautier; are valid. Additionally, \verb;lumier; is used to run BEAST2
+to create posteriors. Using \verb;beastier;, these posteriors are checked to have an
+estimated or fixed crown age.
 
@@
 The default settings are, among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
-a strict clock, and a Yule birth tree prior \cite{yule}. Listing \ref{lis:simplest_example_explicit} shows how
-to explicitly pick these settings:
+a strict clock, and a Yule birth tree prior \cite{yule}.
 
-\begin{lstlisting}[language=R, caption=Simplest example with explicit defaults, label=lst:simplest_example_explicit, floatplacement=H]
-library(beautier)
-create_beast2_input_file(
-  input_fasta_filenames = "alignment.fas",
-  output_xml_filename = "beast2.xml",
-  site_models = create_jc69_site_model(),
-  clock_models = create_strict_clock_model(),
-  tree_priors = create_yule_tree_prior()
-)
-\end{lstlisting}
-
-The argument names \verb;input_fasta_filenames;, \verb;site_models;, \verb;clock_models; and \verb;tree_priors; are plural, as each of these
-can be (a list of) one or more elements. Each of these arguments must have the same number of elements, so that each alignment has its
-own site model, clock model and tree prior. An example of using a different site model, clock model and tree prior is shown by listing \ref{lis:all_different}:
+An example of using a different site model, clock model and tree prior is shown by listing \ref{lst:all_different}:
 
@@
 create_beast2_input_file(
-  input_fasta_filenames = "alignment.fas",
-  output_xml_filename = "beast2.xml",
+  "alignment.fas",
+  "beast2.xml",
   site_models = create_hky_site_model(),
@@
 
+The argument names \verb;site_models;, \verb;clock_models; and \verb;tree_priors; are plural, as each of these
+can be (a list of) one or more elements. Each of these arguments must have the same number of elements, so that each alignment has its
+own site model, clock model and tree prior.
+
 \verb;beautier; creates site models, clock models and tree priors with the same default distributions as BEAUti.
@@
 One may prefer to have an exponential distribution instead, as this would state that birth rates are always positive, and
-higher values are less likely than lower values. To do so \verb;beautier; is shown by listing \ref{lis:diff_distr}:
+higher values are less likely than lower values. To do so \verb;beautier; is shown by listing \ref{lst:diff_distr}:
 
@@
 create_beast2_input_file(
-  input_fasta_filenames = "alignment.fas",
-  output_xml_filename = "beast2.xml",
+  "alignment.fas",
+  "beast2.xml",
   tree_priors = create_yule_tree_prior(
@@
 Novel about \verb;beautier; is that it allows for specifying a fixed crown age. 
-By default, a phylogeny's crown age is jointly estimated with the other parameters.
+By default, a phylogeny's crown age is jointly-estimated with the other parameters.
 Setting a fixed crown age is not yet possible in BEAUti directly, but it is documented how to 
-manually edit the XML file to allow for a fixed crown age. Listing \ref{lst:fixed_crown_age} shows how to specify a fixed crown age with \verb;beautier;:
+manually edit the XML file to allow for a fixed crown age. 
+Listing \ref{lst:fixed_crown_age} shows how to specify a fixed crown age with \verb;beautier;:
 
@@
 
-\verb;beautier;'s development takes place on GitHub \cite{github}. 
-GitHub is a website that hosts (among others) software and facilitates its development.
-Using GitHub is a good practice for computational scientists \cite{perez2016ten} 
+\verb;beautier;'s development takes place on GitHub \cite{github}, 
+which is a good practice for computational scientists \cite{perez2016ten} 
 and improves transparency \cite{gorgolewski2016practical}.
 
-\verb;beautier;'s quality is assured by Travis CI \cite{travis}. Travis CI is
-a continuous integration service, that runs a script upon a (suggested)
-change in \verb;beautier;'s code. The \verb;beautier; script checks if the
-package can be build, runs all unit and integration tests, 
-measures code coverage, coding style and good practices.
-
-Unit and integration tests check the integrity of \verb;beatier;. All functions
-are tested for producing the correct output and desired error handling. 
-Travis CI uses the testing facilities of the \verb;testthat; \cite{testthat} package.
-
-Code coverage is the percentage of code that is executed in tests. 
-Code coverage correlates with code quality \cite{del1995correlation}. 
-Travis CI uses the \verb;covr; \cite{covr} package to measure code coverage. 
-\verb;beautier; has a 100\% code coverage.
-
-Coding style is the way statements are laid out, for example the placement of 
-curly brackets. \verb;beautier; follows Hadley Wickham's style guide \cite{style_guide}. 
-Travis CI uses the \verb;lintr; \cite{lintr} package to confirm this coding style
-is used.
-
-Good practices are miscellaneous things considered good practices. An example
-of a good practice is (next to high code coverage and consistent coding style) 
-to have short functions with a low cyclomatic complexity. Travis CI uses 
-the \verb;goodpractice; \cite{goodpractice} package to comfirm all good practices
-are followed.
+\verb;beautier;'s uses the Travis CI \cite{travis} 
+continuous integration service, which is known to significantly 
+increase the the number of bugs exposed \cite{vasilescu2015}.
+\verb;beautier; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
+\verb;beautier; follows Hadley Wickham's style guide \cite{style_guide}, which improves software quality \cite{fang2001}.
 
@@
 \verb;APE; \cite{APE}, 
+\verb;beastier; \cite{beastier},
 \verb;devtools; \cite{devtools},
@@
 \verb;knitr; \cite{knitr},
+\verb;lumier; \cite{lumier},
 \verb;phangorn; \cite{phangorn},
-\verb;beastier; \cite{beastier},
 \verb;rmarkdown; \cite{rmarkdown},
@@
 Additionally, \verb;beautier; has a vignette that demonstrates in a longer form how
-to use it. The integrity of this documentation is tested each time the package is built by Travis CI.
-The documentation on the GitHub helps to get started, with a dozen examples 
+to use it. The integrity of this documentation is tested by Travis CI.
+The GitHub documentation helps to get started, with a dozen examples 
 of a BEAUti screenshot and the equivalent \verb;beautier; code.
 
-\verb;beautier;'s GitHub facilitates feature requests and guidelines how to do so.
-New code can be submitted using GitHub's infrastructure (a 'Pull Request'). New
-code will be tested by Travis CI to follow the same quality standards and only accepted
-when there are no
+\verb;beautier;'s GitHub facilitates feature requests and has guidelines how to do so.
+Thanks to Travis CI, newly submitted code is expected to be accepted quicker \cite{vasilescu2015}.
 
@@
 \end{document}
+\grid

### 2018-01-18 article.tex
EOD

@@
 
+% Thanks Raphael Scherrer
+\usepackage[switch]{lineno}
+
 \begin{document}
@@
 
+% TODO: RS: Rename to 'Summary 
 \begin{abstract}
   \textbf{1. }
-  Here, we present a package, \verb;beautier;, 'BEAUti for R', for the R programming language. \\
+    Here, we present a free, libre and open-source package, \verb;beautier;, 
+    'BEAUti for R', for the R programming language. \\
   \textbf{2. }
@@
   \textbf{3. }
-    We describe \verb;beautier; usage, the novel functionality it provides
+    We describe \verb;beautier;'s usage, the novel functionality it provides
     compared to BEAUti, and give some minimal examples. \\
   \textbf{4. }
-    As \verb;beautier; is free, libre, open-source and designed to be extended, 
-    We conclude by describing the current development of the package \\
+    As \verb;beautier; is designed to be of high quality and extendable, 
+    we conclude by describing the development of the package \\
 \end{abstract}
 
+% TODO: RS: Get these keywords visualized
 % Key-words: computational biology, evolution, phylogeny, BEAST2, R
@@
 BEAST2 \cite{bouckaert2014beast} is a Bayesian phylogenetics tool.
-BEAST2 creates a posterior of jointly-estimated phylonies and model
-parameters, from a DNA, RNA or amino acid alignment. BEAST2 is a 
+BEAST2 creates a posterior of jointly-estimated phylogenies and model
+parameters, from a DNA, RNA or amino acid alignment (see figure \ref{fig:workflow} for an overview
+of the workflow). BEAST2 is a 
 console application, that needs a configuration file containing alignments and model parameters.
 
-BEAST2 is bundled with the BEAUti \cite{drummond2012bayesian}. 
+BEAST2 is bundled with BEAUti \cite{drummond2012bayesian}. 
 BEAUti is a program to create a BEAST2 XML configuration file, 
@@
 BEAUti cannot be called from a command-line script, which is not a problem in all cases.
-For example, the BEAST book \cite{drummond2015bayesian} encourages to first infer a posterior
-from simpler models first, then exploring if adding complexity changes the inferred results.
-This can easily be done manually using BEAUti. 
-For bigger theoretical explorations (for example, using thousands of simulated alignments), this approach
-becomes inviable.
+For example, the BEAST book \cite{drummond2015bayesian} encourages a stepwise approach: 
+(1) infer a posterior from the simplest models possible, (2) while a posterior with a more complex model gives
+a different posterior, increase complexity. This can be done manually using BEAUti and is the common workflow
+when using a few alignments and doing a superficial search through model space.
 
@@
 to create configuration files from shell scripts.
+Using \verb;beautier; will save you time and thousands of mouse clicks.
+\verb;beautier; brings deep exploration of model space within reach,
+as you can loop through multiple (simulated) alignments, 
+nucleotide substitution models, clock models and tree priors.
 
@@
   \caption{
-    Workflow. From an alignment and priors, one creates a BEAST2 XML input file. This
+    Workflow. From an alignment and priors (depicted as a thought cloud), one creates a BEAST2 XML input file. This
     can be done using beautier or BEAUti. The created configuration file is run by lumier or BEAST2
@@
 \verb;beautier;'s main function is \verb;create_beast2_input_file;, which creates
-an BEAST2 input file. \verb;create_beast2_input_file; needs at least the name of a FASTA file containing a DNA alignment
+a BEAST2 input file. \verb;create_beast2_input_file; needs at least the name of a FASTA file containing a DNA alignment
 and a name for the to-be-created output file. This interface follows BEAUti's default settings.
-Per alignment, a site model, clock model and tree priors can be chosen.
+Per alignment, a site model, clock model and tree prior can be chosen.
 Multiple alignments can be used, each with its own (unlinked) site model, clock model and tree prior.
@@
 a BEAST2 configuration file. \verb;beautier; is an alternative for a majority of BEAUti use cases.
-\verb;beautier; does not support the full functionality of BEAUti. Considering
-BEAUti's flexibility and number of plugins, this would be a Herculean effort.
-To compensate for this, an extensible software architecture is used.
-\verb;beautier;s future extensions can be found on its GitHub.
+\verb;beautier; does not support the full functionality of BEAUti. 
+Because of its high number of plugins, an extensible software architecture is used.
+A roadmap of \verb;beautier;'s future extensions can be found on its GitHub.
 
@@
 with the phylogeny and other parameters. BEAUti does not allow for fixing
-a phylogeny's crown age. Before \verb;beautier;, one needs to manually edit the BEAST2 
+a phylogeny's crown age. Without \verb;beautier;, one needs to manually edit the BEAST2 
 XML configuration file, which is prone to errors. \verb;beautier;, allows easy
@@
 
-\verb;beastier; and \verb;lumier; are related packages, used in testing. 
-\verb;lumier; calls BEAST2 from within R. \verb;lumier; is used to confirm that the XML files 
+\verb;beastier; and \verb;lumier; are related packages, which are used to confirm the correct
+working of verb;beautier;. \verb;lumier; calls BEAST2 from within R and is used to confirm that the XML files 
 created by \verb;beautier; are valid. Additionally, \verb;lumier; is used to run BEAST2
@@
 
-In R, a package's function need to be loaded in the global namespace first:
+In R, a package's function needs to be loaded in the global namespace first:
 
@@
 
-BEAUti, and likewise \verb;beautier;, need at least a FASTA filename
+BEAUti, and likewise \verb;beautier;, needs at least a FASTA filename
 and an XML output filename. In BEAUti, this is achieved by loading a FASTA file (resulting
@@
 One may prefer to have an exponential distribution instead, as this would state that birth rates are always positive, and
-higher values are less likely than lower values. To do so \verb;beautier; is shown by listing \ref{lst:diff_distr}:
+higher values are less likely to occur than lower values. 
+Listing \ref{lst:diff_distr} shows how to do so in \verb;beautier;:
 
@@
 
-Novel about \verb;beautier; is that it allows for specifying a fixed crown age. 
+Novel functionality that \verb;beautier; offers, is that it allows for specifying a fixed crown age. 
 By default, a phylogeny's crown age is jointly-estimated with the other parameters.
@@
 \verb;beautier;'s development takes place on GitHub \cite{github}, 
-which is a good practice for computational scientists \cite{perez2016ten} 
-and improves transparency \cite{gorgolewski2016practical}.
+facilitating collaboration \cite{perez2016ten} 
+and improving transparency \cite{gorgolewski2016practical}.
 

### 2018-01-18 article.tex
Collect feedback

@@
 
-Scientists using \verb;beautier; in a published paper should cite this
-article. Users can additionally cite the \verb;beautier; package 
-directly. Citation information can be obtained by typing:
+Scientists using \verb;beautier; in a published paper can cite this
+article, or cite the \verb;beautier; package 
+directly. To obtain this citation from within an R script, use:
 
@@
 \end{lstlisting}
-
-from within R.
 

### 2018-01-18 article.tex
Before sending to @RSEtienne

@@
 \documentclass{article}
+
+\title{beautier: BEAUti for R}
+\author{Rich\`el J.C. Bilderbeek, Rampal S. Etienne}
 
@@
 
-% \newcommand*\beautier{\verb;beautier;}
-
-\title{beautier: BEAUti for R}
-\author{Rich\`el J.C. Bilderbeek, Rampal S. Etienne}
-
-% \newcommand*\filename[1]{${#1}$}
-% \newcommand*\myfilename[1]{\verb;{#1};}
-
-% Style of code
+% Style of listings
 % From http://r.789695.n4.nabble.com/How-to-nicely-display-R-code-with-the-LaTeX-package-listings-tp4648110.html
@@
 
-% Thanks Raphael Scherrer
-\usepackage[switch]{lineno}
+% Adds numbered lines, thanks to Raphael Scherrer
+% \usepackage[switch]{lineno}
 
@@
 % TODO: RS: Rename to 'Summary 
+% https://tex.stackexchange.com/a/24778 does not work:
+% \addto{\captionsenglish}{\renewcommand{\abstractname}{Summary}}
+
 \begin{abstract}
@@
 
-Phylogenies are a commonly used tool to explore evolutionary hypotheses.
-Not only can phylogenies tell us how species relate to each other, also relevant parameters like
-extinction and speciation rates can be estimated from them.
+Phylogenies are commonly used to explore evolutionary hypotheses.
+Not only can phylogenies show us how species relate to each other, 
+also relevant parameters like extinction and speciation rates can be estimated from them.
 
 BEAST2 \cite{bouckaert2014beast} is a Bayesian phylogenetics tool.
-BEAST2 creates a posterior of jointly-estimated phylogenies and model
-parameters, from a DNA, RNA or amino acid alignment (see figure \ref{fig:workflow} for an overview
-of the workflow). BEAST2 is a 
-console application, that needs a configuration file containing alignments and model parameters.
+BEAST2 creates a posterior of jointly-estimated phylogenies and model parameters, 
+from a DNA, RNA or amino acid alignment (see figure \ref{fig:workflow} for an overview of the workflow). 
+BEAST2 is a console application, that needs a configuration file containing alignments and model parameters.
 
-BEAST2 is bundled with BEAUti \cite{drummond2012bayesian}. 
-BEAUti is a program to create a BEAST2 XML configuration file, 
-using a user-friendly graphical user interface, with helpful and reasonable 
-default settings. BEAUti replaces the manual editing of the BEAST2 XML
-files.
+BEAST2 is bundled with BEAUti \cite{drummond2012bayesian}, a desktop application to create a BEAST2 configuration file.
+BEAUti has a user-friendly graphical user interface, with helpful and reasonable default settings.
+As such, BEAUti is an attractive alternative to the manual and error-prone editing of BEAST2 configuration files.
 
 BEAUti cannot be called from a command-line script, which is not a problem in all cases.
-For example, the BEAST book \cite{drummond2015bayesian} encourages a stepwise approach: 
+One workflow that is already viable can be found in the BEAST book \cite{drummond2015bayesian}:
 (1) infer a posterior from the simplest models possible, (2) while a posterior with a more complex model gives
@@
 creates BEAST2 configuration files from an R function call.
-The interface of \verb;beautier; mimics BEAUti and is easy to use. This
-familiar interface helps both beginner and experienced BEAST2 users 
-to create configuration files from shell scripts.
-Using \verb;beautier; will save you time and thousands of mouse clicks.
 \verb;beautier; brings deep exploration of model space within reach,
@@
 nucleotide substitution models, clock models and tree priors.
+Using \verb;beautier; will save time and tedious mouse clicking.
+The interface of \verb;beautier; mimics BEAUti. This
+familiarity helps both beginner and experienced BEAST2 users 
+to create configuration files using \verb;beautier;.
 
@@
 
-\verb;beautier; is written in the R programming language \cite{R}.
-\verb;beautier; creates the BEAST2 input files from an R function call,
+\verb;beautier; is written in the R programming language \cite{R}
+and creates a BEAST2 configuration file from an R function call,
 in a similar way that BEAUti does.
 
-\verb;beautier;'s main function is \verb;create_beast2_input_file;, which creates
-a BEAST2 input file. \verb;create_beast2_input_file; needs at least the name of a FASTA file containing a DNA alignment
-and a name for the to-be-created output file. This interface follows BEAUti's default settings.
+\verb;beautier;'s main function is \verb;create_beast2_input_file;, which creates a BEAST2 configuration file. 
+\verb;create_beast2_input_file; needs at least the name of a FASTA file containing a DNA alignment
+and a name for the to-be-created configuration file. 
+This interface follows BEAUti's default settings.
 Per alignment, a site model, clock model and tree prior can be chosen.
@@
 
-In total, \verb;beautier; has 59 exported functions to create
-a BEAST2 configuration file. \verb;beautier; is an alternative for a majority of BEAUti use cases.
-\verb;beautier; does not support the full functionality of BEAUti. 
-Because of its high number of plugins, an extensible software architecture is used.
+In total, \verb;beautier; has 61 exported functions to create a BEAST2 configuration file. 
+\verb;beautier; is an alternative for a majority of BEAUti use cases, 
+but does not support the full functionality of BEAUti. 
+Because of BEAUti's high number of plugins, \verb;beautier; uses an extensible software architecture.
 A roadmap of \verb;beautier;'s future extensions can be found on its GitHub.
@@
 a phylogeny's crown age. Without \verb;beautier;, one needs to manually edit the BEAST2 
-XML configuration file, which is prone to errors. \verb;beautier;, allows easy
-fixing of phylogenies' crown ages. For theoretical work, a fixed and known crown age can result
-in a cleaner analysis.
+XML configuration file, which is tedious and prone to errors. 
+\verb;beautier;, allows for easy setting of a fixed crown age, which allows for theoretical experiments with one less source of variation.
 
-\verb;beastier; and \verb;lumier; are related packages, which are used to confirm the correct
-working of verb;beautier;. \verb;lumier; calls BEAST2 from within R and is used to confirm that the XML files 
-created by \verb;beautier; are valid. Additionally, \verb;lumier; is used to run BEAST2
-to create posteriors. Using \verb;beastier;, these posteriors are checked to have an
-estimated or fixed crown age.
+\verb;beastier; \cite{beastier} and \verb;lumier; \cite{lumier} are related packages, used to confirm the correct working of verb;beautier;.
+\verb;lumier; calls BEAST2 from within R and is used to confirm that the XML files created by \verb;beautier; are valid. 
+Additionally, \verb;lumier; is used to run BEAST2 to create posteriors. 
+\verb;beastier; can parse BEAST2 posteriors, and is used to confirm whether posteriors have an estimated or fixed crown age.
 
@@
 
-In R, a package's function needs to be loaded in the global namespace first:
+In R, a package's functions need to be loaded in the global namespace first:
 
@@
 BEAUti, and likewise \verb;beautier;, needs at least a FASTA filename
-and an XML output filename. In BEAUti, this is achieved by loading a FASTA file (resulting
+and an output filename. In BEAUti, this is achieved by loading a FASTA file (resulting
 in figure \ref{fig:simplest_beauti_usage}), then saving an output file using a common
@@
 
-This code will create a BEAST2 file with name '\verb;beast2.xml;',
+This code will create a BEAST2 configuration file with name '\verb;beast2.xml;',
 using a FASTA file with name \verb;alignment.fas;, using the same default settings as BEAUti.
@@
 
-The argument names \verb;site_models;, \verb;clock_models; and \verb;tree_priors; are plural, as each of these
+The arguments' names \verb;site_models;, \verb;clock_models; and \verb;tree_priors; are plural, as each of these
 can be (a list of) one or more elements. Each of these arguments must have the same number of elements, so that each alignment has its
@@
 
-\verb;beautier; creates site models, clock models and tree priors with the same default distributions as BEAUti.
-For example, a Yule tree prior assumes that birth rate likelihoods follow a uniform distribution, from minus infinity
-to infinity. This assumption entails that negative and positive birth rates are just as likely, where a negative birth rate is biologically impossible. 
-One may prefer to have an exponential distribution instead, as this would state that birth rates are always positive, and
-higher values are less likely to occur than lower values. 
+\verb;beautier; also uses the same default distributions as BEAUti for the site models, clock models and tree priors. 
+For example, a Yule tree prior assumes that birth rate likelihoods follow a uniform distribution, from minus infinity to infinity. 
+This assumption entails that negative and positive birth rates are just as likely, 
+where a negative birth rate is biologically impossible\footnote{note that in practice, this works out just fine}.
+One may prefer an exponential distribution instead, as this would assume only positive birth rates, 
+and unlikely high birth rates.
+
 Listing \ref{lst:diff_distr} shows how to do so in \verb;beautier;:
@@
 \verb;beautier; is free, libre and open source software available from the official R package archive at 
-\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#beautier}.  
-\verb;beautier; is licensed under the GNU General Public License.
+\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#beautier}
+and is licensed under the GNU General Public License v3.0.
 
 \verb;beautier;'s development takes place on GitHub \cite{github}, 
-facilitating collaboration \cite{perez2016ten} 
-and improving transparency \cite{gorgolewski2016practical}.
+which facilitates collaboration \cite{perez2016ten} 
+and improves transparency \cite{gorgolewski2016practical}.
+\verb;beautier;'s GitHub facilitates feature requests and has a guidelines how to do so.
 
@@
 continuous integration service, which is known to significantly 
-increase the the number of bugs exposed \cite{vasilescu2015}.
+increase the the number of bugs exposed \cite{vasilescu2015} and increases
+the speed at which new features are added \cite{vasilescu2015}.
 \verb;beautier; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
@@
 Additionally, \verb;beautier; has a vignette that demonstrates in a longer form how
-to use it. The integrity of this documentation is tested by Travis CI.
-The GitHub documentation helps to get started, with a dozen examples 
+to use it. The GitHub documentation helps to get started, with a dozen examples 
 of a BEAUti screenshot and the equivalent \verb;beautier; code.
-
-\verb;beautier;'s GitHub facilitates feature requests and has guidelines how to do so.
-Thanks to Travis CI, newly submitted code is expected to be accepted quicker \cite{vasilescu2015}.
 

### 2018-01-23 article.tex
Before sending to @RSEtienne
Implemented feedback RSE

@@
 \begin{abstract}
+
   \textbf{1. }
+    In the field of phylogenetics, 
+     BEAST2 is one of the most widely used software tools. 
+     It comes with the graphical program BEAUti to 
+     facilitate the creation of input files to BEAST2. 
+     However, when many input files are needed, 
+     such a GUI is cumbersome. 
+     Moreover, many other phygenetics tools are available 
+     in R, which requires switching from one platform 
+     to the other. \\
+  \textbf{2. }
     Here, we present a free, libre and open-source package, \verb;beautier;, 
-    'BEAUti for R', for the R programming language. \\
-  \textbf{2. }
-    \verb;beautier; allows for scripted use of the BEAST2 phylogenetics tool, 
-    by creating BEAST2 input files from an R function call. \\
+    'BEAUti for R', for the R programming language. 
+    \verb;beautier; creates BEAST2 input files 
+    from an R function call. \\
   \textbf{3. }
     We describe \verb;beautier;'s usage, the novel functionality it provides
-    compared to BEAUti, and give some minimal examples. \\
+    compared to BEAUti, and give some examples. \\
   \textbf{4. }
     As \verb;beautier; is designed to be of high quality and extendable, 
-    we conclude by describing the development of the package \\
+    we conclude by describing the further development of the package \\
 \end{abstract}
@@
 Phylogenies are commonly used to explore evolutionary hypotheses.
-Not only can phylogenies show us how species relate to each other, 
-also relevant parameters like extinction and speciation rates can be estimated from them.
+Not only can phylogenies show us how species (or other
+evoliutionary units) relate to each other, 
+but also relevant parameters like extinction and 
+speciation rates can be estimated from them.
 
-BEAST2 \cite{bouckaert2014beast} is a Bayesian phylogenetics tool.
-BEAST2 creates a posterior of jointly-estimated phylogenies and model parameters, 
-from a DNA, RNA or amino acid alignment (see figure \ref{fig:workflow} for an overview of the workflow). 
-BEAST2 is a console application, that needs a configuration file containing alignments and model parameters.
+There are many phylogenetics tools available to obtain an estimate 
+of the phylogenetic tree of a given set of species. 
+BEAST2 \cite{bouckaert2014beast} is one of the most widely used ones. 
+It creates a posterior of jointly-estimated phylogenies and model parameters, 
+from a DNA, RNA or amino acid alignment (see figure \ref{fig:workflow} 
+for an overview of the workflow). 
+It is a console application, that needs a configuration file containing alignments and model parameters.
 
-BEAST2 is bundled with BEAUti \cite{drummond2012bayesian}, a desktop application to create a BEAST2 configuration file.
+BEAST2 is bundled with BEAUti 2 \cite{drummond2012bayesian} ('BEAUti' from now on), 
+a desktop application to create a BEAST2 configuration file.
 BEAUti has a user-friendly graphical user interface, with helpful and reasonable default settings.
-As such, BEAUti is an attractive alternative to the manual and error-prone editing of BEAST2 configuration files.
+As such, BEAUti is an attractive alternative 
+to manual and error-prone editing of BEAST2 configuration files.
 
-BEAUti cannot be called from a command-line script, which is not a problem in all cases.
-One workflow that is already viable can be found in the BEAST book \cite{drummond2015bayesian}:
-(1) infer a posterior from the simplest models possible, (2) while a posterior with a more complex model gives
-a different posterior, increase complexity. This can be done manually using BEAUti and is the common workflow
-when using a few alignments and doing a superficial search through model space.
+BEAUti cannot be called from a command-line script.
+This implies that when the user 
+wants to explore the consequences of various settings, this must be done manually.
+This is the common workflow when using a few alignments and doing a superficial 
+analysis of sensitivity of the reconstructed tree to model settings.
 
-Here, we present \verb;beautier;, 'BEAUti for R', which 
-creates BEAST2 configuration files from an R function call.
-\verb;beautier; brings deep exploration of model space within reach,
-as you can loop through multiple (simulated) alignments, 
-nucleotide substitution models, clock models and tree priors.
-Using \verb;beautier; will save time and tedious mouse clicking.
+However, for exploring many trees (for instance from simulations) and for
+more thorough sensitivity analysis, one would like to loop through 
+multiple (simulated) alignments, nucleotide substitution models, 
+clock models and tree priors.
+
+Here, to provide such functionality we present \verb;beautier;, 
+’BEAUti for R’, which creates BEAST2 configuration files 
+from an R function call and hence
+will save time and tedious mouse clicking and 
+reduces the chances of errors in such repetitive actions.
 The interface of \verb;beautier; mimics BEAUti. This
@@
 to create configuration files using \verb;beautier;.
+Because there are many R packages for exploring the 
+resulting phylogenetic trees, 
+\verb;beautier; enables the creation of a single-script 
+pipeline from sequence alignments to tree analysis in R.
+
+\verb;beautier; has a similar goal as \verb;BEASTmasteR; \cite{beastmaster} (still
+in pre-release), as both
+allow for scripted use of BEAST2. The difference is that \verb;beautier; 
+has its focus on DNA alignments and ultrametric trees, 
+where \verb;BEASTmasteR; is used for 
+morphologucal traits and tip-dating.
 
@@
         (A) edge [anchor = west] node {\includegraphics[height=0.15\textheight]{BeautiSiteModel.png}} (E)
-        (E) edge [anchor = east] node {\includegraphics[width=0.25\textwidth]{lumier_logo_big.png}} (F) 
+        % (E) edge [anchor = east] node {\includegraphics[width=0.25\textwidth]{lumier_logo_big.png}} (F) 
         (E) edge [anchor = west] node {\includegraphics[width=0.2\textwidth]{beast_logo.png}} (F); 
@@
     Workflow. From an alignment and priors (depicted as a thought cloud), one creates a BEAST2 XML input file. This
-    can be done using beautier or BEAUti. The created configuration file is run by lumier or BEAST2
+    can be done using beautier or BEAUti. The created configuration file is run by BEAST2
     to create a posterior of phylogenies and model parameter estimates.
@@
 
-\verb;beautier;'s main function is \verb;create_beast2_input_file;, which creates a BEAST2 configuration file. 
-\verb;create_beast2_input_file; needs at least the name of a FASTA file containing a DNA alignment
+\verb;beautier;'s main function is \verb;create_beast2_input_file;, which, 
+as the name suggests, creates a BEAST2 configuration file. 
+\verb;create_beast2_input_file; needs at least the name of a 
+FASTA file containing a DNA alignment
 and a name for the to-be-created configuration file. 
-This interface follows BEAUti's default settings.
+The default settings for the other arguments of \verb;create_beast2_input_file; 
+are identical to BEAUti's default settings.
 Per alignment, a site model, clock model and tree prior can be chosen.
 Multiple alignments can be used, each with its own (unlinked) site model, clock model and tree prior.
+
+\verb;beautier; currently has 61 exported functions to create a BEAST2 configuration file. 
+\verb;beautier; is an alternative for a majority of BEAUti use cases, 
+but does not yet support the full functionality of BEAUti. 
+Because of BEAUti's high number of plugins, 
+\verb;beautier; uses a software architecture that expects te be extended.
+
+\verb;beastier; \cite{beastier} and \verb;lumier; \cite{lumier} are related packages, used to confirm the correct working of verb;beautier;.
+\verb;lumier; calls BEAST2 from within R and is used to confirm that the XML files created by \verb;beautier; are valid. 
+Additionally, \verb;lumier; is used to run BEAST2 to create posteriors. 
+\verb;beastier; can parse BEAST2 posteriors, and is used to confirm whether posteriors have an estimated or fixed crown age.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Examples}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In R, the functions of a package need to be loaded in the global namespace first:
+
+\begin{lstlisting}[language=R, caption=Loading, label=lst:loading_beautier, floatplacement=H]
+library(beautier)
+\end{lstlisting}
+
+BEAUti, and likewise \verb;beautier;, needs at least a FASTA filename
+and an output filename. In BEAUti, this is achieved by loading a FASTA file, 
+then saving an output file using a common
+save file dialog. In \verb;beautier;, the same is achieved by:
+
+\begin{lstlisting}[language=R, caption=Simplest example, label=lst:simplest_example, floatplacement=H]
+create_beast2_input_file(
+  "alignment.fas",
+  "beast2.xml"
+)
+\end{lstlisting}
+
+This code will create a BEAST2 configuration file with name '\verb;beast2.xml;',
+using a FASTA file with name \verb;alignment.fas;, using the same default settings as BEAUti.
+The default settings are, among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
+a strict clock, and a Yule birth tree prior \cite{yule}.
+
+An example of using a different site model, clock model 
+and tree prior is:
+
+\begin{lstlisting}[language=R, caption=Example with different site model and clock model and tree prior, label=lst:all_different, floatplacement=H]
+library(beautier)
+create_beast2_input_file(
+  "alignment.fas",
+  "beast2.xml",
+  site_models = create_hky_site_model(),
+  clock_models = create_rln_clock_model(),
+  tree_priors = create_bd_tree_prior()
+)
+\end{lstlisting}
+
+This code uses an HKY site model, a relaxed log-normal clock model and a 
+birth-death tree prior, each with their default settings in BEAUti.
+Table \ref{tab:functions} shows an overview of all functions to create site models, clock models and tree priors.
 
@@
 \hline
-\verb;create_gtr_site_model; & Create a GTR site model \cite{tavare1986some} \\
-\verb;create_hky_site_model; & Create an HKY site model \cite{hasegawa1985dating} \\
-\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \cite{cantor1969mammalian} \\
-\verb;create_tn93_site_model; & Create a TN93 site model \cite{tamura1993estimation} \\
+\verb;create_gtr_site_model; & Create a GTR site model \\
+\verb;create_hky_site_model; & Create an HKY site model \\
+\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
+\verb;create_tn93_site_model; & Create a TN93 site model \\
 \hline
-\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \cite{drummond2006relaxed} \\
-\verb;create_strict_clock_model; & Create a strict clock model \cite{sarich1967immunological} \\
+\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
+\verb;create_strict_clock_model; & Create a strict clock model \\
 \hline
-\verb;create_bd_tree_prior; & Create a birth-death tree prior \cite{kendall1948generalized} \\
+\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
 \verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
@@
 \verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
-\verb;create_yule_tree_prior; & Create a Yule tree prior \cite{yule} \\
+\verb;create_yule_tree_prior; & Create a Yule tree prior \\
 \hline
@@
 \end{tabular}
-\caption{beautier's functions}
+\caption{beautier's main functions}
 \label{tab:functions}
@@
 
-In total, \verb;beautier; has 61 exported functions to create a BEAST2 configuration file. 
-\verb;beautier; is an alternative for a majority of BEAUti use cases, 
-but does not support the full functionality of BEAUti. 
-Because of BEAUti's high number of plugins, \verb;beautier; uses an extensible software architecture.
-A roadmap of \verb;beautier;'s future extensions can be found on its GitHub.
+Note that the arguments' names \verb;site_models;, \verb;clock_models; and \verb;tree_priors; are plural, as each of these
+can be (a list of) one or more elements. Each of these arguments must have the same number of elements, so that each alignment has its
+own site model, clock model and tree prior.
 
-BEAUti assumes that a phylogeny has a crown age that needs to be jointly-estimated
-with the phylogeny and other parameters. BEAUti does not allow for fixing
-a phylogeny's crown age. Without \verb;beautier;, one needs to manually edit the BEAST2 
-XML configuration file, which is tedious and prone to errors. 
-\verb;beautier;, allows for easy setting of a fixed crown age, which allows for theoretical experiments with one less source of variation.
+An example of two alignments, each with its own site model, is:
 
-\verb;beastier; \cite{beastier} and \verb;lumier; \cite{lumier} are related packages, used to confirm the correct working of verb;beautier;.
-\verb;lumier; calls BEAST2 from within R and is used to confirm that the XML files created by \verb;beautier; are valid. 
-Additionally, \verb;lumier; is used to run BEAST2 to create posteriors. 
-\verb;beastier; can parse BEAST2 posteriors, and is used to confirm whether posteriors have an estimated or fixed crown age.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Examples}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In R, a package's functions need to be loaded in the global namespace first:
-
-\begin{lstlisting}[language=R, caption=Loading, label=lst:loading_beautier, floatplacement=H]
+\begin{lstlisting}[language=R, caption=Two alignments, label=lst:two_alignments, floatplacement=H]
 library(beautier)
-\end{lstlisting}
-
-BEAUti, and likewise \verb;beautier;, needs at least a FASTA filename
-and an output filename. In BEAUti, this is achieved by loading a FASTA file (resulting
-in figure \ref{fig:simplest_beauti_usage}), then saving an output file using a common
-save file dialog. In \verb;beautier;, the same is achieved by listing \ref{lst:simplest_example}:
-
-\begin{lstlisting}[language=R, caption=Simplest example, label=lst:simplest_example, floatplacement=H]
-library(beautier)
-create_beast2_input_file(
-  "alignment.fas",
-  "beast2.xml"
+beautier::create_beast2_input_file(
+  c("anthus_aco.fas", "anthus_nd2.fas"),
+  "beast2.xml",
+  site_models = list(
+    create_tn93_site_model(), 
+    create_gtr_site_model()
+  )
 )
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{all_default.png}
-  \caption{Simplest BEAUti usage}
-  \label{fig:simplest_beauti_usage}
-\end{figure}
+\verb;beautier; also uses the same default distributions as BEAUti 
+for the site models, clock models and tree priors. 
+For example, a Yule tree prior assumes the birth rate follows a uniform distribution, 
+from minus infinity to plus infinity. 
+This assumption implies that negative and positive birth rates are just as likely, 
+where a negative birth rate is biologically impossible (note that 
+in practice, this usually works out just fine).
+One may prefer an exponential distribution instead, 
+as this would assume only positive birth rates, 
+and makes high birth rates unlikely.
 
-This code will create a BEAST2 configuration file with name '\verb;beast2.xml;',
-using a FASTA file with name \verb;alignment.fas;, using the same default settings as BEAUti.
-The default settings are, among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
-a strict clock, and a Yule birth tree prior \cite{yule}.
-
-An example of using a different site model, clock model and tree prior is shown by listing \ref{lst:all_different}:
-
-\begin{lstlisting}[language=R, caption=Example with different site model and clock model and tree prior, label=lst:all_different, floatplacement=H]
-library(beautier)
-create_beast2_input_file(
-  "alignment.fas",
-  "beast2.xml",
-  site_models = create_hky_site_model(),
-  clock_models = create_rln_clock_model(),
-  tree_priors = create_bd_tree_prior()
-)
-\end{lstlisting}
-
-This code uses an HKY site model, a relaxed log-normal clock model and a birth-death tree prior \cite{kendall1948generalized}.
-Table \ref{tab:functions} shows an overview of all functions to create site models, clock models and tree priors.
-
-The arguments' names \verb;site_models;, \verb;clock_models; and \verb;tree_priors; are plural, as each of these
-can be (a list of) one or more elements. Each of these arguments must have the same number of elements, so that each alignment has its
-own site model, clock model and tree prior.
-
-\verb;beautier; also uses the same default distributions as BEAUti for the site models, clock models and tree priors. 
-For example, a Yule tree prior assumes that birth rate likelihoods follow a uniform distribution, from minus infinity to infinity. 
-This assumption entails that negative and positive birth rates are just as likely, 
-where a negative birth rate is biologically impossible\footnote{note that in practice, this works out just fine}.
-One may prefer an exponential distribution instead, as this would assume only positive birth rates, 
-and unlikely high birth rates.
-
-Listing \ref{lst:diff_distr} shows how to do so in \verb;beautier;:
+The following script shows how to do this in \verb;beautier;:
 
@@
 
-Novel functionality that \verb;beautier; offers, is that it allows for specifying a fixed crown age. 
-By default, a phylogeny's crown age is jointly-estimated with the other parameters.
-Setting a fixed crown age is not yet possible in BEAUti directly, but it is documented how to 
+% TODO: Mix sentences better
+Our initial motivation to create \verb;beautier; 
+is that we wanted to fix the crown age of a phylogeny, but because 
+BEAUti assumes that a phylogeny has a crown age that needs to be jointly-estimated
+with the phylogeny and other parameters. it does not allow for fixing
+the crown age. Without \verb;beautier;, one needs to manually edit the BEAST2 
+XML configuration file, which is tedious and prone to errors. 
+\verb;beautier;, allows for easy setting of a fixed crown age, 
+enabling theoretical experiments with one less source of variation. 
+Setting a fixed crown age is not yet possible in BEAUti directly, 
+but the BEAUti documentation mentions how to 
 manually edit the XML file to allow for a fixed crown age. 
-Listing \ref{lst:fixed_crown_age} shows how to specify a fixed crown age with \verb;beautier;:
+This is how to specify a fixed crown age with \verb;beautier;:
 
@@
 
-\verb;beautier;'s development takes place on GitHub \cite{github}, 
-which facilitates collaboration \cite{perez2016ten} 
-and improves transparency \cite{gorgolewski2016practical}.
-\verb;beautier;'s GitHub facilitates feature requests and has a guidelines how to do so.
-
-\verb;beautier;'s uses the Travis CI \cite{travis} 
+\verb;beautier; uses the Travis CI \cite{travis} 
 continuous integration service, which is known to significantly 
@@
 \verb;beautier; follows Hadley Wickham's style guide \cite{style_guide}, which improves software quality \cite{fang2001}.
-
 \verb;beautier; is dependent on multiple packages, which are 
@@
 
-\verb;beautier;'s documentation is extensive, yet concise. All functions are documented
+\verb;beautier;'s development takes place on GitHub \cite{github},
+\url{https://github.com/richelbilderbeek/beautier}, 
+which accomodates collaboration \cite{perez2016ten} 
+and improves transparency \cite{gorgolewski2016practical}.
+\verb;beautier;'s GitHub facilitates feature requests and has a guidelines how to do so.
+
+\verb;beautier;'s documentation is extensive. All functions are documented
 in the package's internal documentation. For quick use, each exported function shows a minimal example. 
 For easy exploration, each exported function's documentation links to related functions.
-Additionally, \verb;beautier; has a vignette that demonstrates in a longer form how
+Additionally, \verb;beautier; has a vignette that demonstrates extensively how
 to use it. The GitHub documentation helps to get started, with a dozen examples 
-of a BEAUti screenshot and the equivalent \verb;beautier; code.
+of BEAUti screenshots with equivalent \verb;beautier; code.
+
+A roadmap of \verb;beautier;'s future extensions can be found on its GitHub.
 
@@
 Scientists using \verb;beautier; in a published paper can cite this
-article, or cite the \verb;beautier; package 
+article, and/or cite the \verb;beautier; package 
 directly. To obtain this citation from within an R script, use:

### 2018-01-29 article.tex
beastier logo

@@
 
-\title{beautier: BEAUti for R}
+\title{babette: BEAUti, BEAST and Tracer for R}
 \author{Rich\`el J.C. Bilderbeek, Rampal S. Etienne}
@@
      BEAST2 is one of the most widely used software tools. 
-     It comes with the graphical program BEAUti to 
-     facilitate the creation of input files to BEAST2. 
+     It comes with the graphical programs BEAUti 2 and Tracer to 
+     facilitate the creation of input files to BEAST2, and
+     to interpret BEAST 2's created output files. 
      However, when many input files are needed, 
-     such a GUI is cumbersome. 
+     a workflow of GUI programs is cumbersome. 
      Moreover, many other phygenetics tools are available 
@@
   \textbf{2. }
-    Here, we present a free, libre and open-source package, \verb;beautier;, 
-    'BEAUti for R', for the R programming language. 
-    \verb;beautier; creates BEAST2 input files 
+    Here, we present a free, libre and open-source package, \verb;babette;, 
+    'BEAUti, BEAST and Tracer for R', for the R programming language. 
+    \verb;babette; creates BEAST2 input files, runs BEAST2 and parses its results, 
     from an R function call. \\
   \textbf{3. }
-    We describe \verb;beautier;'s usage, the novel functionality it provides
+    We describe \verb;babette;'s usage, the novel functionality it provides
     compared to BEAUti, and give some examples. \\
   \textbf{4. }
-    As \verb;beautier; is designed to be of high quality and extendable, 
+    As \verb;babette; is designed to be of high quality and extendable, 
     we conclude by describing the further development of the package \\
@@
 Not only can phylogenies show us how species (or other
-evoliutionary units) relate to each other, 
+evolutionary units) relate to each other, 
 but also relevant parameters like extinction and 
@@
 for an overview of the workflow). 
-It is a console application, that needs a configuration file containing alignments and model parameters.
+It is a console application, that needs a configuration file containing 
+alignments and model parameters.
 
@@
 a desktop application to create a BEAST2 configuration file.
-BEAUti has a user-friendly graphical user interface, with helpful and reasonable default settings.
+BEAUti has a user-friendly graphical user interface, with helpful and 
+reasonable default settings.
 As such, BEAUti is an attractive alternative 
@@
 
-Here, to provide such functionality we present \verb;beautier;, 
-’BEAUti for R’, which creates BEAST2 configuration files 
+Here, to provide such functionality we present \verb;babette;, 
+’BEAUti, BEAST and Tracer for R’, which creates BEAST2 configuration files 
 from an R function call and hence
@@
 reduces the chances of errors in such repetitive actions.
-The interface of \verb;beautier; mimics BEAUti. This
+The interface of \verb;babette; mimics BEAUti. This
 familiarity helps both beginner and experienced BEAST2 users 
-to create configuration files using \verb;beautier;.
+to create configuration files using \verb;babette;.
 Because there are many R packages for exploring the 
 resulting phylogenetic trees, 
-\verb;beautier; enables the creation of a single-script 
+\verb;babette; enables the creation of a single-script 
 pipeline from sequence alignments to tree analysis in R.
 
-\verb;beautier; has a similar goal as \verb;BEASTmasteR; \cite{beastmaster} (still
+\verb;babette; has a similar goal as \verb;BEASTmasteR; \cite{beastmaster} (still
 in pre-release), as both
-allow for scripted use of BEAST2. The difference is that \verb;beautier; 
+allow for scripted use of BEAST2. The difference is that \verb;babette; 
 has its focus on DNA alignments and ultrametric trees, 
@@
         (A) edge [anchor = west] node {\includegraphics[height=0.15\textheight]{BeautiSiteModel.png}} (E)
-        % (E) edge [anchor = east] node {\includegraphics[width=0.25\textwidth]{lumier_logo_big.png}} (F) 
+        (E) edge [anchor = east] node {\includegraphics[width=0.25\textwidth]{beastier_logo.png}} (F) 
         (E) edge [anchor = west] node {\includegraphics[width=0.2\textwidth]{beast_logo.png}} (F); 
@@
     Workflow. From an alignment and priors (depicted as a thought cloud), one creates a BEAST2 XML input file. This
-    can be done using beautier or BEAUti. The created configuration file is run by BEAST2
+    can be done using babette or BEAUti. The created configuration file is run by BEAST2
     to create a posterior of phylogenies and model parameter estimates.
@@
 
-\verb;beautier; is written in the R programming language \cite{R}
+\verb;babette; is written in the R programming language \cite{R}
 and creates a BEAST2 configuration file from an R function call,
@@
 
-\verb;beautier;'s main function is \verb;create_beast2_input_file;, which, 
+\verb;babette;'s main function is \verb;create_beast2_input_file;, which, 
 as the name suggests, creates a BEAST2 configuration file. 
@@
 
-\verb;beautier; currently has 61 exported functions to create a BEAST2 configuration file. 
-\verb;beautier; is an alternative for a majority of BEAUti use cases, 
+\verb;babette; currently has 61 exported functions to create a BEAST2 configuration file. 
+\verb;babette; is an alternative for a majority of BEAUti use cases, 
 but does not yet support the full functionality of BEAUti. 
 Because of BEAUti's high number of plugins, 
-\verb;beautier; uses a software architecture that expects te be extended.
+\verb;babette; uses a software architecture that expects te be extended.
 
-\verb;beastier; \cite{beastier} and \verb;lumier; \cite{lumier} are related packages, used to confirm the correct working of verb;beautier;.
-\verb;lumier; calls BEAST2 from within R and is used to confirm that the XML files created by \verb;beautier; are valid. 
+\verb;beastier; \cite{beastier} and \verb;lumier; \cite{lumier} are related packages, used to confirm the correct working of verb;babette;.
+\verb;lumier; calls BEAST2 from within R and is used to confirm that the XML files created by \verb;babette; are valid. 
 Additionally, \verb;lumier; is used to run BEAST2 to create posteriors. 
@@
 
-\begin{lstlisting}[language=R, caption=Loading, label=lst:loading_beautier, floatplacement=H]
-library(beautier)
+\begin{lstlisting}[language=R, caption=Loading, label=lst:loading_babette, floatplacement=H]
+library(babette)
 \end{lstlisting}
 
-BEAUti, and likewise \verb;beautier;, needs at least a FASTA filename
+BEAUti, and likewise \verb;babette;, needs at least a FASTA filename
 and an output filename. In BEAUti, this is achieved by loading a FASTA file, 
 then saving an output file using a common
-save file dialog. In \verb;beautier;, the same is achieved by:
+save file dialog. In \verb;babette;, the same is achieved by:
 
@@
 \begin{lstlisting}[language=R, caption=Example with different site model and clock model and tree prior, label=lst:all_different, floatplacement=H]
-library(beautier)
+library(babette)
 create_beast2_input_file(
@@
 \end{tabular}
-\caption{beautier's main functions}
+\caption{babette's main functions}
 \label{tab:functions}
@@
 \begin{lstlisting}[language=R, caption=Two alignments, label=lst:two_alignments, floatplacement=H]
-library(beautier)
-beautier::create_beast2_input_file(
+library(babette)
+babette::create_beast2_input_file(
   c("anthus_aco.fas", "anthus_nd2.fas"),
@@
 
-\verb;beautier; also uses the same default distributions as BEAUti 
+\verb;babette; also uses the same default distributions as BEAUti 
 for the site models, clock models and tree priors. 
@@
 
-The following script shows how to do this in \verb;beautier;:
+The following script shows how to do this in \verb;babette;:
 
 \begin{lstlisting}[language=R, caption=Example with Yule tree prior with different birth rate distribution, label=lst:diff_distr, floatplacement=H]
-library(beautier)
+library(babette)
 create_beast2_input_file(
@@
 % TODO: Mix sentences better
-Our initial motivation to create \verb;beautier; 
+Our initial motivation to create \verb;babette; 
 is that we wanted to fix the crown age of a phylogeny, but because 
@@
 with the phylogeny and other parameters. it does not allow for fixing
-the crown age. Without \verb;beautier;, one needs to manually edit the BEAST2 
+the crown age. Without \verb;babette;, one needs to manually edit the BEAST2 
 XML configuration file, which is tedious and prone to errors. 
-\verb;beautier;, allows for easy setting of a fixed crown age, 
+\verb;babette;, allows for easy setting of a fixed crown age, 
 enabling theoretical experiments with one less source of variation. 
@@
 manually edit the XML file to allow for a fixed crown age. 
-This is how to specify a fixed crown age with \verb;beautier;:
+This is how to specify a fixed crown age with \verb;babette;:
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{beautier development and other resources}
+\section{babette development and other resources}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\verb;beautier; is free, libre and open source software available from the official R package archive at 
-\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#beautier}
+\verb;babette; is free, libre and open source software available from the official R package archive at 
+\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#babette}
 and is licensed under the GNU General Public License v3.0.
 
-\verb;beautier; uses the Travis CI \cite{travis} 
+\verb;babette; uses the Travis CI \cite{travis} 
 continuous integration service, which is known to significantly 
@@
 the speed at which new features are added \cite{vasilescu2015}.
-\verb;beautier; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
-\verb;beautier; follows Hadley Wickham's style guide \cite{style_guide}, which improves software quality \cite{fang2001}.
-\verb;beautier; is dependent on multiple packages, which are 
+\verb;babette; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
+\verb;babette; follows Hadley Wickham's style guide \cite{style_guide}, which improves software quality \cite{fang2001}.
+\verb;babette; is dependent on multiple packages, which are 
 \verb;APE; \cite{APE}, 
@@
 
-\verb;beautier;'s development takes place on GitHub \cite{github},
-\url{https://github.com/richelbilderbeek/beautier}, 
+\verb;babette;'s development takes place on GitHub \cite{github},
+\url{https://github.com/richelbilderbeek/babette}, 
 which accomodates collaboration \cite{perez2016ten} 
 and improves transparency \cite{gorgolewski2016practical}.
-\verb;beautier;'s GitHub facilitates feature requests and has a guidelines how to do so.
+\verb;babette;'s GitHub facilitates feature requests and has a guidelines how to do so.
 
-\verb;beautier;'s documentation is extensive. All functions are documented
+\verb;babette;'s documentation is extensive. All functions are documented
 in the package's internal documentation. For quick use, each exported function shows a minimal example. 
 For easy exploration, each exported function's documentation links to related functions.
-Additionally, \verb;beautier; has a vignette that demonstrates extensively how
+Additionally, \verb;babette; has a vignette that demonstrates extensively how
 to use it. The GitHub documentation helps to get started, with a dozen examples 
-of BEAUti screenshots with equivalent \verb;beautier; code.
+of BEAUti screenshots with equivalent \verb;babette; code.
 
-A roadmap of \verb;beautier;'s future extensions can be found on its GitHub.
+A roadmap of \verb;babette;'s future extensions can be found on its GitHub.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Citation of beautier}
+\section{Citation of babette}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Scientists using \verb;beautier; in a published paper can cite this
-article, and/or cite the \verb;beautier; package 
+Scientists using \verb;babette; in a published paper can cite this
+article, and/or cite the \verb;babette; package 
 directly. To obtain this citation from within an R script, use:
@@
 \begin{lstlisting}[language=R]
-> citation("beautier")
+> citation("babette")
 \end{lstlisting}

### 2018-02-05 article.tex
EOD

@@
 library(babette)
+library(beautier)
+library(beastier)
+library(tracerer)
 \end{lstlisting}
@@
 \begin{lstlisting}[language=R, caption=Example with different site model and clock model and tree prior, label=lst:all_different, floatplacement=H]
-library(babette)
 create_beast2_input_file(
@@
 \begin{lstlisting}[language=R, caption=Two alignments, label=lst:two_alignments, floatplacement=H]
-library(babette)
-babette::create_beast2_input_file(
+create_beast2_input_file(
   c("anthus_aco.fas", "anthus_nd2.fas"),
@@
 Our initial motivation to create \verb;babette; 
-is that we wanted to fix the crown age of a phylogeny, but because 
+is that we wanted to fix the crown age of a phylogeny.
 BEAUti assumes that a phylogeny has a crown age that needs to be jointly-estimated
-with the phylogeny and other parameters. it does not allow for fixing
+with the phylogeny and other parameters. It does not allow for fixing
 the crown age. Without \verb;babette;, one needs to manually edit the BEAST2 
 XML configuration file, which is tedious and prone to errors. 
-\verb;babette;, allows for easy setting of a fixed crown age, 
-enabling theoretical experiments with one less source of variation. 
-Setting a fixed crown age is not yet possible in BEAUti directly, 
-but the BEAUti documentation mentions how to 
-manually edit the XML file to allow for a fixed crown age. 
+Fixing the crown ages allows for theoretical experiments 
+with one less source of variation.
+
 This is how to specify a fixed crown age with \verb;babette;:
@@
 )
+\end{lstlisting}
+
+Instead of creating a BEAST2 input file and then running BEAST2,
+\verb;babette; allows to do both steps at once:
+
+\begin{lstlisting}[language=R, caption=Run BEAST2, label=lst:run_beast2, floatplacement=H]
+out <- run_beast2(
+  "alignment.fas"
+)
+\end{lstlisting}
+
+\verb;run_beast2; also allows for setting a site model, clock model,
+tree prior and a fixed crown age. The variable \verb;out; 
+is a list that contains the posterior
+parameter estimates, posterior phylogenies (one per alignment)
+and operator acceptances.
+
+\verb;babette; has functionality of both Tracer and
+DensiTree. To calculate the effective sample sizes in \verb;babette;:
+
+\begin{lstlisting}[language=R, caption=Calculate ESSes, label=lst:calc_esses, floatplacement=H]
+traces <- remove_burn_ins(traces = out$estimates, burn_in_fraction = 0.2)
+esses <- calc_esses(traces, sample_interval = 1000)
+\end{lstlisting}
+
+Tracer displays multiple summary statistics for each
+estimated variable. To obtain, for example, the
+summary statistics of the estimated birth rate in \verb;babette;:
+
+sum_stats <- calc_sum_stats(
+  out$estimates$birthRate, 
+  sample_interval = 1000, burn_in_fraction = 0.1
+)
+
+DensiTree displays the phylogenies in a posterior.
+To do the same in \verb;babette;:
+
+\begin{lstlisting}[language=R, caption=Show posterior phylogenies, label=lst:densitree, floatplacement=H]
+library(phangorn)
+densiTree(out$anthus_aco_trees)
 \end{lstlisting}

### 2018-02-06 article.tex
Gone through it all

@@
      BEAST2 is one of the most widely used software tools. 
-     It comes with the graphical programs BEAUti 2 and Tracer to 
+     It comes with the graphical programs BEAUti 2 to
      facilitate the creation of input files to BEAST2, and
+     with DensiTree and Tracer 
      to interpret BEAST 2's created output files. 
-     However, when many input files are needed, 
+     However, when many input and output files are required, 
      a workflow of GUI programs is cumbersome. 
@@
     Here, we present a free, libre and open-source package, \verb;babette;, 
-    'BEAUti, BEAST and Tracer for R', for the R programming language. 
+    'BEAUti 2, BEAST2 and Tracer for R', for the R programming language. 
     \verb;babette; creates BEAST2 input files, runs BEAST2 and parses its results, 
@@
     We describe \verb;babette;'s usage, the novel functionality it provides
-    compared to BEAUti, and give some examples. \\
+    compared to BEAUti 2, and give some examples. \\
   \textbf{4. }
@@
 
+BEAST2 is also associated with Tracer \cite{tracer} and 
+DensiTree 2 \cite{DensiTree}. Both are desktop applications 
+to analyze the output of BEAST2, each with a user-friendly graphical user interface.
+
+Tracer's purpose is to analyze the parameter estimates generated
+from a BEAST 2 run. It shows, among
+others, the effective sample size (ESS) and time series ('the trace', 
+hence the name) of each variable in the MCMC run. Both ESS and trace
+are needed to assess the strength of the inference. 
+DensiTree visualizes the phylogenies of a BEAST2 posterior, with
+many options to improve the displayal of those many phylogenies.
+
+However, for exploring the output of many BEAST2 runs, 
+one would like a script to collect all parameter ESSes,
+parameter traces and posterior phylogenies.
+
 Here, to provide such functionality we present \verb;babette;, 
-’BEAUti, BEAST and Tracer for R’, which creates BEAST2 configuration files 
+’BEAUti 2, BEAST2 and Tracer for R’, 
+which creates BEAST2 configuration files,
+runs BEAST2 and analyzes its results 
 from an R function call and hence
@@
 reduces the chances of errors in such repetitive actions.
-The interface of \verb;babette; mimics BEAUti. This
+The interface of \verb;babette; to create BEAST2 configureation
+files closely mimics BEAUti. This
 familiarity helps both beginner and experienced BEAST2 users 
 to create configuration files using \verb;babette;.
-Because there are many R packages for exploring the 
-resulting phylogenetic trees, 
 \verb;babette; enables the creation of a single-script 
@@
 
-\verb;babette; has a similar goal as \verb;BEASTmasteR; \cite{beastmaster} (still
-in pre-release), as both
-allow for scripted use of BEAST2. The difference is that \verb;babette; 
+\verb;babette; is the first R package that unifies the
+full workflow of working with BEAST2. An
+example to create a BEAST2 input file is 
+\verb;BEASTmasteR; \cite{beastmaster}.
+Also \verb;BEASTmasteR; allows 
+to create BEAST2 configuration files from R. 
+The difference is that \verb;babette; 
 has its focus on DNA alignments and ultrametric trees, 
 where \verb;BEASTmasteR; is used for 
-morphologucal traits and tip-dating.
+morphological traits and tip-dating.
+Examples of R packages to parse the BEAST2 output files
+are \verb;rBEAST; \cite{rBEAST}, 
+\verb;RBEAST; \cite{RBEAST} and 
+\verb;rbeast2; \cite{rbeast2}.
 
@@
 \verb;babette; is written in the R programming language \cite{R}
-and creates a BEAST2 configuration file from an R function call,
-in a similar way that BEAUti does.
+and enables the full BEAST2 workflow from an R function call,
+in a similar way that BEAUti, DensiTree and Tracer do.
 
-\verb;babette;'s main function is \verb;create_beast2_input_file;, which, 
-as the name suggests, creates a BEAST2 configuration file. 
-\verb;create_beast2_input_file; needs at least the name of a 
-FASTA file containing a DNA alignment
-and a name for the to-be-created configuration file. 
-The default settings for the other arguments of \verb;create_beast2_input_file; 
-are identical to BEAUti's default settings.
+\verb;babette;'s main function is \verb;run_beast2;, which, 
+configures BEAST2, runs it and parses its output. 
+\verb;run_beast2; needs at least the name of a 
+FASTA file containing a DNA alignment. 
+The default settings for the other arguments of \verb;run_beast2; 
+are identical to BEAUti's and BEAST2's default settings.
 Per alignment, a site model, clock model and tree prior can be chosen.
-Multiple alignments can be used, each with its own (unlinked) site model, clock model and tree prior.
+Multiple alignments can be used, each with its own (unlinked) site model, 
+clock model and tree prior.
 
-\verb;babette; currently has 61 exported functions to create a BEAST2 configuration file. 
+\verb;babette; currently has 61 exported functions to set up  
+a BEAST2 configuration file. 
 \verb;babette; is an alternative for a majority of BEAUti use cases, 
@@
 
-\verb;beastier; \cite{beastier} and \verb;lumier; \cite{lumier} are related packages, used to confirm the correct working of verb;babette;.
-\verb;lumier; calls BEAST2 from within R and is used to confirm that the XML files created by \verb;babette; are valid. 
-Additionally, \verb;lumier; is used to run BEAST2 to create posteriors. 
-\verb;beastier; can parse BEAST2 posteriors, and is used to confirm whether posteriors have an estimated or fixed crown age.
+\verb;babette; has 7 exported function to run and help run BEAST2.
+One function is a wrapper function to run BEAST2, others
+allow the user to check if a BEAST2 configuration file is indeed valid.
+
+\verb;babette; has 20 exported function to parse the BEAST2 output
+file and analyse the created posterior. \verb;babette; gives the
+same ESSes and summary statistics as Tracer. The data is formatted
+as such, that it can easily be visualized using ggplot2 (for a trace,
+similar to Tracer)
+or phangorn (for the phylogenies in a posterior, simular to DensiTree).
 
@@
 library(babette)
-library(beautier)
-library(beastier)
-library(tracerer)
 \end{lstlisting}
@@
 BEAUti, and likewise \verb;babette;, needs at least a FASTA filename
-and an output filename. In BEAUti, this is achieved by loading a FASTA file, 
+to produce a BEAST2 configuration file. 
+In BEAUti, this is achieved by loading a FASTA file, 
 then saving an output file using a common
-save file dialog. In \verb;babette;, the same is achieved by:
+save file dialog. After this, BEAST2 needs to be invoked
+on the created configuration file to create multiple files
+storing the created posterior. Finally, these output
+files must be parsed by either Tracer of DensiTree.
+
+In \verb;babette;, the same is achieved by:
 
 \begin{lstlisting}[language=R, caption=Simplest example, label=lst:simplest_example, floatplacement=H]
-create_beast2_input_file(
-  "alignment.fas",
-  "beast2.xml"
+out <- run_beast2(
+  "alignment.fas"
 )
@@
 
-This code will create a BEAST2 configuration file with name '\verb;beast2.xml;',
+This code will create a (temporary) BEAST2 configuration file,
 using a FASTA file with name \verb;alignment.fas;, using the same default settings as BEAUti.
-The default settings are, among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
+\verb;babette; will then execute a BEAST2 with that file, and
+parses the output. The default settings are, among others, 
+to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
 a strict clock, and a Yule birth tree prior \cite{yule}.
@@
 \begin{lstlisting}[language=R, caption=Example with different site model and clock model and tree prior, label=lst:all_different, floatplacement=H]
-create_beast2_input_file(
+out <- run_beast2(
   "alignment.fas",
-  "beast2.xml",
   site_models = create_hky_site_model(),
@@
 \begin{lstlisting}[language=R, caption=Two alignments, label=lst:two_alignments, floatplacement=H]
-create_beast2_input_file(
+out <- run_beast2(
   c("anthus_aco.fas", "anthus_nd2.fas"),
-  "beast2.xml",
   site_models = list(
@@
 \begin{lstlisting}[language=R, caption=Example with Yule tree prior with different birth rate distribution, label=lst:diff_distr, floatplacement=H]
-library(babette)
-create_beast2_input_file(
+out <- run_beast2(
   "alignment.fas",
-  "beast2.xml",
   tree_priors = create_yule_tree_prior(
@@
 
-% TODO: Mix sentences better
 Our initial motivation to create \verb;babette; 
@@
 \begin{lstlisting}[language=R, caption=Example with fixed crown age, label=lst:fixed_crown_age, floatplacement=H]
-create_beast2_input_file(
+out <- run_beast2(
   "alignment.fas",
-  "beast2.xml"
   posterior_crown_age = 15
@@
 \end{lstlisting}
-
-Instead of creating a BEAST2 input file and then running BEAST2,
-\verb;babette; allows to do both steps at once:
-
-\begin{lstlisting}[language=R, caption=Run BEAST2, label=lst:run_beast2, floatplacement=H]
-out <- run_beast2(
-  "alignment.fas"
-)
-\end{lstlisting}
-
-\verb;run_beast2; also allows for setting a site model, clock model,
-tree prior and a fixed crown age. The variable \verb;out; 
-is a list that contains the posterior
-parameter estimates, posterior phylogenies (one per alignment)
-and operator acceptances.
 
@@
 \begin{lstlisting}[language=R, caption=Show posterior phylogenies, label=lst:densitree, floatplacement=H]
-library(phangorn)
-densiTree(out$anthus_aco_trees)
+densitree(out$anthus_aco_trees)
 \end{lstlisting}
@@
 \verb;APE; \cite{APE}, 
+\verb;beautier; \cite{beautier},
 \verb;beastier; \cite{beastier},
@@
 \verb;knitr; \cite{knitr},
-\verb;lumier; \cite{lumier},
 \verb;phangorn; \cite{phangorn},
@@
 \verb;testit; \cite{testit} and 
+\verb;tracerer; \cite{tracerer},
 \verb;TreeSim; \cite{TreeSim}.
@@
 \verb;babette;'s documentation is extensive. All functions are documented
-in the package's internal documentation. For quick use, each exported function shows a minimal example. 
+in the package's internal documentation. For quick use, 
+each exported function shows a minimal example. 
 For easy exploration, each exported function's documentation links to related functions.
@@
 of BEAUti screenshots with equivalent \verb;babette; code.
-
-A roadmap of \verb;babette;'s future extensions can be found on its GitHub.
 

### 2018-02-08 article.tex
Numbered lines, arrows look funny

@@
 
-\title{babette: BEAUti, BEAST and Tracer for R}
+\title{babette: BEAUti 2, BEAST2 and Tracer for R}
 \author{Rich\`el J.C. Bilderbeek, Rampal S. Etienne}
@@
 \usepackage{pgf}
+\usepackage{bm}
 \usetikzlibrary{arrows,automata}
@@
 
-% Adds numbered lines, thanks to Raphael Scherrer
-% \usepackage[switch]{lineno}
+% Adds numbered lines
+\usepackage{lineno}
+\linenumbers
 
@@
 
+\begin{lstlisting}[language=R, caption=Calculate all summary statistics, label=lst:calc_sum_stats, floatplacement=H]
 sum_stats <- calc_sum_stats(
@@
 )
+\end{lstlisting}
 

### 2018-02-08 article.tex
Fixed arrow

@@
   extendedchars=false,% prohibit extended chars (chars of codes 128--255)
-  literate={"}{{\texttt{"}}}1{<-}{{$\bm\leftarrow$}}1{<<-}{{$\bm\twoheadleftarrow$}}1
-  {~}{{$\bm\sim$}}1{<=}{{$\bm\le$}}1{>=}{{$\bm\ge$}}1{!=}{{$\bm\neq$}}1{^}{{$^{\bm\wedge}$}}1,% item to replace, text, length of chars
   alsoletter={.<-},% becomes a letter

### 2018-02-08 article.tex
Abstract is called 'Summary'
Keywords
Better figure

@@
 
+% Rename 'Abstract' to 'Summary 
+\usepackage[english]{babel}
+\addto{\captionsenglish}{\renewcommand{\abstractname}{Summary}}
+
+% Keywords
+% \usepackage{spconf}
+
+\usetikzlibrary{calc}
+\usetikzlibrary{arrows.meta}
+
 \begin{document}
@@
 \maketitle
-
-% TODO: RS: Rename to 'Summary 
-% https://tex.stackexchange.com/a/24778 does not work:
-% \addto{\captionsenglish}{\renewcommand{\abstractname}{Summary}}
 
@@
 
-% TODO: RS: Get these keywords visualized
-% Key-words: computational biology, evolution, phylogeny, BEAST2, R
+% Ideal
+%\begin{keywords}
+%  computational biology, evolution, phylogeny, BEAST2, R
+%\end{keywords}
+
+% Dirty hack
+{\bf Keywords:} computational biology, evolution, phylogeny, BEAST2, R
 
@@
   \centering
+  \resizebox {0.8\columnwidth} {!} {
     \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=6cm, semithick]   
@@
       \includegraphics[width=0.2\textwidth]{alignment.png}
-    \includegraphics[width=0.2\textwidth]{thought_cloud.png}
+    };   
+    \node[state] (AL) [above left=-0.25cm and -0.25cm of A, fill=white] {
+      1
+    };   
+    \node[state] (B) [right of = A, rectangle] {
+      \includegraphics[height=0.15\textheight]{BeautiSiteModel.png}
+    };   
+    \node[state] (BL) [above left=-0.25cm and -0.25cm of B, fill=white] {
+      2
     };   
     \node[state] (E) [below of=A, rectangle] {
-    \includegraphics[height=0.1\textheight]{xml.png}
+      \includegraphics[height=0.1\textheight]{file2.png}
+    };   
+    \node[state] (EL) [above left=-0.25cm and -0.25cm of E, fill=white] {
+      3
+    };   
+    \node[state] (C) [right of = E, rectangle] {
+      \includegraphics[width=0.3\textwidth]{beast_logo.png}
+    };   
+    \node[state] (CL) [above left=-0.25cm and -0.25cm of C, fill=white] {
+      4
     };   
     \node[state] (F) [rectangle, below of=E] {
+      \includegraphics[height=0.1\textheight]{file.png}
+    };
+    \node[state] (FL) [above left=-0.25cm and -0.25cm of F, fill=white] {
+      5
+    };   
+    \node[state] (H) [rectangle, below of=F] {
       \includegraphics[width=0.3\textwidth]{DensiTreeExample2.jpg}
-    \includegraphics[width=0.6\textwidth]{ParameterEstimates.png}
     };
-  \path (A) edge [anchor = east] node {\includegraphics[height=0.15\textheight]{beautier_logo.png}} (E)
-        (A) edge [anchor = west] node {\includegraphics[height=0.15\textheight]{BeautiSiteModel.png}} (E)
-        (E) edge [anchor = east] node {\includegraphics[width=0.25\textwidth]{beastier_logo.png}} (F) 
-        (E) edge [anchor = west] node {\includegraphics[width=0.2\textwidth]{beast_logo.png}} (F); 
+    \node[state] (HL) [above left=-0.25cm and -0.25cm of H, fill=white] {
+      6
+    };   
+    \node[state] (I) [rectangle, right of=H] {
+      \includegraphics[width=0.6\textwidth]{tracer_example_output.png}
+    };
+    \node[state] (IL) [above left=-0.25cm and -0.25cm of I, fill=white] {
+      7
+    };   
+    \path 
+      (A) edge [anchor = west] node {} (E)
+      (E) edge [anchor = west] node {} (F)
+      (F) edge [anchor = west] node {} (H)
+      (F) edge [anchor = west] node {} (I)
+    ; 
+    \path [-o,draw] (B) -- ($ (A) !.5! (E) $);
+    \path [-o,draw] (C) -- ($ (E) !.5! (F) $);
     \end{tikzpicture}
-
+  }
   \caption{
-    Workflow. From an alignment and priors (depicted as a thought cloud), one creates a BEAST2 XML input file. This
-    can be done using babette or BEAUti. The created configuration file is run by BEAST2
-    to create a posterior of phylogenies and model parameter estimates.
+    Workflow using GUI tools. From an alignment, BEAUti is used to create a 
+    BEAST2 configuration file. That file is run by BEAST2. The results
+    are visualized using DensiTree and Tracer.
   }

### 2018-02-08 article.tex
Bibliography

@@
 Examples of R packages to parse the BEAST2 output files
-are \verb;rBEAST; \cite{rBEAST}, 
-\verb;RBEAST; \cite{RBEAST} and 
-\verb;rbeast2; \cite{rbeast2}.
+are \verb;rBEAST; \cite{rBEAST} and 
+\verb;RBEAST; \cite{RBEAST}.
 
@@
   \caption{
-    Workflow using GUI tools. From an alignment, BEAUti is used to create a 
-    BEAST2 configuration file. That file is run by BEAST2. The results
-    are visualized using DensiTree and Tracer.
+    Workflow using GUI tools. From an alignment (1) and BEAUti (2), 
+    a BEAST2 configuration file (3) is created. BEAST2 (4) uses that file
+    to a posterior, storing it in multiple files (5). These results
+    are visualized using DensiTree (6) and Tracer (7).
   }

### 2018-02-08 article.tex
EOD

@@
 This code will create a (temporary) BEAST2 configuration file,
-using a FASTA file with name \verb;alignment.fas;, using the same default settings as BEAUti.
+using a FASTA file with name \verb;alignment.fas;, 
+using the same default settings as BEAUti.
 \verb;babette; will then execute a BEAST2 with that file, and
-parses the output. The default settings are, among others, 
-to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
+parses the output. The output, named \verb;out;, is a list of
+parameter estimates, posterior phylogenies (one per alignment)
+and operator acceptances.
+
+The default settings for BEAUti (and thus \verb;babette;) are, 
+among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
 a strict clock, and a Yule birth tree prior \cite{yule}.
@@
 birth-death tree prior, each with their default settings in BEAUti.
-Table \ref{tab:functions} shows an overview of all functions to create site models, clock models and tree priors.
+Table \ref{tab:functions} shows an overview of all functions to 
+create site models, clock models and tree priors.
 
@@
 
-Note that the arguments' names \verb;site_models;, \verb;clock_models; and \verb;tree_priors; are plural, as each of these
-can be (a list of) one or more elements. Each of these arguments must have the same number of elements, so that each alignment has its
+Note that the arguments' names \verb;site_models;, \verb;clock_models; 
+and \verb;tree_priors; are plural, as each of these
+can be (a list of) one or more elements. Each of these arguments must 
+have the same number of elements, so that each alignment has its
 own site model, clock model and tree prior.
@@
 \verb;testit; \cite{testit} and 
-\verb;tracerer; \cite{tracerer},
+\verb;tracerer; \cite{tracerer} and
 \verb;TreeSim; \cite{TreeSim}.

### 2018-02-09 article.tex
Better

@@
      facilitate the creation of input files to BEAST2, and
-     with DensiTree and Tracer 
-     to interpret BEAST 2's created output files. 
-     However, when many input and output files are required, 
+     with DensiTree and Tracer, 
+     to interpret BEAST2's output. 
+     However, when many input files are required, 
      a workflow of GUI programs is cumbersome. 
@@
     We describe \verb;babette;'s usage, the novel functionality it provides
-    compared to BEAUti 2, and give some examples. \\
+    compared to the tools it replaces, and give some examples. \\
   \textbf{4. }
@@
 BEAST2 is also associated with Tracer \cite{tracer} and 
-DensiTree 2 \cite{DensiTree}. Both are desktop applications 
+DensiTree \cite{DensiTree}. Both are desktop applications 
 to analyze the output of BEAST2, each with a user-friendly graphical user interface.
@@
 which creates BEAST2 configuration files,
-runs BEAST2 and analyzes its results 
-from an R function call and hence
-will save time and tedious mouse clicking and 
+runs BEAST2, and analyzes its results,
+all from an R function call. This
+will save time, tedious mouse clicking and 
 reduces the chances of errors in such repetitive actions.
-The interface of \verb;babette; to create BEAST2 configureation
-files closely mimics BEAUti. This
+The interface of \verb;babette; mimics the tools it
+is inspired on. This
 familiarity helps both beginner and experienced BEAST2 users 
-to create configuration files using \verb;babette;.
+to make the step from those tools to \verb;babette;.
 \verb;babette; enables the creation of a single-script 
-pipeline from sequence alignments to tree analysis in R.
+pipeline from sequence alignments to posterior analysis in R.
 
@@
 same ESSes and summary statistics as Tracer. The data is formatted
-as such, that it can easily be visualized using ggplot2 (for a trace,
+as such, that it can easily be visualized using \verb;ggplot2; (for a trace,
 similar to Tracer)
-or phangorn (for the phylogenies in a posterior, simular to DensiTree).
+or \verb;phangorn; (for the phylogenies in a posterior, simular to DensiTree).
 
@@
 the crown age. Without \verb;babette;, one needs to manually edit the BEAST2 
-XML configuration file, which is tedious and prone to errors. 
-Fixing the crown ages allows for theoretical experiments 
-with one less source of variation.
+configuration file, which is tedious and prone to errors. 
+Fixing the crown ages is especially useful for theoretical experiments,
+as this allows for one less source of variation.
 
@@
 \verb;babette; has functionality of both Tracer and
-DensiTree. To calculate the effective sample sizes in \verb;babette;:
+DensiTree. Tracer, among others, shows the effective sample
+sizes of each posterior's variables. As an MCMC run needs to
+converge first, Tracer discards the first 10\% of all parameter
+estimates. This is called the burn-in. To calculate the effective
+sample sizes in \verb;babette;, with the same burn-in of 10\%:
 
 \begin{lstlisting}[language=R, caption=Calculate ESSes, label=lst:calc_esses, floatplacement=H]
-traces <- remove_burn_ins(traces = out$estimates, burn_in_fraction = 0.2)
+traces <- remove_burn_ins(traces = out$estimates, burn_in_fraction = 0.1)
 esses <- calc_esses(traces, sample_interval = 1000)
@@
   out$estimates$birthRate, 
-  sample_interval = 1000, burn_in_fraction = 0.1
+  sample_interval = 1000, 
+  burn_in_fraction = 0.1
 )

### 2018-02-09 article.tex
Better

@@
 
-\verb;babette; has functionality of both Tracer and
-DensiTree. Tracer, among others, shows the effective sample
+\verb;babette; allows for the same functionality of Tracer. 
+Tracer, among others, shows the effective sample
 sizes of each posterior's variables. As an MCMC run needs to
@@
 Tracer displays multiple summary statistics for each
-estimated variable. To obtain, for example, the
-summary statistics of the estimated birth rate in \verb;babette;:
+estimated variable: the mean and its standard error, standard deviation,
+variance, median, mode, geometric mean, 95\% HPD interval, auto-correlation
+time and effective sample size. To obtain all these summary statistics 
+of the estimated birth rate in \verb;babette;:
 
@@
 
-DensiTree displays the phylogenies in a posterior.
-To do the same in \verb;babette;:
+\verb;babette; allows for the same functionality of DensiTree.
+DensiTree displays the phylogenies in a posterior at the same
+time scale over one another, allowing to see the uncertainty in
+topology and branch lengths. To vizualize the same in \verb;babette;:
 

### 2018-02-09 article.tex
Show bibliography once
No listing captions

@@
   commentstyle=\color{gray},% comment style
-  numbers=left,% display line numbers on the left side
+  % numbers=left,% display line numbers on the left side
   numberstyle=\scriptsize,% use small line numbers
@@
 
-\begin{lstlisting}[language=R, caption=Loading, label=lst:loading_babette, floatplacement=H]
+\begin{lstlisting}[language=R, floatplacement=H]
 library(babette)
@@
 
-\begin{lstlisting}[language=R, caption=Simplest example, label=lst:simplest_example, floatplacement=H]
-out <- run_beast2(
-  "alignment.fas"
-)
+\begin{lstlisting}[language=R, floatplacement=H]
+out <- run_beast2("alignment.fas")
 \end{lstlisting}
@@
 
-\begin{lstlisting}[language=R, caption=Example with different site model and clock model and tree prior, label=lst:all_different, floatplacement=H]
+\begin{lstlisting}[language=R, floatplacement=H]
 out <- run_beast2(
@@
 
-\begin{lstlisting}[language=R, caption=Two alignments, label=lst:two_alignments, floatplacement=H]
+\begin{lstlisting}[language=R, floatplacement=H]
 out <- run_beast2(
@@
 
-\begin{lstlisting}[language=R, caption=Example with Yule tree prior with different birth rate distribution, label=lst:diff_distr, floatplacement=H]
+\begin{lstlisting}[language=R, floatplacement=H]
 out <- run_beast2(
@@
 
-\begin{lstlisting}[language=R, caption=Example with fixed crown age, label=lst:fixed_crown_age, floatplacement=H]
+\begin{lstlisting}[language=R, floatplacement=H]
 out <- run_beast2(
@@
 
-\begin{lstlisting}[language=R, caption=Calculate ESSes, label=lst:calc_esses, floatplacement=H]
+\begin{lstlisting}[language=R, floatplacement=H]
 traces <- remove_burn_ins(traces = out$estimates, burn_in_fraction = 0.1)
@@
 
-\begin{lstlisting}[language=R, caption=Calculate all summary statistics, label=lst:calc_sum_stats, floatplacement=H]
+\begin{lstlisting}[language=R, floatplacement=H]
 sum_stats <- calc_sum_stats(
@@
 
-\begin{lstlisting}[language=R, caption=Show posterior phylogenies, label=lst:densitree, floatplacement=H]
+\begin{lstlisting}[language=R, floatplacement=H]
 densitree(out$anthus_aco_trees)
@@
 \bibliography{article}
-
-\begin{thebibliography}{}
-
-\end{thebibliography}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-02-09 article.tex
No abbrev

@@
 estimated variable: the mean and its standard error, standard deviation,
-variance, median, mode, geometric mean, 95\% HPD interval, auto-correlation
-time and effective sample size. To obtain all these summary statistics 
-of the estimated birth rate in \verb;babette;:
+variance, median, mode, geometric mean, 95\% highest posterior density interval, 
+auto-correlation time and effective sample size. To obtain all these summary statistics 
+of, for example, the estimated birth rate in \verb;babette;:
 

### 2018-02-09 article.tex
Better

@@
      It comes with the graphical programs BEAUti 2 to
-     facilitate the creation of input files to BEAST2, and
-     with DensiTree and Tracer, 
-     to interpret BEAST2's output. 
-     However, when many input files are required, 
-     a workflow of GUI programs is cumbersome. 
-     Moreover, many other phygenetics tools are available 
-     in R, which requires switching from one platform 
-     to the other. \\
+     facilitate the creation of BEAST2 configuration files, and
+     with DensiTree and Tracer, to interpret BEAST2's output files. 
+     However, when many different alignments or model 
+     setups are required, a workflow of GUI programs is cumbersome. \\
   \textbf{2. }
@@
     \verb;babette; creates BEAST2 input files, runs BEAST2 and parses its results, 
-    from an R function call. \\
+    all from an R function call. \\
   \textbf{3. }
     We describe \verb;babette;'s usage, the novel functionality it provides
-    compared to the tools it replaces, and give some examples. \\
+    compared to the tools it is alternative of, and give some examples. \\
   \textbf{4. }

### 2018-02-09 article.tex
Better

@@
     a BEAST2 configuration file (3) is created. BEAST2 (4) uses that file
-    to a posterior, storing it in multiple files (5). These results
-    are visualized using DensiTree (6) and Tracer (7).
+    to infer a posterior, storing it in multiple files (5). These results
+    are visualized using DensiTree (6) and Tracer (7). babette allows
+    for the same workflow, all from an R function call.
   }
@@
 \verb;babette; has 20 exported function to parse the BEAST2 output
-file and analyse the created posterior. \verb;babette; gives the
+files and analyse the created posterior. \verb;babette; gives the
 same ESSes and summary statistics as Tracer. The data is formatted
@@
 similar to Tracer)
-or \verb;phangorn; (for the phylogenies in a posterior, simular to DensiTree).
+or \verb;phangorn; \cite{phangorn} (for the phylogenies in a posterior, simular to DensiTree).
 

### 2018-02-09 article.tex
spellcheck

@@
 similar to Tracer)
-or \verb;phangorn; \cite{phangorn} (for the phylogenies in a posterior, simular to DensiTree).
+or \verb;phangorn; \cite{phangorn} (for the phylogenies in a posterior, similar to DensiTree).
 
@@
 time scale over one another, allowing to see the uncertainty in
-topology and branch lengths. To vizualize the same in \verb;babette;:
+topology and branch lengths. To visualize the same in \verb;babette;:
 
@@
 \url{https://github.com/richelbilderbeek/babette}, 
-which accomodates collaboration \cite{perez2016ten} 
+which accommodates collaboration \cite{perez2016ten} 
 and improves transparency \cite{gorgolewski2016practical}.

### 2018-02-15 article.tex
better keyword
Before implementing feedback GL

@@
 %\begin{keywords}
-%  computational biology, evolution, phylogeny, BEAST2, R
+%  computational biology, evolution, phylogenetics, BEAST2, R
 %\end{keywords}
@@
 % Dirty hack
-{\bf Keywords:} computational biology, evolution, phylogeny, BEAST2, R
+{\bf Keywords:} computational biology, evolution, phylogenetics, BEAST2, R
 
@@
 and improves transparency \cite{gorgolewski2016practical}.
-\verb;babette;'s GitHub facilitates feature requests and has a guidelines how to do so.
+\verb;babette;'s GitHub facilitates feature requests and has guidelines how to do so.
 

### 2018-02-15 article.tex
Feedback @Giappo

@@
 and enables the full BEAST2 workflow from an R function call,
-in a similar way that BEAUti, DensiTree and Tracer do.
+in a similar way to what BEAUti, DensiTree and Tracer do.
 
@@
 Because of BEAUti's high number of plugins, 
-\verb;babette; uses a software architecture that expects te be extended.
+\verb;babette; uses a software architecture that expects to be extended.
 
 \verb;babette; has 7 exported function to run and help run BEAST2.
-One function is a wrapper function to run BEAST2, others
+One function is used to run BEAST2, others
 allow the user to check if a BEAST2 configuration file is indeed valid.
@@
 using the same default settings as BEAUti.
-\verb;babette; will then execute a BEAST2 with that file, and
+\verb;babette; will then execute BEAST2 with that file, and
 parses the output. The output, named \verb;out;, is a list of
-parameter estimates, posterior phylogenies (one per alignment)
+parameter estimates, posterior phylogenies (one for each alignment)
 and operator acceptances.
@@
 
-\verb;babette; also uses the same default distributions as BEAUti 
-for the site models, clock models and tree priors. 
-For example, a Yule tree prior assumes the birth rate follows a uniform distribution, 
+\verb;babette; also uses the same default prior distributions as BEAUti 
+for each of the site models, clock models and tree priors. 
+For example, by default, a Yule tree prior assumes the birth rate 
+follows a uniform distribution, 
 from minus infinity to plus infinity. 
@@
 converge first, Tracer discards the first 10\% of all parameter
-estimates. This is called the burn-in. To calculate the effective
-sample sizes in \verb;babette;, with the same burn-in of 10\%:
+estimates. This is called the "burn-in". To remove the burn-in
+in \verb;babette;:
 
 \begin{lstlisting}[language=R, floatplacement=H]
-traces <- remove_burn_ins(traces = out$estimates, burn_in_fraction = 0.1)
-esses <- calc_esses(traces, sample_interval = 1000)
+traces <- remove_burn_ins(out$estimates)
+\end{lstlisting}
+
+Then, to calculate the effective sample sizes in \verb;babette;:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+esses <- calc_esses(
+  traces, 
+  sample_interval = 1000
+)
 \end{lstlisting}
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-sum_stats <- calc_sum_stats(
-  out$estimates$birthRate, 
-  sample_interval = 1000, 
-  burn_in_fraction = 0.1
+sum_stats <- calc_summary_stats(
+  traces$birthRate, 
+  sample_interval = 1000
 )

### 2018-02-15 article.tex
Renamed package to 'rbeast2' from 'babette'

@@
 
-\title{babette: BEAUti 2, BEAST2 and Tracer for R}
+\title{rbeast2: BEAUti 2, BEAST2 and Tracer for R}
 \author{Rich\`el J.C. Bilderbeek, Rampal S. Etienne}
@@
   \textbf{2. }
-    Here, we present a free, libre and open-source package, \verb;babette;, 
+    Here, we present a free, libre and open-source package, \verb;rbeast2;, 
     'BEAUti 2, BEAST2 and Tracer for R', for the R programming language. 
-    \verb;babette; creates BEAST2 input files, runs BEAST2 and parses its results, 
+    \verb;rbeast2; creates BEAST2 input files, runs BEAST2 and parses its results, 
     all from an R function call. \\
   \textbf{3. }
-    We describe \verb;babette;'s usage, the novel functionality it provides
+    We describe \verb;rbeast2;'s usage, the novel functionality it provides
     compared to the tools it is alternative of, and give some examples. \\
   \textbf{4. }
-    As \verb;babette; is designed to be of high quality and extendable, 
+    As \verb;rbeast2; is designed to be of high quality and extendable, 
     we conclude by describing the further development of the package \\
@@
 
-Here, to provide such functionality we present \verb;babette;, 
+Here, to provide such functionality we present \verb;rbeast2;, 
 ’BEAUti 2, BEAST2 and Tracer for R’, 
@@
 reduces the chances of errors in such repetitive actions.
-The interface of \verb;babette; mimics the tools it
+The interface of \verb;rbeast2; mimics the tools it
 is inspired on. This
 familiarity helps both beginner and experienced BEAST2 users 
-to make the step from those tools to \verb;babette;.
-\verb;babette; enables the creation of a single-script 
+to make the step from those tools to \verb;rbeast2;.
+\verb;rbeast2; enables the creation of a single-script 
 pipeline from sequence alignments to posterior analysis in R.
 
-\verb;babette; is the first R package that unifies the
+\verb;rbeast2; is the first R package that unifies the
 full workflow of working with BEAST2. An
@@
 to create BEAST2 configuration files from R. 
-The difference is that \verb;babette; 
+The difference is that \verb;rbeast2; 
 has its focus on DNA alignments and ultrametric trees, 
@@
     to infer a posterior, storing it in multiple files (5). These results
-    are visualized using DensiTree (6) and Tracer (7). babette allows
+    are visualized using DensiTree (6) and Tracer (7). rbeast2 allows
     for the same workflow, all from an R function call.
@@
 
-\verb;babette; is written in the R programming language \cite{R}
+\verb;rbeast2; is written in the R programming language \cite{R}
 and enables the full BEAST2 workflow from an R function call,
@@
 
-\verb;babette;'s main function is \verb;run_beast2;, which, 
+\verb;rbeast2;'s main function is \verb;run_beast2;, which, 
 configures BEAST2, runs it and parses its output. 
@@
 
-\verb;babette; currently has 61 exported functions to set up  
+\verb;rbeast2; currently has 61 exported functions to set up  
 a BEAST2 configuration file. 
-\verb;babette; is an alternative for a majority of BEAUti use cases, 
+\verb;rbeast2; is an alternative for a majority of BEAUti use cases, 
 but does not yet support the full functionality of BEAUti. 
 Because of BEAUti's high number of plugins, 
-\verb;babette; uses a software architecture that expects to be extended.
+\verb;rbeast2; uses a software architecture that expects to be extended.
 
-\verb;babette; has 7 exported function to run and help run BEAST2.
+\verb;rbeast2; has 7 exported function to run and help run BEAST2.
 One function is used to run BEAST2, others
@@
 
-\verb;babette; has 20 exported function to parse the BEAST2 output
-files and analyse the created posterior. \verb;babette; gives the
+\verb;rbeast2; has 20 exported function to parse the BEAST2 output
+files and analyse the created posterior. \verb;rbeast2; gives the
 same ESSes and summary statistics as Tracer. The data is formatted
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-library(babette)
+library(rbeast2)
 \end{lstlisting}
 
-BEAUti, and likewise \verb;babette;, needs at least a FASTA filename
+BEAUti, and likewise \verb;rbeast2;, needs at least a FASTA filename
 to produce a BEAST2 configuration file. 
@@
 
-In \verb;babette;, the same is achieved by:
+In \verb;rbeast2;, the same is achieved by:
 
@@
 using the same default settings as BEAUti.
-\verb;babette; will then execute BEAST2 with that file, and
+\verb;rbeast2; will then execute BEAST2 with that file, and
 parses the output. The output, named \verb;out;, is a list of
@@
 
-The default settings for BEAUti (and thus \verb;babette;) are, 
+The default settings for BEAUti (and thus \verb;rbeast2;) are, 
 among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
@@
 \end{tabular}
-\caption{babette's main functions}
+\caption{rbeast2's main functions}
 \label{tab:functions}
@@
 
-\verb;babette; also uses the same default prior distributions as BEAUti 
+\verb;rbeast2; also uses the same default prior distributions as BEAUti 
 for each of the site models, clock models and tree priors. 
@@
 
-The following script shows how to do this in \verb;babette;:
+The following script shows how to do this in \verb;rbeast2;:
 
@@
 
-Our initial motivation to create \verb;babette; 
+Our initial motivation to create \verb;rbeast2; 
 is that we wanted to fix the crown age of a phylogeny.
@@
 with the phylogeny and other parameters. It does not allow for fixing
-the crown age. Without \verb;babette;, one needs to manually edit the BEAST2 
+the crown age. Without \verb;rbeast2;, one needs to manually edit the BEAST2 
 configuration file, which is tedious and prone to errors. 
@@
 
-This is how to specify a fixed crown age with \verb;babette;:
+This is how to specify a fixed crown age with \verb;rbeast2;:
 
@@
 
-\verb;babette; allows for the same functionality of Tracer. 
+\verb;rbeast2; allows for the same functionality of Tracer. 
 Tracer, among others, shows the effective sample
@@
 estimates. This is called the "burn-in". To remove the burn-in
-in \verb;babette;:
+in \verb;rbeast2;:
 
@@
 
-Then, to calculate the effective sample sizes in \verb;babette;:
+Then, to calculate the effective sample sizes in \verb;rbeast2;:
 
@@
 auto-correlation time and effective sample size. To obtain all these summary statistics 
-of, for example, the estimated birth rate in \verb;babette;:
+of, for example, the estimated birth rate in \verb;rbeast2;:
 
@@
 
-\verb;babette; allows for the same functionality of DensiTree.
+\verb;rbeast2; allows for the same functionality of DensiTree.
 DensiTree displays the phylogenies in a posterior at the same
 time scale over one another, allowing to see the uncertainty in
-topology and branch lengths. To visualize the same in \verb;babette;:
+topology and branch lengths. To visualize the same in \verb;rbeast2;:
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{babette development and other resources}
+\section{rbeast2 development and other resources}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\verb;babette; is free, libre and open source software available from the official R package archive at 
-\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#babette}
+\verb;rbeast2; is free, libre and open source software available from the official R package archive at 
+\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#rbeast2}
 and is licensed under the GNU General Public License v3.0.
 
-\verb;babette; uses the Travis CI \cite{travis} 
+\verb;rbeast2; uses the Travis CI \cite{travis} 
 continuous integration service, which is known to significantly 
@@
 the speed at which new features are added \cite{vasilescu2015}.
-\verb;babette; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
-\verb;babette; follows Hadley Wickham's style guide \cite{style_guide}, which improves software quality \cite{fang2001}.
-\verb;babette; is dependent on multiple packages, which are 
+\verb;rbeast2; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
+\verb;rbeast2; follows Hadley Wickham's style guide \cite{style_guide}, which improves software quality \cite{fang2001}.
+\verb;rbeast2; is dependent on multiple packages, which are 
 \verb;APE; \cite{APE}, 
@@
 
-\verb;babette;'s development takes place on GitHub \cite{github},
-\url{https://github.com/richelbilderbeek/babette}, 
+\verb;rbeast2;'s development takes place on GitHub \cite{github},
+\url{https://github.com/richelbilderbeek/rbeast2}, 
 which accommodates collaboration \cite{perez2016ten} 
 and improves transparency \cite{gorgolewski2016practical}.
-\verb;babette;'s GitHub facilitates feature requests and has guidelines how to do so.
+\verb;rbeast2;'s GitHub facilitates feature requests and has guidelines how to do so.
 
-\verb;babette;'s documentation is extensive. All functions are documented
+\verb;rbeast2;'s documentation is extensive. All functions are documented
 in the package's internal documentation. For quick use, 
@@
 For easy exploration, each exported function's documentation links to related functions.
-Additionally, \verb;babette; has a vignette that demonstrates extensively how
+Additionally, \verb;rbeast2; has a vignette that demonstrates extensively how
 to use it. The GitHub documentation helps to get started, with a dozen examples 
-of BEAUti screenshots with equivalent \verb;babette; code.
+of BEAUti screenshots with equivalent \verb;rbeast2; code.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Citation of babette}
+\section{Citation of rbeast2}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Scientists using \verb;babette; in a published paper can cite this
-article, and/or cite the \verb;babette; package 
+Scientists using \verb;rbeast2; in a published paper can cite this
+article, and/or cite the \verb;rbeast2; package 
 directly. To obtain this citation from within an R script, use:
@@
 \begin{lstlisting}[language=R]
-> citation("babette")
+> citation("rbeast2")
 \end{lstlisting}

### 2018-02-16 article.tex
Feedback @Giappo all in

@@
     BEAST2 is one of the most widely used software tools. 
-     It comes with the graphical programs BEAUti 2 to
-     facilitate the creation of BEAST2 configuration files, and
-     with DensiTree and Tracer, to interpret BEAST2's output files. 
+    It comes with the graphical programs BEAUti 2, DensiTree and Tracer,
+    to create BEAST2 configuration files and to interpret BEAST2's output files. 
     However, when many different alignments or model 
@@
   \textbf{2. }
-    Here, we present a free, libre and open-source package, \verb;rbeast2;, 
+    Here, we present a free, libre and open-source package, \verb;rbeast2;: 
     'BEAUti 2, BEAST2 and Tracer for R', for the R programming language. 
@@
     As \verb;rbeast2; is designed to be of high quality and extendable, 
-    we conclude by describing the further development of the package \\
+    we conclude by describing the further development of the package. \\
 \end{abstract}
@@
 It creates a posterior of jointly-estimated phylogenies and model parameters, 
-from a DNA, RNA or amino acid alignment (see figure \ref{fig:workflow} 
+from one or more DNA, RNA or amino acid alignments (see figure \ref{fig:workflow} 
 for an overview of the workflow). 
@@
 
-BEAUti cannot be called from a command-line script.
+However, BEAUti cannot be called from a command-line script.
 This implies that when the user 
@@
 However, for exploring the output of many BEAST2 runs, 
-one would like a script to collect all parameter ESSes,
+one would like a script to collect all parameters' ESSes,
 parameter traces and posterior phylogenies.
 
-Here, to provide such functionality we present \verb;rbeast2;, 
+Here, to provide such functionality we present \verb;rbeast2;:
 ’BEAUti 2, BEAST2 and Tracer for R’, 
@@
 The difference is that \verb;rbeast2; 
-has its focus on DNA alignments and ultrametric trees, 
+has its focus on DNA alignments and ultrametric trees (that
+is, trees that have their tips measured in the present), 
 where \verb;BEASTmasteR; is used for 

### 2018-02-16 article.tex
Removed comma
Rewrote Examples

@@
 
-\verb;rbeast2;'s main function is \verb;run_beast2;, which, 
+\verb;rbeast2;'s main function is \verb;run_beast2;, which
 configures BEAST2, runs it and parses its output. 
@@
 on the created configuration file to create multiple files
-storing the created posterior. Finally, these output
+storing the posterior created by BEAST2. Finally, these output
 files must be parsed by either Tracer of DensiTree.
@@
 This code will create a (temporary) BEAST2 configuration file,
-using a FASTA file with name \verb;alignment.fas;, 
+from the FASTA file with name \verb;alignment.fas;, 
 using the same default settings as BEAUti.
-\verb;rbeast2; will then execute BEAST2 with that file, and
-parses the output. The output, named \verb;out;, is a list of
-parameter estimates, posterior phylogenies (one for each alignment)
+\verb;rbeast2; will then execute BEAST2 using that file, and
+parses the output. The returned data structure, named \verb;out;, 
+is a list of parameter estimates, posterior phylogenies (one for each alignment)
 and operator acceptances.
@@
 
-The following script shows how to do this in \verb;rbeast2;:
+To do this in \verb;rbeast2;:
 
@@
 \verb;rbeast2; allows for the same functionality of Tracer.
-Tracer, among others, shows the effective sample
-sizes of each posterior's variables. As an MCMC run needs to
-converge first, Tracer discards the first 10\% of all parameter
-estimates. This is called the "burn-in". To remove the burn-in
-in \verb;rbeast2;:
+Tracer works on the values of the parameter estimates sampled
+in the BEAST2 run. This is called the "trace" (hence the name).
+The start of the trace is usually discarded, as an MCMC 
+algorithm (such as used by BEAST2) first has to converge to
+its equilibrium. The start of the trace, called the "burn-in", 
+will be removed, as its parameter estimates are not 
+representative. By default, Tracer discards the first 10\% of all 
+the parameter estimates.
+
+To remove the burn-in from all parameter estimates in \verb;rbeast2;:
 
@@
 
-Then, to calculate the effective sample sizes in \verb;rbeast2;:
+Tracer shows the ESSes of each posterior's variables.
+These ESSes are important to determine the strength of the
+inference. As a rule of thumb, an ESS of 200 is acceptable 
+for any parameter estimate.
+
+To calculate the effective sample sizes (of all estimated variables) in \verb;rbeast2;:
 
@@
 variance, median, mode, geometric mean, 95\% highest posterior density interval, 
-auto-correlation time and effective sample size. To obtain all these summary statistics 
-of, for example, the estimated birth rate in \verb;rbeast2;:
+auto-correlation time and effective sample size. It displays these statistics per
+variable. In \verb;rbeast2;, these summary statistics are collected for
+all estimated parameters at once:
 
@@
 sum_stats <- calc_summary_stats(
-  traces$birthRate, 
+  traces, 
   sample_interval = 1000
@@
 
-\verb;rbeast2; allows for the same functionality of DensiTree.
+\verb;rbeast2; allows for the same functionality as DensiTree.
 DensiTree displays the phylogenies in a posterior at the same
-time scale over one another, allowing to see the uncertainty in
-topology and branch lengths. To visualize the same in \verb;rbeast2;:
+time scale, drawn one over one another, allowing to see the uncertainty in
+topology and branch lengths. To do so in \verb;rbeast2;:
 

### 2018-02-19 article.tex
Implemneted feedback, thanks @rsetienne

@@
     BEAST2 is one of the most widely used software tools. 
-    It comes with the graphical programs BEAUti 2, DensiTree and Tracer,
+    It comes with the graphical user interfaces BEAUti 2, DensiTree and Tracer,
     to create BEAST2 configuration files and to interpret BEAST2's output files. 
     However, when many different alignments or model 
-    setups are required, a workflow of GUI programs is cumbersome. \\
+    setups are required, a workflow of graphical user interfaces is cumbersome. \\
   \textbf{2. }
@@
   \textbf{3. }
-    We describe \verb;rbeast2;'s usage, the novel functionality it provides
-    compared to the tools it is alternative of, and give some examples. \\
+    We describe \verb;rbeast2;'s usage and the novel functionality it provides
+    compared to the original tools and give some examples. \\
   \textbf{4. }
@@
 evolutionary units) relate to each other, 
-but also relevant parameters like extinction and 
-speciation rates can be estimated from them.
+but we also estimate relevant parameters such as extinction and 
+speciation rates.
 
@@
 
-However, for exploring many trees (for instance from simulations) and for
+For exploring many trees (for instance from simulations) and for
 more thorough sensitivity analysis, one would like to loop through 
@@
 DensiTree visualizes the phylogenies of a BEAST2 posterior, with
-many options to improve the displayal of those many phylogenies.
+many options to improve the display of many phylogenies.
 
@@
 
-Here, to provide such functionality we present \verb;rbeast2;:
+Here, we present \verb;rbeast2;:
 ’BEAUti 2, BEAST2 and Tracer for R’, 
@@
 The interface of \verb;rbeast2; mimics the tools it
-is inspired on. This
+is based on. This
 familiarity helps both beginner and experienced BEAST2 users 
@@
 
-\verb;rbeast2; has 7 exported function to run and help run BEAST2.
+Furthermore, \verb;rbeast2; has 7 exported function to run and help run BEAST2.
 One function is used to run BEAST2, others
@@
 
-\verb;rbeast2; has 20 exported function to parse the BEAST2 output
-files and analyse the created posterior. \verb;rbeast2; gives the
+Finally, \verb;rbeast2; has 20 exported function to parse the BEAST2 output
+files and analyze the created posterior. \verb;rbeast2; gives the
 same ESSes and summary statistics as Tracer. The data is formatted
@@
 from the FASTA file with name \verb;alignment.fas;, 
-using the same default settings as BEAUti.
+using the same default settings as BEAUti, which are, 
+among others, a Jukes-Cantor site model, a strict clock, and a Yule birth tree prior.
 \verb;rbeast2; will then execute BEAST2 using that file, and
@@
 is a list of parameter estimates, posterior phylogenies (one for each alignment)
-and operator acceptances.
-
-The default settings for BEAUti (and thus \verb;rbeast2;) are, 
-among others, to use a Jukes-Cantor site model \cite{cantor1969mammalian}, 
-a strict clock, and a Yule birth tree prior \cite{yule}.
+and MCMC operator performance.
 
@@
 Our initial motivation to create \verb;rbeast2; 
-is that we wanted to fix the crown age of a phylogeny.
+was that we wanted to fix the crown age of a phylogeny.
 BEAUti assumes that a phylogeny has a crown age that needs to be jointly-estimated
@@
 
-\verb;rbeast2; allows for the same functionality of Tracer.
+\verb;rbeast2; allows for the same functionality as Tracer.
 Tracer works on the values of the parameter estimates sampled
@@
 
-To remove the burn-in from all parameter estimates in \verb;rbeast2;:
+To remove the burn-in from all parameter estimates in \verb;rbeast2;,
+the following code can be used:
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{rbeast2 development and other resources}
+\section{rbeast2 resources}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\verb;rbeast2; is free, libre and open source software available from the official R package archive at 
+\verb;rbeast2; is free, libre and open source software available 
+from the official R package archive at 
 \url{http://cran.r-project.org/src/contrib/PACKAGES.html\#rbeast2}
@@
 \verb;rbeast2; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
-\verb;rbeast2; follows Hadley Wickham's style guide \cite{style_guide}, which improves software quality \cite{fang2001}.
-\verb;rbeast2; is dependent on multiple packages, which are 
+\verb;rbeast2; follows Hadley Wickham's style guide \cite{style_guide}, 
+which improves software quality \cite{fang2001}.
+\verb;rbeast2; dependends on multiple packages, which are 
 \verb;APE; \cite{APE}, 

### 2018-02-19 article.tex
Indeed do not need TreeSim, thanks @rsetienne
Fix refs
EOD

@@
 analysis of sensitivity of the reconstructed tree to model settings. 
-
 For exploring many trees (for instance from simulations) and for
@@
 clock models and tree priors. 
+One such tool to replace 
+BEAUti is \verb;BEASTmasteR; \cite{beastmaster},
+which focuses on morphological traits and tip-dating, but also 
+supports DNA data.
 
@@
 parameter traces and posterior phylogenies. 
+Examples of R packages to do some of these
+are \verb;rBEAST; \cite{rBEAST_ratmann} and 
+\verb;RBeast; \cite{RBeast_faria}.
 
@@
 \verb;rbeast2; is the first R package that unifies the
-full workflow of working with BEAST2. An
-example to create a BEAST2 input file is 
-\verb;BEASTmasteR; \cite{beastmaster}.
-Also \verb;BEASTmasteR; allows 
-to create BEAST2 configuration files from R. 
-The difference is that \verb;rbeast2; 
-has its focus on DNA alignments and ultrametric trees (that
-is, trees that have their tips measured in the present), 
-where \verb;BEASTmasteR; is used for 
-morphological traits and tip-dating.
-Examples of R packages to parse the BEAST2 output files
-are \verb;rBEAST; \cite{rBEAST} and 
-\verb;RBEAST; \cite{RBEAST}.
+full workflow of working with BEAST2. 
+Where \verb;BEASTmasteR; needs dozens for lines to create
+a BEAST2 configuration file, with \verb;rbeast2; the same 
+can be created by a simple one-liner. Unlike \verb;rBEAST; 
+and \verb;RBeast;, \verb;rbeast2; implements all of Tracer's
+primary functionality. This makes \verb;rbeast2; a complete 
+solution for using BEAST2 from R.
 
@@
 \verb;testit; \cite{testit} and 
-\verb;tracerer; \cite{tracerer} and
-\verb;TreeSim; \cite{TreeSim}.
+\verb;tracerer; \cite{tracerer}.
 

### 2018-02-19 article.tex
Add what rbeast2 cannot do

@@
 as such, that it can easily be visualized using \verb;ggplot2; (for a trace,
-similar to Tracer)
-or \verb;phangorn; \cite{phangorn} (for the phylogenies in a posterior, similar to DensiTree).
+similar to Tracer) or \verb;phangorn; \cite{phangorn} (for 
+the phylogenies in a posterior, similar to DensiTree).
+
+Currently, \verb;rbeast2; does not replace all functionality in BEAUti,
+as it does not supply 3 out of 7 tree priors, nor does it support RNA
+alignments or use of morphological data. The many plug-ins of BEAUti
+are not supported by \verb;rbeast2;. \verb;rbeast2; does not support
+all command-line arguments of BEAST2, does not supply
+the more specialized Tracer analysis options, nor is it as feature-rich
+in plotting options as DensiTree. Up until now, the \verb;rbeast2; features 
+implemented are those requested by users. Further extension of \verb;rbeast2; 
+will have to come from future user requests.
 

### 2018-02-19 article.tex
Removed 'create_', thanks @rsetienne, Hadley Wickham, Hanno Hildenbrandt

@@
   "alignment.fas",
-  site_models = create_hky_site_model(),
-  clock_models = create_rln_clock_model(),
-  tree_priors = create_bd_tree_prior()
+  site_models = hky_site_model(),
+  clock_models = rln_clock_model(),
+  tree_priors = bd_tree_prior()
 )
@@
 \hline
-\verb;create_gtr_site_model; & Create a GTR site model \\
-\verb;create_hky_site_model; & Create an HKY site model \\
-\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
-\verb;create_tn93_site_model; & Create a TN93 site model \\
+\verb;gtr_site_model; & Create a GTR site model \\
+\verb;hky_site_model; & Create an HKY site model \\
+\verb;jc69_site_model; & Create a Jukes-Cantor site model \\
+\verb;tn93_site_model; & Create a TN93 site model \\
 \hline
-\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
-\verb;create_strict_clock_model; & Create a strict clock model \\
+\verb;rln_clock_model; & Create a relaxed log-normal clock model \\
+\verb;strict_clock_model; & Create a strict clock model \\
 \hline
-\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
-\verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
-\verb;create_ccp_tree_prior; & Create a coalescent constant-population tree prior \\
-\verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
-\verb;create_yule_tree_prior; & Create a Yule tree prior \\
+\verb;bd_tree_prior; & Create a birth-death tree prior \\
+\verb;cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
+\verb;ccp_tree_prior; & Create a coalescent constant-population tree prior \\
+\verb;cep_tree_prior; & Create a coalescent exponential-population tree prior \\
+\verb;yule_tree_prior; & Create a Yule tree prior \\
 \hline
-\verb;create_beta_distr; & Create a beta distribution \\
-\verb;create_exp_distr; & Create an exponential distribution \\
-\verb;create_gamma_distr; & Create a gamma distribution \\
-\verb;create_inv_gamma_distr; & Create an inverse gamma distribution \\
-\verb;create_laplace_distr; & Create a Laplace distribution \\
-\verb;create_log_normal_distr; & Create a log-normal distribution \\
-\verb;create_normal_distr; & Create a normal distribution \\
-\verb;create_one_div_x_distr; & Create a 1/X distribution \\
-\verb;create_poisson_distr; & Create a Poisson distribution \\
-\verb;create_uniform_distr; & Create a uniform distribution \\
+\verb;beta_distr; & Create a beta distribution \\
+\verb;exp_distr; & Create an exponential distribution \\
+\verb;gamma_distr; & Create a gamma distribution \\
+\verb;inv_gamma_distr; & Create an inverse gamma distribution \\
+\verb;laplace_distr; & Create a Laplace distribution \\
+\verb;log_normal_distr; & Create a log-normal distribution \\
+\verb;normal_distr; & Create a normal distribution \\
+\verb;one_div_x_distr; & Create a 1/X distribution \\
+\verb;poisson_distr; & Create a Poisson distribution \\
+\verb;uniform_distr; & Create a uniform distribution \\
 \hline
@@
   site_models = list(
-    create_tn93_site_model(), 
-    create_gtr_site_model()
+    tn93_site_model(), 
+    gtr_site_model()
   )
@@
   "alignment.fas",
-  tree_priors = create_yule_tree_prior(
-    birth_rate_distr = create_exp_distr()    
+  tree_priors = yule_tree_prior(
+    birth_rate_distr = exp_distr()    
   )

### 2018-02-19 article.tex
Use 'run_beast2' as main function
Use 'create_' idiom

--- 2018-02-19 article.tex
@@
 \hline
-\verb;create_beast2_input_file; & Creates a BEAST2 input file \\
+\verb;run_beast2; & Run BEAST2 \\
 \hline

### 2018-02-20 article.tex
Add acknowledgements, improve 'Usage' section

@@
 for an overview of the workflow). 
-It is a console application, that needs a configuration file containing 
+It has both a graphical and a command-line interface, 
+that both need a configuration file containing 
 alignments and model parameters.
@@
 to analyze the output of BEAST2, each with a user-friendly graphical user interface. 
-
 Tracer's purpose is to analyze the parameter estimates generated
@@
 \verb;rbeast2; uses a software architecture that expects to be extended.
-
 Furthermore, \verb;rbeast2; has 7 exported function to run and help run BEAST2.
@@
 allow the user to check if a BEAST2 configuration file is indeed valid.
-
 Finally, \verb;rbeast2; has 20 exported function to parse the BEAST2 output
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Examples}
+\section{Usage}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2("alignment.fas")
+out <- run_beast2("anthus_aco.fas")
 \end{lstlisting}
@@
 This code will create a (temporary) BEAST2 configuration file,
-from the FASTA file with name \verb;alignment.fas;, 
+from the FASTA file with name \verb;anthus_aco.fas;, 
 using the same default settings as BEAUti, which are, 
@@
 parses the output. The returned data structure, named \verb;out;, 
-is a list of parameter estimates, posterior phylogenies (one for each alignment)
-and MCMC operator performance.
+is a list of parameter estimates (called \verb;estimates;), posterior 
+phylogenies (called \verb;anthus_aco_trees;)
+and MCMC operator performance (\verb;operators;).
 
@@
 out <- run_beast2(
-  "alignment.fas",
+  "anthus_aco.fas",
   site_models = hky_site_model(),
@@
 time scale, drawn one over one another, allowing to see the uncertainty in
-topology and branch lengths. To do so in \verb;rbeast2;:
+topology and branch lengths. Within the object \verb;out;, 
+the posterior phylogenies are stored as \verb;anthus_aco_trees;,
+and can be plotted as such:
 
 \begin{lstlisting}[language=R, floatplacement=H]
-densitree(out$anthus_aco_trees)
+plot_densitree(out$anthus_aco_trees)
 \end{lstlisting}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Acknowledgements}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Thanks to Yacine Ben Chehida and Paul van Els for supplying their 
+BEAST2 use cases. Thanks to Leonel Herrera-Alsina, Raphael Scherrer 
+and Giovanni Laudanno for their contributions to this package and article.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{plain}

### 2018-02-20 article.tex
Fig at end of paper

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Description}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\verb;rbeast2; is written in the R programming language \cite{R}
+and enables the full BEAST2 workflow from an R function call,
+in a similar way to what BEAUti, DensiTree and Tracer do.
+
+\verb;rbeast2;'s main function is \verb;run_beast2;, which
+configures BEAST2, runs it and parses its output. 
+\verb;run_beast2; needs at least the name of a 
+FASTA file containing a DNA alignment. 
+The default settings for the other arguments of \verb;run_beast2; 
+are identical to BEAUti's and BEAST2's default settings.
+Per alignment, a site model, clock model and tree prior can be chosen.
+Multiple alignments can be used, each with its own (unlinked) site model, 
+clock model and tree prior.
+
+\verb;rbeast2; currently has 61 exported functions to set up  
+a BEAST2 configuration file. 
+\verb;rbeast2; is an alternative for a majority of BEAUti use cases, 
+but does not yet support the full functionality of BEAUti. 
+Because of BEAUti's high number of plugins, 
+\verb;rbeast2; uses a software architecture that expects to be extended.
+Furthermore, \verb;rbeast2; has 7 exported function to run and help run BEAST2.
+One function is used to run BEAST2, others
+allow the user to check if a BEAST2 configuration file is indeed valid.
+Finally, \verb;rbeast2; has 20 exported function to parse the BEAST2 output
+files and analyze the created posterior. \verb;rbeast2; gives the
+same ESSes and summary statistics as Tracer. The data is formatted
+as such, that it can easily be visualized using \verb;ggplot2; (for a trace,
+similar to Tracer) or \verb;phangorn; \cite{phangorn} (for 
+the phylogenies in a posterior, similar to DensiTree).
+
+Currently, \verb;rbeast2; does not replace all functionality in BEAUti,
+as it does not supply 3 out of 7 tree priors, nor does it support RNA
+alignments or use of morphological data. The many plug-ins of BEAUti
+are not supported by \verb;rbeast2;. \verb;rbeast2; does not support
+all command-line arguments of BEAST2, does not supply
+the more specialized Tracer analysis options, nor is it as feature-rich
+in plotting options as DensiTree. Up until now, the \verb;rbeast2; features 
+implemented are those requested by users. Further extension of \verb;rbeast2; 
+will have to come from future user requests.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Usage}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In R, the functions of a package need to be loaded in the global namespace first:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+library(rbeast2)
+\end{lstlisting}
+
+BEAUti, and likewise \verb;rbeast2;, needs at least a FASTA filename
+to produce a BEAST2 configuration file. 
+In BEAUti, this is achieved by loading a FASTA file, 
+then saving an output file using a common
+save file dialog. After this, BEAST2 needs to be invoked
+on the created configuration file to create multiple files
+storing the posterior created by BEAST2. Finally, these output
+files must be parsed by either Tracer of DensiTree.
+In \verb;rbeast2;, the same is achieved by:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+out <- run_beast2("anthus_aco.fas")
+\end{lstlisting}
+
+This code will create a (temporary) BEAST2 configuration file,
+from the FASTA file with name \verb;anthus_aco.fas;, 
+using the same default settings as BEAUti, which are, 
+among others, a Jukes-Cantor site model, a strict clock, and a Yule birth tree prior.
+\verb;rbeast2; will then execute BEAST2 using that file, and
+parses the output. The returned data structure, named \verb;out;, 
+is a list of parameter estimates (called \verb;estimates;), posterior 
+phylogenies (called \verb;anthus_aco_trees;)
+and MCMC operator performance (\verb;operators;).
+
+An example of using a different site model, clock model 
+and tree prior is:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+out <- run_beast2(
+  "anthus_aco.fas",
+  site_models = hky_site_model(),
+  clock_models = rln_clock_model(),
+  tree_priors = bd_tree_prior()
+)
+\end{lstlisting}
+
+This code uses an HKY site model, a relaxed log-normal clock model and a 
+birth-death tree prior, each with their default settings in BEAUti.
+Table \ref{tab:functions} shows an overview of all functions to 
+create site models, clock models and tree priors.
+
+Note that the arguments' names \verb;site_models;, \verb;clock_models; 
+and \verb;tree_priors; are plural, as each of these
+can be (a list of) one or more elements. Each of these arguments must 
+have the same number of elements, so that each alignment has its
+own site model, clock model and tree prior.
+
+An example of two alignments, each with its own site model, is:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+out <- run_beast2(
+  c("anthus_aco.fas", "anthus_nd2.fas"),
+  site_models = list(
+    create_tn93_site_model(), 
+    create_gtr_site_model()
+  )
+)
+\end{lstlisting}
+
+\verb;rbeast2; also uses the same default prior distributions as BEAUti 
+for each of the site models, clock models and tree priors. 
+For example, by default, a Yule tree prior assumes the birth rate 
+follows a uniform distribution, 
+from minus infinity to plus infinity. 
+This assumption implies that negative and positive birth rates are just as likely, 
+where a negative birth rate is biologically impossible (note that 
+in practice, this usually works out just fine).
+One may prefer an exponential distribution instead, 
+as this would assume only positive birth rates, 
+and makes high birth rates unlikely.
+
+To do this in \verb;rbeast2;:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+out <- run_beast2(
+  "anthus_aco.fas",
+  tree_priors = create_yule_tree_prior(
+    birth_rate_distr = create_exp_distr()    
+  )
+)
+\end{lstlisting}
+
+Within this same example, one may specify
+the initial shape parameters of the exponential distribution.
+In BEAST2's implementation, an exponential distribution 
+has one shape parameter: its mean, which can be set to any
+value with \verb;BEAUti;. Within \verb;rbeast2;, to set the 
+initial mean value of the exponential distribution, do:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+out <- run_beast2(
+  get_path("anthus_aco.fas"),
+  tree_priors = create_yule_tree_prior(
+    birth_rate_distr = create_exp_distr(
+      mean = create_mean_param(value = 1.0)
+    )    
+  )
+)
+\end{lstlisting}
+
+Our initial motivation to create \verb;rbeast2; 
+was that we wanted to fix the crown age of a phylogeny.
+BEAUti assumes that a phylogeny has a crown age that needs to be jointly-estimated
+with the phylogeny and other parameters. It does not allow for fixing
+the crown age. Without \verb;rbeast2;, one needs to manually edit the BEAST2 
+configuration file, which is tedious and prone to errors. 
+Fixing the crown ages is especially useful for theoretical experiments,
+as this allows for one less source of variation.
+
+This is how to specify a fixed crown age with \verb;rbeast2;:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+out <- run_beast2(
+  "anthus_aco.fas",
+  posterior_crown_age = 15
+)
+\end{lstlisting}
+
+\verb;rbeast2; allows for the same functionality as Tracer.
+Tracer works on the values of the parameter estimates sampled
+in the BEAST2 run. This is called the "trace" (hence the name).
+The start of the trace is usually discarded, as an MCMC 
+algorithm (such as used by BEAST2) first has to converge to
+its equilibrium. The start of the trace, called the "burn-in", 
+will be removed, as its parameter estimates are not 
+representative. By default, Tracer discards the first 10\% of all 
+the parameter estimates.
+
+To remove the burn-in from all parameter estimates in \verb;rbeast2;,
+the following code can be used:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+traces <- remove_burn_ins(out$estimates)
+\end{lstlisting}
+
+Tracer shows the ESSes of each posterior's variables.
+These ESSes are important to determine the strength of the
+inference. As a rule of thumb, an ESS of 200 is acceptable 
+for any parameter estimate.
+
+To calculate the effective sample sizes (of all estimated variables) in \verb;rbeast2;:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+esses <- calc_esses(
+  traces, 
+  sample_interval = 1000
+)
+\end{lstlisting}
+
+Tracer displays multiple summary statistics for each
+estimated variable: the mean and its standard error, standard deviation,
+variance, median, mode, geometric mean, 95\% highest posterior density interval, 
+auto-correlation time and effective sample size. It displays these statistics per
+variable. In \verb;rbeast2;, these summary statistics are collected for
+all estimated parameters at once:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+sum_stats <- calc_summary_stats(
+  traces, 
+  sample_interval = 1000
+)
+\end{lstlisting}
+
+\verb;rbeast2; allows for the same functionality as DensiTree.
+DensiTree displays the phylogenies in a posterior at the same
+time scale, drawn one over one another, allowing to see the uncertainty in
+topology and branch lengths. Within the object \verb;out;, 
+the posterior phylogenies are stored as \verb;anthus_aco_trees;,
+and can be plotted as such:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+plot_densitree(out$anthus_aco_trees)
+\end{lstlisting}
+
+\begin{table}[]
+\centering
+\begin{tabular}{ | l | l | }
+\hline
+\textbf{Name} & \textbf{Description} \\
+\hline
+\verb;run_beast2; & Run BEAST2 \\
+\hline
+\verb;create_gtr_site_model; & Create a GTR site model \\
+\verb;create_hky_site_model; & Create an HKY site model \\
+\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
+\verb;create_tn93_site_model; & Create a TN93 site model \\
+\hline
+\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
+\verb;create_strict_clock_model; & Create a strict clock model \\
+\hline
+\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
+\verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
+\verb;create_ccp_tree_prior; & Create a coalescent constant-population tree prior \\
+\verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
+\verb;create_yule_tree_prior; & Create a Yule tree prior \\
+\hline
+\verb;create_beta_distr; & Create a beta distribution \\
+\verb;create_exp_distr; & Create an exponential distribution \\
+\verb;create_gamma_distr; & Create a gamma distribution \\
+\verb;create_inv_gamma_distr; & Create an inverse gamma distribution \\
+\verb;create_laplace_distr; & Create a Laplace distribution \\
+\verb;create_log_normal_distr; & Create a log-normal distribution \\
+\verb;create_normal_distr; & Create a normal distribution \\
+\verb;create_one_div_x_distr; & Create a 1/X distribution \\
+\verb;create_poisson_distr; & Create a Poisson distribution \\
+\verb;create_uniform_distr; & Create a uniform distribution \\
+\hline
+\end{tabular}
+\caption{rbeast2's main functions}
+\label{tab:functions}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{rbeast2 resources}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\verb;rbeast2; is free, libre and open source software available 
+from the official R package archive at 
+\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#rbeast2}
+and is licensed under the GNU General Public License v3.0.
+
+\verb;rbeast2; uses the Travis CI \cite{travis} 
+continuous integration service, which is known to significantly 
+increase the the number of bugs exposed \cite{vasilescu2015} and increases
+the speed at which new features are added \cite{vasilescu2015}.
+\verb;rbeast2; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
+\verb;rbeast2; follows Hadley Wickham's style guide \cite{style_guide}, 
+which improves software quality \cite{fang2001}.
+\verb;rbeast2; dependends on multiple packages, which are 
+\verb;APE; \cite{APE}, 
+\verb;beautier; \cite{beautier},
+\verb;beastier; \cite{beastier},
+\verb;devtools; \cite{devtools},
+\verb;geiger; \cite{GEIGER},
+\verb;ggplot2; \cite{ggplot2},
+\verb;knitr; \cite{knitr},
+\verb;phangorn; \cite{phangorn},
+\verb;rmarkdown; \cite{rmarkdown},
+\verb;seqinr; \cite{seqinr},
+\verb;stringr; \cite{stringr},
+\verb;testit; \cite{testit} and 
+\verb;tracerer; \cite{tracerer}.
+
+\verb;rbeast2;'s development takes place on GitHub \cite{github},
+\url{https://github.com/richelbilderbeek/rbeast2}, 
+which accommodates collaboration \cite{perez2016ten} 
+and improves transparency \cite{gorgolewski2016practical}.
+\verb;rbeast2;'s GitHub facilitates feature requests and has guidelines how to do so.
+
+\verb;rbeast2;'s documentation is extensive. All functions are documented
+in the package's internal documentation. For quick use, 
+each exported function shows a minimal example. 
+For easy exploration, each exported function's documentation links to related functions.
+Additionally, \verb;rbeast2; has a vignette that demonstrates extensively how
+to use it. The GitHub documentation helps to get started, with a dozen examples 
+of BEAUti screenshots with equivalent \verb;rbeast2; code.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Citation of rbeast2}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Scientists using \verb;rbeast2; in a published paper can cite this
+article, and/or cite the \verb;rbeast2; package 
+directly. To obtain this citation from within an R script, use:
+
+\begin{lstlisting}[language=R]
+> citation("rbeast2")
+\end{lstlisting}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Acknowledgements}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Thanks to Yacine Ben Chehida and Paul van Els for supplying their 
+BEAST2 use cases. Thanks to Leonel Herrera-Alsina, Raphael Scherrer 
+and Giovanni Laudanno for their contributions to this package and article.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Description}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\verb;rbeast2; is written in the R programming language \cite{R}
-and enables the full BEAST2 workflow from an R function call,
-in a similar way to what BEAUti, DensiTree and Tracer do.
-
-\verb;rbeast2;'s main function is \verb;run_beast2;, which
-configures BEAST2, runs it and parses its output. 
-\verb;run_beast2; needs at least the name of a 
-FASTA file containing a DNA alignment. 
-The default settings for the other arguments of \verb;run_beast2; 
-are identical to BEAUti's and BEAST2's default settings.
-Per alignment, a site model, clock model and tree prior can be chosen.
-Multiple alignments can be used, each with its own (unlinked) site model, 
-clock model and tree prior.
-
-\verb;rbeast2; currently has 61 exported functions to set up  
-a BEAST2 configuration file. 
-\verb;rbeast2; is an alternative for a majority of BEAUti use cases, 
-but does not yet support the full functionality of BEAUti. 
-Because of BEAUti's high number of plugins, 
-\verb;rbeast2; uses a software architecture that expects to be extended.
-Furthermore, \verb;rbeast2; has 7 exported function to run and help run BEAST2.
-One function is used to run BEAST2, others
-allow the user to check if a BEAST2 configuration file is indeed valid.
-Finally, \verb;rbeast2; has 20 exported function to parse the BEAST2 output
-files and analyze the created posterior. \verb;rbeast2; gives the
-same ESSes and summary statistics as Tracer. The data is formatted
-as such, that it can easily be visualized using \verb;ggplot2; (for a trace,
-similar to Tracer) or \verb;phangorn; \cite{phangorn} (for 
-the phylogenies in a posterior, similar to DensiTree).
-
-Currently, \verb;rbeast2; does not replace all functionality in BEAUti,
-as it does not supply 3 out of 7 tree priors, nor does it support RNA
-alignments or use of morphological data. The many plug-ins of BEAUti
-are not supported by \verb;rbeast2;. \verb;rbeast2; does not support
-all command-line arguments of BEAST2, does not supply
-the more specialized Tracer analysis options, nor is it as feature-rich
-in plotting options as DensiTree. Up until now, the \verb;rbeast2; features 
-implemented are those requested by users. Further extension of \verb;rbeast2; 
-will have to come from future user requests.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Usage}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In R, the functions of a package need to be loaded in the global namespace first:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-library(rbeast2)
-\end{lstlisting}
-
-BEAUti, and likewise \verb;rbeast2;, needs at least a FASTA filename
-to produce a BEAST2 configuration file. 
-In BEAUti, this is achieved by loading a FASTA file, 
-then saving an output file using a common
-save file dialog. After this, BEAST2 needs to be invoked
-on the created configuration file to create multiple files
-storing the posterior created by BEAST2. Finally, these output
-files must be parsed by either Tracer of DensiTree.
-
-In \verb;rbeast2;, the same is achieved by:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2("anthus_aco.fas")
-\end{lstlisting}
-
-This code will create a (temporary) BEAST2 configuration file,
-from the FASTA file with name \verb;anthus_aco.fas;, 
-using the same default settings as BEAUti, which are, 
-among others, a Jukes-Cantor site model, a strict clock, and a Yule birth tree prior.
-\verb;rbeast2; will then execute BEAST2 using that file, and
-parses the output. The returned data structure, named \verb;out;, 
-is a list of parameter estimates (called \verb;estimates;), posterior 
-phylogenies (called \verb;anthus_aco_trees;)
-and MCMC operator performance (\verb;operators;).
-
-An example of using a different site model, clock model 
-and tree prior is:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(
-  "anthus_aco.fas",
-  site_models = hky_site_model(),
-  clock_models = rln_clock_model(),
-  tree_priors = bd_tree_prior()
-)
-\end{lstlisting}
-
-This code uses an HKY site model, a relaxed log-normal clock model and a 
-birth-death tree prior, each with their default settings in BEAUti.
-Table \ref{tab:functions} shows an overview of all functions to 
-create site models, clock models and tree priors.
-
-\begin{table}[]
-\centering
-\begin{tabular}{ | l | l | }
-\hline
-\textbf{Name} & \textbf{Description} \\
-\hline
-\verb;run_beast2; & Run BEAST2 \\
-\hline
-\verb;create_gtr_site_model; & Create a GTR site model \\
-\verb;create_hky_site_model; & Create an HKY site model \\
-\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
-\verb;create_tn93_site_model; & Create a TN93 site model \\
-\hline
-\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
-\verb;create_strict_clock_model; & Create a strict clock model \\
-\hline
-\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
-\verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
-\verb;create_ccp_tree_prior; & Create a coalescent constant-population tree prior \\
-\verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
-\verb;create_yule_tree_prior; & Create a Yule tree prior \\
-\hline
-\verb;create_beta_distr; & Create a beta distribution \\
-\verb;create_exp_distr; & Create an exponential distribution \\
-\verb;create_gamma_distr; & Create a gamma distribution \\
-\verb;create_inv_gamma_distr; & Create an inverse gamma distribution \\
-\verb;create_laplace_distr; & Create a Laplace distribution \\
-\verb;create_log_normal_distr; & Create a log-normal distribution \\
-\verb;create_normal_distr; & Create a normal distribution \\
-\verb;create_one_div_x_distr; & Create a 1/X distribution \\
-\verb;create_poisson_distr; & Create a Poisson distribution \\
-\verb;create_uniform_distr; & Create a uniform distribution \\
-\hline
-\end{tabular}
-\caption{rbeast2's main functions}
-\label{tab:functions}
-\end{table}
-
-Note that the arguments' names \verb;site_models;, \verb;clock_models; 
-and \verb;tree_priors; are plural, as each of these
-can be (a list of) one or more elements. Each of these arguments must 
-have the same number of elements, so that each alignment has its
-own site model, clock model and tree prior.
-
-An example of two alignments, each with its own site model, is:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(
-  c("anthus_aco.fas", "anthus_nd2.fas"),
-  site_models = list(
-    create_tn93_site_model(), 
-    create_gtr_site_model()
-  )
-)
-\end{lstlisting}
-
-\verb;rbeast2; also uses the same default prior distributions as BEAUti 
-for each of the site models, clock models and tree priors. 
-For example, by default, a Yule tree prior assumes the birth rate 
-follows a uniform distribution, 
-from minus infinity to plus infinity. 
-This assumption implies that negative and positive birth rates are just as likely, 
-where a negative birth rate is biologically impossible (note that 
-in practice, this usually works out just fine).
-One may prefer an exponential distribution instead, 
-as this would assume only positive birth rates, 
-and makes high birth rates unlikely.
-
-To do this in \verb;rbeast2;:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(
-  "alignment.fas",
-  tree_priors = create_yule_tree_prior(
-    birth_rate_distr = create_exp_distr()    
-  )
-)
-\end{lstlisting}
-
-Our initial motivation to create \verb;rbeast2; 
-was that we wanted to fix the crown age of a phylogeny.
-BEAUti assumes that a phylogeny has a crown age that needs to be jointly-estimated
-with the phylogeny and other parameters. It does not allow for fixing
-the crown age. Without \verb;rbeast2;, one needs to manually edit the BEAST2 
-configuration file, which is tedious and prone to errors. 
-Fixing the crown ages is especially useful for theoretical experiments,
-as this allows for one less source of variation.
-
-This is how to specify a fixed crown age with \verb;rbeast2;:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(
-  "alignment.fas",
-  posterior_crown_age = 15
-)
-\end{lstlisting}
-
-\verb;rbeast2; allows for the same functionality as Tracer.
-Tracer works on the values of the parameter estimates sampled
-in the BEAST2 run. This is called the "trace" (hence the name).
-The start of the trace is usually discarded, as an MCMC 
-algorithm (such as used by BEAST2) first has to converge to
-its equilibrium. The start of the trace, called the "burn-in", 
-will be removed, as its parameter estimates are not 
-representative. By default, Tracer discards the first 10\% of all 
-the parameter estimates.
-
-To remove the burn-in from all parameter estimates in \verb;rbeast2;,
-the following code can be used:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-traces <- remove_burn_ins(out$estimates)
-\end{lstlisting}
-
-Tracer shows the ESSes of each posterior's variables.
-These ESSes are important to determine the strength of the
-inference. As a rule of thumb, an ESS of 200 is acceptable 
-for any parameter estimate.
-
-To calculate the effective sample sizes (of all estimated variables) in \verb;rbeast2;:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-esses <- calc_esses(
-  traces, 
-  sample_interval = 1000
-)
-\end{lstlisting}
-
-Tracer displays multiple summary statistics for each
-estimated variable: the mean and its standard error, standard deviation,
-variance, median, mode, geometric mean, 95\% highest posterior density interval, 
-auto-correlation time and effective sample size. It displays these statistics per
-variable. In \verb;rbeast2;, these summary statistics are collected for
-all estimated parameters at once:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-sum_stats <- calc_summary_stats(
-  traces, 
-  sample_interval = 1000
-)
-\end{lstlisting}
-
-\verb;rbeast2; allows for the same functionality as DensiTree.
-DensiTree displays the phylogenies in a posterior at the same
-time scale, drawn one over one another, allowing to see the uncertainty in
-topology and branch lengths. Within the object \verb;out;, 
-the posterior phylogenies are stored as \verb;anthus_aco_trees;,
-and can be plotted as such:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-plot_densitree(out$anthus_aco_trees)
-\end{lstlisting}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{rbeast2 resources}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\verb;rbeast2; is free, libre and open source software available 
-from the official R package archive at 
-\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#rbeast2}
-and is licensed under the GNU General Public License v3.0.
-
-\verb;rbeast2; uses the Travis CI \cite{travis} 
-continuous integration service, which is known to significantly 
-increase the the number of bugs exposed \cite{vasilescu2015} and increases
-the speed at which new features are added \cite{vasilescu2015}.
-\verb;rbeast2; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
-\verb;rbeast2; follows Hadley Wickham's style guide \cite{style_guide}, 
-which improves software quality \cite{fang2001}.
-\verb;rbeast2; dependends on multiple packages, which are 
-\verb;APE; \cite{APE}, 
-\verb;beautier; \cite{beautier},
-\verb;beastier; \cite{beastier},
-\verb;devtools; \cite{devtools},
-\verb;geiger; \cite{GEIGER},
-\verb;ggplot2; \cite{ggplot2},
-\verb;knitr; \cite{knitr},
-\verb;phangorn; \cite{phangorn},
-\verb;rmarkdown; \cite{rmarkdown},
-\verb;seqinr; \cite{seqinr},
-\verb;stringr; \cite{stringr},
-\verb;testit; \cite{testit} and 
-\verb;tracerer; \cite{tracerer}.
-
-\verb;rbeast2;'s development takes place on GitHub \cite{github},
-\url{https://github.com/richelbilderbeek/rbeast2}, 
-which accommodates collaboration \cite{perez2016ten} 
-and improves transparency \cite{gorgolewski2016practical}.
-\verb;rbeast2;'s GitHub facilitates feature requests and has guidelines how to do so.
-
-\verb;rbeast2;'s documentation is extensive. All functions are documented
-in the package's internal documentation. For quick use, 
-each exported function shows a minimal example. 
-For easy exploration, each exported function's documentation links to related functions.
-Additionally, \verb;rbeast2; has a vignette that demonstrates extensively how
-to use it. The GitHub documentation helps to get started, with a dozen examples 
-of BEAUti screenshots with equivalent \verb;rbeast2; code.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Citation of rbeast2}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Scientists using \verb;rbeast2; in a published paper can cite this
-article, and/or cite the \verb;rbeast2; package 
-directly. To obtain this citation from within an R script, use:
-
-\begin{lstlisting}[language=R]
-> citation("rbeast2")
-\end{lstlisting}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowledgements}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Thanks to Yacine Ben Chehida and Paul van Els for supplying their 
-BEAST2 use cases. Thanks to Leonel Herrera-Alsina, Raphael Scherrer 
-and Giovanni Laudanno for their contributions to this package and article.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \bibliographystyle{plain}

### 2018-02-21 article.tex
Processed feedback, thanks @rsetienne

@@
 clock models and tree priors. 
-One such tool to replace 
-BEAUti is \verb;BEASTmasteR; \cite{beastmaster},
+One such tool to replace BEAUti is \verb;BEASTmasteR; \cite{beastmaster},
 which focuses on morphological traits and tip-dating, but also 
-supports DNA data.
+supports DNA data. \verb;BEASTmasteR;, however, takes hundreds of
+lines to set up (next to a Miscrosft Excel spreadsheet), 
+resulting in only 7 citations, all before 2017.
 
@@
 parameter traces and posterior phylogenies.
-Examples of R packages to do some of these
+There is no single package that offers a complete solution,
+but examples of R packages that offer a partial solution
 are \verb;rBEAST; \cite{rBEAST_ratmann} and 
@@
 full workflow of working with BEAST2. 
-Where \verb;BEASTmasteR; needs dozens for lines to create
+Whilst \verb;BEASTmasteR; needs hundreds of lines to create
 a BEAST2 configuration file, with \verb;rbeast2; the same 
@@
 in a similar way to what BEAUti, DensiTree and Tracer do.
-
 \verb;rbeast2;'s main function is \verb;run_beast2;, which
@@
 Currently, \verb;rbeast2; does not replace all functionality in BEAUti,
-as it does not supply 3 out of 7 tree priors, nor does it support RNA
+as it does not provide 3 out of 7 tree priors, nor does it support RNA
 alignments or use of morphological data. The many plug-ins of BEAUti
-are not supported by \verb;rbeast2;. \verb;rbeast2; does not support
-all command-line arguments of BEAST2, does not supply
+are not yet supported by \verb;rbeast2;. \verb;rbeast2; does not support
+all command-line arguments of BEAST2, does not provide
 the more specialized Tracer analysis options, nor is it as feature-rich
@@
 implemented are those requested by users. Further extension of \verb;rbeast2; 
-will have to come from future user requests.
+will be based on future user requests.
 
@@
 then saving an output file using a common
-save file dialog. After this, BEAST2 needs to be invoked
-on the created configuration file to create multiple files
-storing the posterior created by BEAST2. Finally, these output
+save file dialog. After this, BEAST2 needs to be applied to
+the created configuration file. It creates multiple files
+storing the posterior. These output
 files must be parsed by either Tracer of DensiTree.
-In \verb;rbeast2;, the same is achieved by:
+In \verb;rbeast2;, all this is achieved by:
 
@@
 and MCMC operator performance (\verb;operators;).
-
 An example of using a different site model, clock model 
@@
   "anthus_aco.fas",
-  site_models = hky_site_model(),
-  clock_models = rln_clock_model(),
-  tree_priors = bd_tree_prior()
+  site_models = create_hky_site_model(),
+  clock_models = create_rln_clock_model(),
+  tree_priors = create_bd_tree_prior()
 )
@@
 create site models, clock models and tree priors.
-
 Note that the arguments' names \verb;site_models;, \verb;clock_models; 
@@
 own site model, clock model and tree prior. 
-
 An example of two alignments, each with its own site model, is:
@@
 for each of the site models, clock models and tree priors. 
-For example, by default, a Yule tree prior assumes the birth rate 
+For example, by default, a Yule tree prior assumes that the birth rate 
 follows a uniform distribution, 
@@
 and makes high birth rates unlikely.
-
 To do this in \verb;rbeast2;:
@@
 out <- run_beast2(
-  get_path("anthus_aco.fas"),
+  "anthus_aco.fas",
   tree_priors = create_yule_tree_prior(
@@
 as this allows for one less source of variation.
-
 This is how to specify a fixed crown age with \verb;rbeast2;:
@@
 the parameter estimates. 
-
 To remove the burn-in from all parameter estimates in \verb;rbeast2;,
@@
 for any parameter estimate.
-
 To calculate the effective sample sizes (of all estimated variables) in \verb;rbeast2;:
@@
 continuous integration service, which is known to significantly 
-increase the the number of bugs exposed \cite{vasilescu2015} and increases
+increase the number of bugs exposed \cite{vasilescu2015} and increases
 the speed at which new features are added \cite{vasilescu2015}.

### 2018-02-22 article.tex
Process feedback, thanks @rsetienne

@@
 supports DNA data. \verb;BEASTmasteR;, however, takes hundreds of
-lines to set up (next to a Miscrosft Excel spreadsheet), 
-resulting in only 7 citations, all before 2017.
+lines to R code and a Miscrosft Excel file.
 
@@
 but examples of R packages that offer a partial solution
-are \verb;rBEAST; \cite{rBEAST_ratmann} and 
+are \verb;BEASTmasteR;, \verb;rBEAST; 
+\cite{rBEAST_ratmann} and 
 \verb;RBeast; \cite{RBeast_faria}.
@@
 a BEAST2 configuration file, with \verb;rbeast2; the same 
-can be created by a simple one-liner. Unlike \verb;rBEAST; 
-and \verb;RBeast;, \verb;rbeast2; implements all of Tracer's
-primary functionality. This makes \verb;rbeast2; a complete 
-solution for using BEAST2 from R.
+can be created by a simple one-liner. Unlike \verb;BEASTmasteR;,
+\verb;rBEAST; and \verb;RBeast;, \verb;rbeast2; implements all of Tracer's
+primary functionality. There exists no package that calls BEAST2 from R.
+\verb;rbeast2; sets up BEAST2, runs it, and analyzes its
+results, making it a complete solution for using BEAST2 from R.
 

### 2018-02-26 article.tex
Name is 'babette' again

@@
 
-\title{rbeast2: BEAUti 2, BEAST2 and Tracer for R}
+\title{babette: BEAUti 2, BEAST2 and Tracer for R}
 \author{Rich\`el J.C. Bilderbeek, Rampal S. Etienne}
@@
   \textbf{2. }
-    Here, we present a free, libre and open-source package, \verb;rbeast2;: 
+    Here, we present a free, libre and open-source package, \verb;babette;: 
     'BEAUti 2, BEAST2 and Tracer for R', for the R programming language. 
-    \verb;rbeast2; creates BEAST2 input files, runs BEAST2 and parses its results, 
+    \verb;babette; creates BEAST2 input files, runs BEAST2 and parses its results, 
     all from an R function call. \\
   \textbf{3. }
-    We describe \verb;rbeast2;'s usage and the novel functionality it provides
+    We describe \verb;babette;'s usage and the novel functionality it provides
     compared to the original tools and give some examples. \\
   \textbf{4. }
-    As \verb;rbeast2; is designed to be of high quality and extendable, 
+    As \verb;babette; is designed to be of high quality and extendable, 
     we conclude by describing the further development of the package. \\
@@
 
-Here, we present \verb;rbeast2;:
+Here, we present \verb;babette;:
 ’BEAUti 2, BEAST2 and Tracer for R’, 
@@
 reduces the chances of errors in such repetitive actions.
-The interface of \verb;rbeast2; mimics the tools it
+The interface of \verb;babette; mimics the tools it
 is based on. This
 familiarity helps both beginner and experienced BEAST2 users 
-to make the step from those tools to \verb;rbeast2;.
-\verb;rbeast2; enables the creation of a single-script 
+to make the step from those tools to \verb;babette;.
+\verb;babette; enables the creation of a single-script 
 pipeline from sequence alignments to posterior analysis in R.
 
-\verb;rbeast2; is the first R package that unifies the
+\verb;babette; is the first R package that unifies the
 full workflow of working with BEAST2. 
 Whilst \verb;BEASTmasteR; needs hundreds of lines to create
-a BEAST2 configuration file, with \verb;rbeast2; the same 
+a BEAST2 configuration file, with \verb;babette; the same 
 can be created by a simple one-liner. Unlike \verb;BEASTmasteR;,
-\verb;rBEAST; and \verb;RBeast;, \verb;rbeast2; implements all of Tracer's
+\verb;rBEAST; and \verb;RBeast;, \verb;babette; implements all of Tracer's
 primary functionality. There exists no package that calls BEAST2 from R.
-\verb;rbeast2; sets up BEAST2, runs it, and analyzes its
+\verb;babette; sets up BEAST2, runs it, and analyzes its
 results, making it a complete solution for using BEAST2 from R.
@@
 
-\verb;rbeast2; is written in the R programming language \cite{R}
+\verb;babette; is written in the R programming language \cite{R}
 and enables the full BEAST2 workflow from an R function call,
 in a similar way to what BEAUti, DensiTree and Tracer do.
-\verb;rbeast2;'s main function is \verb;run_beast2;, which
+\verb;babette;'s main function is \verb;run_beast2;, which
 configures BEAST2, runs it and parses its output. 
@@
 
-\verb;rbeast2; currently has 61 exported functions to set up  
+\verb;babette; currently has 61 exported functions to set up  
 a BEAST2 configuration file. 
-\verb;rbeast2; is an alternative for a majority of BEAUti use cases, 
+\verb;babette; is an alternative for a majority of BEAUti use cases, 
 but does not yet support the full functionality of BEAUti. 
 Because of BEAUti's high number of plugins, 
-\verb;rbeast2; uses a software architecture that expects to be extended.
-Furthermore, \verb;rbeast2; has 7 exported function to run and help run BEAST2.
+\verb;babette; uses a software architecture that expects to be extended.
+Furthermore, \verb;babette; has 7 exported function to run and help run BEAST2.
 One function is used to run BEAST2, others
 allow the user to check if a BEAST2 configuration file is indeed valid.
-Finally, \verb;rbeast2; has 20 exported function to parse the BEAST2 output
-files and analyze the created posterior. \verb;rbeast2; gives the
+Finally, \verb;babette; has 20 exported function to parse the BEAST2 output
+files and analyze the created posterior. \verb;babette; gives the
 same ESSes and summary statistics as Tracer. The data is formatted
@@
 
-Currently, \verb;rbeast2; does not replace all functionality in BEAUti,
+Currently, \verb;babette; does not replace all functionality in BEAUti,
 as it does not provide 3 out of 7 tree priors, nor does it support RNA
 alignments or use of morphological data. The many plug-ins of BEAUti
-are not yet supported by \verb;rbeast2;. \verb;rbeast2; does not support
+are not yet supported by \verb;babette;. \verb;babette; does not support
 all command-line arguments of BEAST2, does not provide
 the more specialized Tracer analysis options, nor is it as feature-rich
-in plotting options as DensiTree. Up until now, the \verb;rbeast2; features 
-implemented are those requested by users. Further extension of \verb;rbeast2; 
+in plotting options as DensiTree. Up until now, the \verb;babette; features 
+implemented are those requested by users. Further extension of \verb;babette; 
 will be based on future user requests.
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-library(rbeast2)
+library(babette)
 \end{lstlisting}
 
-BEAUti, and likewise \verb;rbeast2;, needs at least a FASTA filename
+BEAUti, and likewise \verb;babette;, needs at least a FASTA filename
 to produce a BEAST2 configuration file. 
@@
 files must be parsed by either Tracer of DensiTree.
-In \verb;rbeast2;, all this is achieved by:
+In \verb;babette;, all this is achieved by:
 
@@
 among others, a Jukes-Cantor site model, a strict clock, and a Yule birth tree prior.
-\verb;rbeast2; will then execute BEAST2 using that file, and
+\verb;babette; will then execute BEAST2 using that file, and
 parses the output. The returned data structure, named \verb;out;, 
@@
 
-\verb;rbeast2; also uses the same default prior distributions as BEAUti 
+\verb;babette; also uses the same default prior distributions as BEAUti 
 for each of the site models, clock models and tree priors. 
@@
 and makes high birth rates unlikely.
-To do this in \verb;rbeast2;:
+To do this in \verb;babette;:
 
@@
 has one shape parameter: its mean, which can be set to any
-value with \verb;BEAUti;. Within \verb;rbeast2;, to set the 
+value with \verb;BEAUti;. Within \verb;babette;, to set the 
 initial mean value of the exponential distribution, do:
@@
 
-Our initial motivation to create \verb;rbeast2; 
+Our initial motivation to create \verb;babette; 
 was that we wanted to fix the crown age of a phylogeny.
@@
 with the phylogeny and other parameters. It does not allow for fixing
-the crown age. Without \verb;rbeast2;, one needs to manually edit the BEAST2 
+the crown age. Without \verb;babette;, one needs to manually edit the BEAST2 
 configuration file, which is tedious and prone to errors. 
@@
 as this allows for one less source of variation.
-This is how to specify a fixed crown age with \verb;rbeast2;:
+This is how to specify a fixed crown age with \verb;babette;:
 
@@
 
-\verb;rbeast2; allows for the same functionality as Tracer.
+\verb;babette; allows for the same functionality as Tracer.
 Tracer works on the values of the parameter estimates sampled
@@
 the parameter estimates. 
-To remove the burn-in from all parameter estimates in \verb;rbeast2;,
+To remove the burn-in from all parameter estimates in \verb;babette;,
 the following code can be used:
@@
 for any parameter estimate.
-To calculate the effective sample sizes (of all estimated variables) in \verb;rbeast2;:
+To calculate the effective sample sizes (of all estimated variables) in \verb;babette;:
 
@@
 auto-correlation time and effective sample size. It displays these statistics per
-variable. In \verb;rbeast2;, these summary statistics are collected for
+variable. In \verb;babette;, these summary statistics are collected for
 all estimated parameters at once:
@@
 
-\verb;rbeast2; allows for the same functionality as DensiTree.
+\verb;babette; allows for the same functionality as DensiTree.
 DensiTree displays the phylogenies in a posterior at the same
@@
 \end{tabular}
-\caption{rbeast2's main functions}
+\caption{babette's main functions}
 \label{tab:functions}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{rbeast2 resources}
+\section{babette resources}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\verb;rbeast2; is free, libre and open source software available 
+\verb;babette; is free, libre and open source software available 
 from the official R package archive at 
-\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#rbeast2}
+\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#babette}
 and is licensed under the GNU General Public License v3.0.
 
-\verb;rbeast2; uses the Travis CI \cite{travis} 
+\verb;babette; uses the Travis CI \cite{travis} 
 continuous integration service, which is known to significantly 
@@
 the speed at which new features are added \cite{vasilescu2015}.
-\verb;rbeast2; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
-\verb;rbeast2; follows Hadley Wickham's style guide \cite{style_guide}, 
+\verb;babette; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
+\verb;babette; follows Hadley Wickham's style guide \cite{style_guide}, 
 which improves software quality \cite{fang2001}.
-\verb;rbeast2; dependends on multiple packages, which are 
+\verb;babette; dependends on multiple packages, which are 
 \verb;APE; \cite{APE}, 
@@
 
-\verb;rbeast2;'s development takes place on GitHub \cite{github},
-\url{https://github.com/richelbilderbeek/rbeast2}, 
+\verb;babette;'s development takes place on GitHub \cite{github},
+\url{https://github.com/richelbilderbeek/babette}, 
 which accommodates collaboration \cite{perez2016ten} 
 and improves transparency \cite{gorgolewski2016practical}.
-\verb;rbeast2;'s GitHub facilitates feature requests and has guidelines how to do so.
+\verb;babette;'s GitHub facilitates feature requests and has guidelines how to do so.
 
-\verb;rbeast2;'s documentation is extensive. All functions are documented
+\verb;babette;'s documentation is extensive. All functions are documented
 in the package's internal documentation. For quick use, 
@@
 For easy exploration, each exported function's documentation links to related functions.
-Additionally, \verb;rbeast2; has a vignette that demonstrates extensively how
+Additionally, \verb;babette; has a vignette that demonstrates extensively how
 to use it. The GitHub documentation helps to get started, with a dozen examples 
-of BEAUti screenshots with equivalent \verb;rbeast2; code.
+of BEAUti screenshots with equivalent \verb;babette; code.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Citation of rbeast2}
+\section{Citation of babette}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Scientists using \verb;rbeast2; in a published paper can cite this
-article, and/or cite the \verb;rbeast2; package 
+Scientists using \verb;babette; in a published paper can cite this
+article, and/or cite the \verb;babette; package 
 directly. To obtain this citation from within an R script, use:
@@
 \begin{lstlisting}[language=R]
-> citation("rbeast2")
+> citation("babette")
 \end{lstlisting}
@@
     to infer a posterior, storing it in multiple files (5). These results
-    are visualized using DensiTree (6) and Tracer (7). rbeast2 allows
+    are visualized using DensiTree (6) and Tracer (7). babette allows
     for the same workflow, all from an R function call.

### 2018-02-26 article.tex
Add affiliated university
Added feedback from @rsetienne

@@
 
+% Affiliations
+\usepackage{authblk}
+
 \title{babette: BEAUti 2, BEAST2 and Tracer for R}
-\author{Rich\`el J.C. Bilderbeek, Rampal S. Etienne}
+\author[1]{Rich\`el J.C. Bilderbeek}
+\author[1]{Rampal S. Etienne}
+\affil[1]{Groningen Institute for Evolutionary Life Sciences, University of Groningen, Groningen, The Netherlands}
 
@@
 \usepackage{bm}
+
 \usetikzlibrary{arrows,automata}
@@
     We describe \verb;babette;'s usage and the novel functionality it provides
-    compared to the original tools and give some examples. \\
+    compared to the original tools and we give some examples. \\
   \textbf{4. }
@@
 speciation rates.
-
 There are many phylogenetics tools available to obtain an estimate 
@@
 for an overview of the workflow). 
-It has both a graphical and a command-line interface, 
+It has a graphical and a command-line interface, 
 that both need a configuration file containing 
 alignments and model parameters.
-
 BEAST2 is bundled with BEAUti 2 \cite{drummond2012bayesian} ('BEAUti' from now on), 
 a desktop application to create a BEAST2 configuration file.
-BEAUti has a user-friendly graphical user interface, with helpful and 
-reasonable default settings.
+BEAUti has a user-friendly graphical user interface, with helpful
+default settings.
 As such, BEAUti is an attractive alternative 
@@
 supports DNA data. \verb;BEASTmasteR;, however, takes hundreds of
-lines to R code and a Miscrosft Excel file.
+lines of R code to setup the BEAST2 model configuration 
+and a Microsoft Excel file to specify alignment files.
 
@@
 \verb;RBeast; \cite{RBeast_faria}. 
+\verb;BEASTmasteR; and \verb;RBeast; are incomplete
+packages, where \verb;rBEAST; does not aim to be a 
+package to be used by most BEAST2 users.
 
@@
 pipeline from sequence alignments to posterior analysis in R.
-
-\verb;babette; is the first R package that unifies the
-full workflow of working with BEAST2. 
-Whilst \verb;BEASTmasteR; needs hundreds of lines to create
-a BEAST2 configuration file, with \verb;babette; the same 
-can be created by a simple one-liner. Unlike \verb;BEASTmasteR;,
-\verb;rBEAST; and \verb;RBeast;, \verb;babette; implements all of Tracer's
-primary functionality. There exists no package that calls BEAST2 from R.
-\verb;babette; sets up BEAST2, runs it, and analyzes its
-results, making it a complete solution for using BEAST2 from R.
 
@@
 a BEAST2 configuration file. 
-\verb;babette; is an alternative for a majority of BEAUti use cases, 
-but does not yet support the full functionality of BEAUti. 
+\verb;babette; is an alternative for a majority of BEAUti use cases.
 Because of BEAUti's high number of plugins, 
-\verb;babette; uses a software architecture that expects to be extended.
+\verb;babette; uses a software architecture that is designed to be extended.
 Furthermore, \verb;babette; has 7 exported function to run and help run BEAST2.
@@
 \end{lstlisting}
-
 BEAUti, and likewise \verb;babette;, needs at least a FASTA filename
@@
 \end{lstlisting}
-
 This code will create a (temporary) BEAST2 configuration file,
-from the FASTA file with name \verb;anthus_aco.fas;, 
+from the FASTA file with name \verb;anthus_aco.fas; (which
+is supplied with the package, from \cite{VanEls2018}), 
 using the same default settings as BEAUti, which are, 
@@
 is a list of parameter estimates (called \verb;estimates;), posterior 
-phylogenies (called \verb;anthus_aco_trees;)
-and MCMC operator performance (\verb;operators;).
+phylogenies (called \verb;anthus_aco_trees;, named after
+the alignment's name) and MCMC operator performance (\verb;operators;).
 An example of using a different site model, clock model 
@@
 \end{lstlisting}
-
 This code uses an HKY site model, a relaxed log-normal clock model and a 
@@
 \end{lstlisting}
-
 \verb;babette; also uses the same default prior distributions as BEAUti 
@@
 \end{lstlisting}
-
 Within this same example, one may specify
@@
 value with \verb;BEAUti;. Within \verb;babette;, to set the 
-initial mean value of the exponential distribution, do:
+mean value of the exponential distribution to a 
+fixed (non-estimated) value, do:
 
@@
     birth_rate_distr = create_exp_distr(
-      mean = create_mean_param(value = 1.0)
+      mean = create_mean_param(value = 1.0, estimate = FALSE)
     )    
@@
 \end{lstlisting}
-
 Our initial motivation to create \verb;babette; 
@@
 the crown age. Without \verb;babette;, one needs to manually edit the BEAST2 
-configuration file, which is tedious and prone to errors. 
+configuration file \cite{fix_starting_tree}, which is tedious and prone to errors. 
 Fixing the crown ages is especially useful for theoretical experiments,
@@
 \end{lstlisting}
-
 \verb;babette; allows for the same functionality as Tracer.
@@
 the parameter estimates. 
-To remove the burn-in from all parameter estimates in \verb;babette;,
-the following code can be used:
+To remove a 20\% burn-in from all parameter estimates 
+in \verb;babette;, the following code can be used:
 
 \begin{lstlisting}[language=R, floatplacement=H]
-traces <- remove_burn_ins(out$estimates)
+traces <- remove_burn_ins(out$estimates, burn_in_fraction = 0.2)
 \end{lstlisting}
-
 Tracer shows the ESSes of each posterior's variables.
@@
 \end{lstlisting}
-
 Tracer displays multiple summary statistics for each
@@
 \end{lstlisting}
-
 \verb;babette; allows for the same functionality as DensiTree.
@@
 and is licensed under the GNU General Public License v3.0.
-
 \verb;babette; uses the Travis CI \cite{travis}
@@
 \verb;babette; dependends on multiple packages, which are 
-\verb;APE; \cite{APE}, 
+\verb;ape; \cite{APE}, 
 \verb;beautier; \cite{beautier},
@@
 Thanks to Yacine Ben Chehida and Paul van Els for supplying their 
-BEAST2 use cases. Thanks to Leonel Herrera-Alsina, Raphael Scherrer 
-and Giovanni Laudanno for their contributions to this package and article.
+BEAST2 use cases. Thanks again to Paul van Els for the sharing his FASTA files 
+for use by this package. Thanks to Leonel Herrera-Alsina, Raphael Scherrer 
+and Giovanni Laudanno for their comments on this package and article.
 

### 2018-02-27 article.tex
EOD

@@
     birth_rate_distr = create_exp_distr(
-      mean = create_mean_param(value = 1.0, estimate = FALSE)
+      mean = create_mean_param(
+        value = 1.0, 
+        estimate = FALSE
+      )
     )    
@@
 and Giovanni Laudanno for their comments on this package and article.
+We would like to thank the Center for Information Technology of the University 
+of Groningen for their support and for providing access to the Peregrine 
+high performance computing cluster.
 
@@
 \grid
+\grid

### 2018-02-28 article.tex
Use MEE bibliography style
Proper bibliography
Correct citestyle
Correct citation style

@@
 \documentclass{article}
+
+% Bibliography
+\usepackage{natbib}
+\bibpunct{(}{)}{;}{a}{}{;}
+
+% Use 'Name 1234' style
+\setcitestyle{authoryear,open={},close={}}
 
@@
 of the phylogenetic tree of a given set of species. 
-BEAST2 \cite{bouckaert2014beast} is one of the most widely used ones. 
+BEAST2 (\cite{bouckaert2014beast}) is one of the most widely used ones. 
 It creates a posterior of jointly-estimated phylogenies and model parameters, 
@@
 alignments and model parameters.
-BEAST2 is bundled with BEAUti 2 \cite{drummond2012bayesian} ('BEAUti' from now on), 
+BEAST2 is bundled with BEAUti 2 (\cite{drummond2012bayesian}) ('BEAUti' from now on), 
 a desktop application to create a BEAST2 configuration file.
@@
 clock models and tree priors. 
-One such tool to replace BEAUti is \verb;BEASTmasteR; \cite{beastmaster},
+One such tool to replace BEAUti is \verb;BEASTmasteR; (\cite{beastmaster}),
 which focuses on morphological traits and tip-dating, but also 
@@
 
-BEAST2 is also associated with Tracer \cite{tracer} and 
-DensiTree \cite{DensiTree}. Both are desktop applications 
+BEAST2 is also associated with Tracer (\cite{tracer}) and 
+DensiTree (\cite{DensiTree}). Both are desktop applications 
 to analyze the output of BEAST2, each with a user-friendly graphical user interface. 
@@
 are \verb;BEASTmasteR;, \verb;rBEAST; 
-\cite{rBEAST_ratmann} and 
-\verb;RBeast; \cite{RBeast_faria}. 
+(\cite{rBEAST_ratmann}) and 
+\verb;RBeast; (\cite{RBeast_faria}). 
 \verb;BEASTmasteR; and \verb;RBeast; are incomplete
@@
 
-\verb;babette; is written in the R programming language \cite{R}
+\verb;babette; is written in the R programming language (\cite{R})
 and enables the full BEAST2 workflow from an R function call,
@@
 as such, that it can easily be visualized using \verb;ggplot2; (for a trace,
-similar to Tracer) or \verb;phangorn; \cite{phangorn} (for 
+similar to Tracer) or \verb;phangorn; (\cite{phangorn}) (for 
 the phylogenies in a posterior, similar to DensiTree).
@@
 from the FASTA file with name \verb;anthus_aco.fas; (which
-is supplied with the package, from \cite{VanEls2018}), 
+is supplied with the package, from (\cite{VanEls2018})), 
 using the same default settings as BEAUti, which are, 
@@
 the crown age. Without \verb;babette;, one needs to manually edit the BEAST2 
-configuration file \cite{fix_starting_tree}, which is tedious and prone to errors. 
+configuration file (\cite{fix_starting_tree}), which is tedious and prone to errors. 
 Fixing the crown ages is especially useful for theoretical experiments,
@@
 and is licensed under the GNU General Public License v3.0.
-\verb;babette; uses the Travis CI \cite{travis}
+\verb;babette; uses the Travis CI (\cite{travis})
 continuous integration service, which is known to significantly 
-increase the number of bugs exposed \cite{vasilescu2015} and increases
-the speed at which new features are added \cite{vasilescu2015}.
-\verb;babette; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
-\verb;babette; follows Hadley Wickham's style guide \cite{style_guide}, 
-which improves software quality \cite{fang2001}.
+increase the number of bugs exposed (\cite{vasilescu2015}) and increases
+the speed at which new features are added (\cite{vasilescu2015}).
+\verb;babette; has a 100\% code coverage, which correlates with 
+code quality (\cite{horgan1994,del1995correlation}). 
+\verb;babette; follows Hadley Wickham's style guide (\cite{style_guide}), 
+which improves software quality (\cite{fang2001}).
 \verb;babette; dependends on multiple packages, which are 
-\verb;ape; \cite{APE}, 
-\verb;beautier; \cite{beautier},
-\verb;beastier; \cite{beastier},
-\verb;devtools; \cite{devtools},
-\verb;geiger; \cite{GEIGER},
-\verb;ggplot2; \cite{ggplot2},
-\verb;knitr; \cite{knitr},
-\verb;phangorn; \cite{phangorn},
-\verb;rmarkdown; \cite{rmarkdown},
-\verb;seqinr; \cite{seqinr},
-\verb;stringr; \cite{stringr},
-\verb;testit; \cite{testit} and 
-\verb;tracerer; \cite{tracerer}.
+\verb;ape; (\cite{APE}), 
+\verb;beautier; (\cite{beautier}),
+\verb;beastier; (\cite{beastier}),
+\verb;devtools; (\cite{devtools}),
+\verb;geiger; (\cite{GEIGER}),
+\verb;ggplot2; (\cite{ggplot2}),
+\verb;knitr; (\cite{knitr}),
+\verb;phangorn; (\cite{phangorn}),
+\verb;rmarkdown; (\cite{rmarkdown}),
+\verb;seqinr; (\cite{seqinr}),
+\verb;stringr; (\cite{stringr}),
+\verb;testit; (\cite{testit}) and 
+\verb;tracerer; (\cite{tracerer}).
 
-\verb;babette;'s development takes place on GitHub \cite{github},
+\verb;babette;'s development takes place on GitHub (\cite{github}),
 \url{https://github.com/richelbilderbeek/babette}, 
-which accommodates collaboration \cite{perez2016ten} 
-and improves transparency \cite{gorgolewski2016practical}.
+which accommodates collaboration (\cite{perez2016ten}) 
+and improves transparency (\cite{gorgolewski2016practical}).
 \verb;babette;'s GitHub facilitates feature requests and has guidelines how to do so.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\bibliographystyle{plain}
+% MEE styles
+%\input{mee.bst}
+%\input{mee.dbj}
+\bibliographystyle{mee}
+% \bibliographystyle{plain}
+
 \bibliography{article}

### 2018-03-02 article.tex
Citations correct, fix #2

@@
 and is licensed under the GNU General Public License v3.0.
-\verb;babette; uses the Travis CI (\cite{travis})
+\verb;babette; uses the Travis CI (\url{https://travis-ci.org})
 continuous integration service, which is known to significantly 
@@
 
-\verb;babette;'s development takes place on GitHub (\cite{github}),
+\verb;babette;'s development takes place on GitHub,
 \url{https://github.com/richelbilderbeek/babette}, 

### 2018-03-02 article.tex
Figure and table at end
Use double space
Fixed #3
Layout
Use 'BEAST2', instead of 'BEAST 2', fixed #6

@@
 
-% Use 'Name 1234' style
+% Use 'It was found that A is B (Name 1234)' style
 \setcitestyle{authoryear,open={},close={}}
@@
 \usepackage{authblk}
-
 \title{babette: BEAUti 2, BEAST2 and Tracer for R}
@@
 \affil[1]{Groningen Institute for Evolutionary Life Sciences, University of Groningen, Groningen, The Netherlands}
+
+% Use double spacing
+\usepackage{setspace}
+\doublespacing
 
@@
 
-% Keywords
-% \usepackage{spconf}
-
 \usetikzlibrary{calc}
@@
 
-% Ideal
-%\begin{keywords}
-%  computational biology, evolution, phylogenetics, BEAST2, R
-%\end{keywords}
-
-% Dirty hack
 {\bf Keywords:} computational biology, evolution, phylogenetics, BEAST2, R
@@
 Tracer's purpose is to analyze the parameter estimates generated
-from a BEAST 2 run. It shows, among
+from a BEAST2 run. It shows, among
 others, the effective sample size (ESS) and time series ('the trace', 
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-traces <- remove_burn_ins(out$estimates, burn_in_fraction = 0.2)
+traces <- remove_burn_ins(
+  out$estimates, 
+  burn_in_fraction = 0.2
+)
 \end{lstlisting}
@@
 \end{lstlisting}
-
-\begin{table}[]
-\centering
-\begin{tabular}{ | l | l | }
-\hline
-\textbf{Name} & \textbf{Description} \\
-\hline
-\verb;run_beast2; & Run BEAST2 \\
-\hline
-\verb;create_gtr_site_model; & Create a GTR site model \\
-\verb;create_hky_site_model; & Create an HKY site model \\
-\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
-\verb;create_tn93_site_model; & Create a TN93 site model \\
-\hline
-\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
-\verb;create_strict_clock_model; & Create a strict clock model \\
-\hline
-\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
-\verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
-\verb;create_ccp_tree_prior; & Create a coalescent constant-population tree prior \\
-\verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
-\verb;create_yule_tree_prior; & Create a Yule tree prior \\
-\hline
-\verb;create_beta_distr; & Create a beta distribution \\
-\verb;create_exp_distr; & Create an exponential distribution \\
-\verb;create_gamma_distr; & Create a gamma distribution \\
-\verb;create_inv_gamma_distr; & Create an inverse gamma distribution \\
-\verb;create_laplace_distr; & Create a Laplace distribution \\
-\verb;create_log_normal_distr; & Create a log-normal distribution \\
-\verb;create_normal_distr; & Create a normal distribution \\
-\verb;create_one_div_x_distr; & Create a 1/X distribution \\
-\verb;create_poisson_distr; & Create a Poisson distribution \\
-\verb;create_uniform_distr; & Create a uniform distribution \\
-\hline
-\end{tabular}
-\caption{babette's main functions}
-\label{tab:functions}
-\end{table}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Bibliography
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% MEE style
+\bibliographystyle{mee}
+\bibliography{article}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Figures at the end
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% MEE styles
-%\input{mee.bst}
-%\input{mee.dbj}
-\bibliographystyle{mee}
-% \bibliographystyle{plain}
-
-\bibliography{article}
+\begin{table}[h]
+\centering
+\begin{tabular}{ | l | l | }
+\hline
+\textbf{Name} & \textbf{Description} \\
+\hline
+\verb;run_beast2; & Run BEAST2 \\
+\hline
+\verb;create_gtr_site_model; & Create a GTR site model \\
+\verb;create_hky_site_model; & Create an HKY site model \\
+\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
+\verb;create_tn93_site_model; & Create a TN93 site model \\
+\hline
+\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
+\verb;create_strict_clock_model; & Create a strict clock model \\
+\hline
+\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
+\verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
+\verb;create_ccp_tree_prior; & Create a coalescent constant-population tree prior \\
+\verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
+\verb;create_yule_tree_prior; & Create a Yule tree prior \\
+\hline
+\verb;create_beta_distr; & Create a beta distribution \\
+\verb;create_exp_distr; & Create an exponential distribution \\
+\verb;create_gamma_distr; & Create a gamma distribution \\
+\verb;create_inv_gamma_distr; & Create an inverse gamma distribution \\
+\verb;create_laplace_distr; & Create a Laplace distribution \\
+\verb;create_log_normal_distr; & Create a log-normal distribution \\
+\verb;create_normal_distr; & Create a normal distribution \\
+\verb;create_one_div_x_distr; & Create a 1/X distribution \\
+\verb;create_poisson_distr; & Create a Poisson distribution \\
+\verb;create_uniform_distr; & Create a uniform distribution \\
+\hline
+\end{tabular}
+\caption{babette's main functions}
+\label{tab:functions}
+\end{table}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \grid
+\grid
+\grid

### 2018-03-02 article.tex
Added version, fixed #5

@@
 ’BEAUti 2, BEAST2 and Tracer for R’, 
-which creates BEAST2 configuration files,
+which creates BEAST2 (v.2.4.7) configuration files,
 runs BEAST2, and analyzes its results,

### 2018-03-05 article.tex
Implemented feedback, thanks @rsetienne

@@
 Not only can phylogenies show us how species (or other
-evolutionary units) relate to each other, 
+evolutionary units) are related to each other, 
 but we also estimate relevant parameters such as extinction and 
@@
 BEAST2 (\cite{bouckaert2014beast}) is one of the most widely used ones. 
-It creates a posterior of jointly-estimated phylogenies and model parameters, 
+It creates a posterior of jointly estimated phylogenies and model parameters, 
 from one or more DNA, RNA or amino acid alignments (see figure \ref{fig:workflow} 
@@
 wants to explore the consequences of various settings, this must be done manually.
-This is the common workflow when using a few alignments and doing a superficial 
+This is the managable workflow when using a few alignments and doing a superficial 
 analysis of sensitivity of the reconstructed tree to model settings. 
@@
 which focuses on morphological traits and tip-dating, but also 
-supports DNA data. \verb;BEASTmasteR;, however, takes hundreds of
+supports DNA data. \verb;BEASTmasteR;, however, requires hundreds of
 lines of R code to setup the BEAST2 model configuration 
@@
 DensiTree visualizes the phylogenies of a BEAST2 posterior, with
-many options to improve the display of many phylogenies.
+many options to improve the simultaneous display of many phylogenies.
 
@@
 \verb;RBeast; (\cite{RBeast_faria}). 
-\verb;BEASTmasteR; and \verb;RBeast; are incomplete
-packages, where \verb;rBEAST; does not aim to be a 
-package to be used by most BEAST2 users.
+\verb;BEASTmasteR; is a partial BEAUti alternative,
+does not offer a way to call BEAST2, 
+nor allows for the same data analysis as done by Tracer. 
+\verb;RBeast; provides some plotting options and parsing
+of BEAST2 output files. \verb;rBEAST; is a package developed
+around testing a biological hypothesis, 
+that does not aim to be a generally used package.
 
@@
 a BEAST2 configuration file. 
-\verb;babette; is an alternative for a majority of BEAUti use cases.
+\verb;babette; can currently handle a majority of BEAUti use cases.
 Because of BEAUti's high number of plugins, 
 \verb;babette; uses a software architecture that is designed to be extended.
-Furthermore, \verb;babette; has 7 exported function to run and help run BEAST2.
+Furthermore, \verb;babette; has 7 exported functions to run and help run BEAST2.
 One function is used to run BEAST2, others
@@
 same ESSes and summary statistics as Tracer. The data is formatted
-as such, that it can easily be visualized using \verb;ggplot2; (for a trace,
+such that it can easily be visualized using \verb;ggplot2; (for a trace,
 similar to Tracer) or \verb;phangorn; (\cite{phangorn}) (for 
@@
 \end{lstlisting}
-Within this same example, one may specify
+In this same example, one may specify
 the initial shape parameters of the exponential distribution.
@@
 was that we wanted to fix the crown age of a phylogeny.
-BEAUti assumes that a phylogeny has a crown age that needs to be jointly-estimated
-with the phylogeny and other parameters. It does not allow for fixing
+BEAUti assumes that a phylogeny has a crown age that needs to be 
+jointly estimated with the phylogeny and other parameters. 
+It does not allow for fixing
 the crown age. Without \verb;babette;, one needs to manually edit the BEAST2 
@@
 its equilibrium. The start of the trace, called the "burn-in", 
-will be removed, as its parameter estimates are not 
+will be removed, because its parameter estimates are not 
 representative. By default, Tracer discards the first 10\% of all 
@@
 \verb;tracerer; (\cite{tracerer}).
+\verb;babette; is tested to give a clean 
+error message for incorrect input, by
+calling \verb;babette; one million times
+with random or random sensible inputs, 
+using the Peregrine high performance computer cluster. 
+The scripts to do so, are supplied with \verb;babette;.
 
@@
 and improves transparency (\cite{gorgolewski2016practical}).
-\verb;babette;'s GitHub facilitates feature requests and has guidelines how to do so.
+\verb;babette;'s GitHub facilitates feature requests and 
+has guidelines how to do so.
 
@@
 Additionally, \verb;babette; has a vignette that demonstrates extensively how
-to use it. The GitHub documentation helps to get started, with a dozen examples 
-of BEAUti screenshots with equivalent \verb;babette; code.
+to use it. There is documentation on the GitHub to get started, 
+with a dozen examples of BEAUti screenshots with equivalent \verb;babette; code.
+Finally, \verb;babette; has some tutorial video's that can 
+be downloaded or viewed on YouTube, \url{https://goo.gl/weKaaU}.
 

### 2018-03-05 article.tex
Count number of functions

@@
 
-\verb;babette; currently has 61 exported functions to set up  
+\verb;babette; currently has 100 exported functions to set up  
 a BEAST2 configuration file. 
@@
 \verb;babette; uses a software architecture that is designed to be extended.
-Furthermore, \verb;babette; has 7 exported functions to run and help run BEAST2.
+Furthermore, \verb;babette; has 12 exported functions to run and help run BEAST2.
 One function is used to run BEAST2, others
 allow the user to check if a BEAST2 configuration file is indeed valid.
-Finally, \verb;babette; has 20 exported function to parse the BEAST2 output
+Finally, \verb;babette; has 21 exported function to parse the BEAST2 output
 files and analyze the created posterior. \verb;babette; gives the

### 2018-03-06 article.tex
Spellcheck
Feedback, thanks @rsetienne

@@
 
-However, for exploring the output of many BEAST2 runs, 
-one would like a script to collect all parameters' ESSes,
-parameter traces and posterior phylogenies.
-There is no single package that offers a complete solution,
-but examples of R packages that offer a partial solution
-are \verb;BEASTmasteR;, \verb;rBEAST; 
-(\cite{rBEAST_ratmann}) and 
-\verb;RBeast; (\cite{RBeast_faria}). 
-\verb;BEASTmasteR; is a partial BEAUti alternative,
-does not offer a way to call BEAST2, 
-nor allows for the same data analysis as done by Tracer. 
-\verb;RBeast; provides some plotting options and parsing
-of BEAST2 output files. \verb;rBEAST; is a package developed
-around testing a biological hypothesis, 
-that does not aim to be a generally used package.
+However, for exploring the output of many BEAST2 runs, one would like a
+script to collect all parameters' ESSes, parameter traces and posterior
+phylogenies. There is no single package that offers a complete solution,
+but examples of R packages that offer a partial solution are rBEAST
+(\cite{rBEAST_ratmann}) and RBeast (\cite{RBeast_faria}). RBeast provides some
+plotting options and parsing of BEAST2 output files, but the plotting
+functions are too specific for general use, where the functions for parsing
+call those of \verb;babette;. rBEAST was developed to test a 
+particular biological hypothesis (\cite{ratmann2016}), 
+and hence was not designed for general use.
 
@@
 which improves software quality (\cite{fang2001}).
-\verb;babette; dependends on multiple packages, which are 
+\verb;babette; depends on multiple packages, which are 
 \verb;ape; (\cite{APE}), 

### 2018-03-06 article.tex
Add explicit function argument name, thanks @rsetienne

@@
 plotting options and parsing of BEAST2 output files, but the plotting
-functions are too specific for general use, where the functions for parsing
+functions are too specific for general use, whilst the functions for parsing
 call those of \verb;babette;. rBEAST was developed to test a 
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2("anthus_aco.fas")
+out <- run_beast2(fasta_filenames = "anthus_aco.fas")
 \end{lstlisting}
@@
 out <- run_beast2(
-  "anthus_aco.fas",
+  fasta_filenames = "anthus_aco.fas",
   site_models = create_hky_site_model(),
@@
 out <- run_beast2(
-  c("anthus_aco.fas", "anthus_nd2.fas"),
+  fasta_filenames = c(
+    "anthus_aco.fas", 
+    "anthus_nd2.fas"
+  ),
   site_models = list(
@@
 out <- run_beast2(
-  "anthus_aco.fas",
+  fasta_filenames = "anthus_aco.fas",
   tree_priors = create_yule_tree_prior(
@@
 out <- run_beast2(
-  "anthus_aco.fas",
+  fasta_filenames = "anthus_aco.fas",
   posterior_crown_age = 15
@@
 traces <- remove_burn_ins(
-  out$estimates, 
+  traces = out$estimates, 
   burn_in_fraction = 0.2
@@
 esses <- calc_esses(
-  traces, 
+  traces = traces, 
   sample_interval = 1000
@@
 sum_stats <- calc_summary_stats(
-  traces, 
+  traces = traces, 
   sample_interval = 1000
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-plot_densitree(out$anthus_aco_trees)
+plot_densitree(phylos = out$anthus_aco_trees)
 \end{lstlisting}

### 2018-03-06 article.tex
Added feedback @rsetienne

@@
 \verb;tracerer; (\cite{tracerer}).
-\verb;babette; is tested to give a clean 
+We tested \verb;babette; to give a clean 
 error message for incorrect input, by
@@
 using the Peregrine high performance computer cluster. 
-The scripts to do so, are supplied with \verb;babette;.
+The scripts to do so are supplied with \verb;babette;.
 
@@
 with a dozen examples of BEAUti screenshots with equivalent \verb;babette; code.
-Finally, \verb;babette; has some tutorial video's that can 
+Finally, \verb;babette; has tutorial videos that can 
 be downloaded or viewed on YouTube, \url{https://goo.gl/weKaaU}.

### 2018-03-16 article.tex
Add 'Authors’ contributions'

@@
 in a similar way to what BEAUti, DensiTree and Tracer do.
-\verb;babette;'s main function is \verb;run_beast2;, which
+\verb;babette;'s main function is \verb;run;, which
 configures BEAST2, runs it and parses its output. 
-\verb;run_beast2; needs at least the name of a 
+\verb;run; needs at least the name of a 
 FASTA file containing a DNA alignment. 
-The default settings for the other arguments of \verb;run_beast2; 
+The default settings for the other arguments of \verb;run; 
 are identical to BEAUti's and BEAST2's default settings.
@@
 
-\verb;babette; currently has 100 exported functions to set up  
+\verb;babette; currently has 108 exported functions to set up  
 a BEAST2 configuration file. 
@@
 \verb;babette; uses a software architecture that is designed to be extended.
-Furthermore, \verb;babette; has 12 exported functions to run and help run BEAST2.
+Furthermore, \verb;babette; has 13 exported functions to run and help run BEAST2.
 One function is used to run BEAST2, others
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(fasta_filenames = "anthus_aco.fas")
+out <- run(fasta_filenames = "anthus_aco.fas")
 \end{lstlisting}
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(
+out <- run(
   fasta_filenames = "anthus_aco.fas",
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(
+out <- run(
   fasta_filenames = c(
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Authors' contributions}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+RJCB created the package. 
+RJCB wrote the first manuscript draft. 
+All authors critically revised the text and gave approval for publication.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Bibliography
@@
 \hline
-\verb;run_beast2; & Run BEAST2 \\
+\verb;run; & Run BEAST2 \\
 \hline

### 2018-04-23 article.tex
Split article, according to Methods in Ecology and Evolution guidelines
Mention package reviewers

@@
 \usepackage{verbatim}
-\usepackage{tikz}
-\usepackage{tkz-graph}
 \usepackage{pgf}
 \usepackage{bm}
-
-\usetikzlibrary{arrows,automata}
 
@@
 \addto{\captionsenglish}{\renewcommand{\abstractname}{Summary}}
-
-\usetikzlibrary{calc}
-\usetikzlibrary{arrows.meta}
 
@@
 and Giovanni Laudanno for their comments on this package and article.
+Thanks to rOpenSci, and especially Noam Ross, Guangchuang Yu and 
+David Winter for reviewing the package's source code.
 We would like to thank the Center for Information Technology of the University 
@@
 
-RJCB created the package. 
-RJCB wrote the first manuscript draft. 
-All authors critically revised the text and gave approval for publication.
+RJCB and RSE conceived the idea for the package. RJCB created and tested the package, and wrote the first draft of the manuscript. RSE contributed substantially to revisions.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Figures at the end
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-  \centering
-  \resizebox {0.8\columnwidth} {!} {
-    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=6cm, semithick]   
-    \tikzstyle{every state}=[]
-    \node[state] (A) [rectangle] {
-      \includegraphics[width=0.2\textwidth]{alignment.png}
-    };   
-    \node[state] (AL) [above left=-0.25cm and -0.25cm of A, fill=white] {
-      1
-    };   
-    \node[state] (B) [right of = A, rectangle] {
-      \includegraphics[height=0.15\textheight]{BeautiSiteModel.png}
-    };   
-    \node[state] (BL) [above left=-0.25cm and -0.25cm of B, fill=white] {
-      2
-    };   
-    \node[state] (E) [below of=A, rectangle] {
-      \includegraphics[height=0.1\textheight]{file2.png}
-    };   
-    \node[state] (EL) [above left=-0.25cm and -0.25cm of E, fill=white] {
-      3
-    };   
-    \node[state] (C) [right of = E, rectangle] {
-      \includegraphics[width=0.3\textwidth]{beast_logo.png}
-    };   
-    \node[state] (CL) [above left=-0.25cm and -0.25cm of C, fill=white] {
-      4
-    };   
-    \node[state] (F) [rectangle, below of=E] {
-      \includegraphics[height=0.1\textheight]{file.png}
-    };
-    \node[state] (FL) [above left=-0.25cm and -0.25cm of F, fill=white] {
-      5
-    };   
-    \node[state] (H) [rectangle, below of=F] {
-      \includegraphics[width=0.3\textwidth]{DensiTreeExample2.jpg}
-    };
-    \node[state] (HL) [above left=-0.25cm and -0.25cm of H, fill=white] {
-      6
-    };   
-    \node[state] (I) [rectangle, right of=H] {
-      \includegraphics[width=0.6\textwidth]{tracer_example_output.png}
-    };
-    \node[state] (IL) [above left=-0.25cm and -0.25cm of I, fill=white] {
-      7
-    };   
-    \path 
-      (A) edge [anchor = west] node {} (E)
-      (E) edge [anchor = west] node {} (F)
-      (F) edge [anchor = west] node {} (H)
-      (F) edge [anchor = west] node {} (I)
-    ; 
-    \path [-o,draw] (B) -- ($ (A) !.5! (E) $);
-    \path [-o,draw] (C) -- ($ (E) !.5! (F) $);
-    \end{tikzpicture}
-  }
-  \caption{
-    Workflow using GUI tools. From an alignment (1) and BEAUti (2), 
-    a BEAST2 configuration file (3) is created. BEAST2 (4) uses that file
-    to infer a posterior, storing it in multiple files (5). These results
-    are visualized using DensiTree (6) and Tracer (7). babette allows
-    for the same workflow, all from an R function call.
-  }
-  \label{fig:workflow}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2018-05-02 article.tex
Fix typo
Thanks Huw Ogilvie and anonymous reviewer
Implement feedback reviewers

@@
 \end{lstlisting}
+
 Our initial motivation to create \verb;babette; 
@@
 \end{lstlisting}
-\verb;babette; allows for the same functionality as Tracer.
-Tracer works on the values of the parameter estimates sampled
+
+\verb;babette; also supports node dating. Like BEAUti, one
+can specify Most Recent Common Ancestor ('MRCA') priors.
+An MRCA prior allows to specify taxa having a common ancestor,
+including a distribution for the date of that ancestor.
+An application of such a prior is to specify a (close to) fixed
+crown age, by including all taxa and assuming a tight 
+normal distribution around the desired crown age. 
+Within \verb;babette;, this is achieved as such:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+posterior <- run(
+  fasta_filenames = "anthus_aco.fas",
+  mrca_priors = create_mrca_prior(
+    taxa_names = get_taxa_names("anthus_aco.fas"),
+    alignment_id = get_alignment_id("anthus_aco.fas"),
+    mrca_distr = create_normal_distr(
+      mean = create_mean_param(value = 15.0, estimate = FALSE),
+      sigma = create_sigma_param(value = 0.01, estimate = FALSE)
+    )
+  )
+)
+\end{lstlisting}
+
+\verb;babette; allows for the same core functionality as Tracer,
+in which it works on the values of the parameter estimates sampled
 in the BEAST2 run. This is called the "trace" (hence the name).
@@
 Thanks to Yacine Ben Chehida and Paul van Els for supplying their 
-BEAST2 use cases. Thanks again to Paul van Els for the sharing his FASTA files 
+BEAST2 use cases. Thanks again to Paul van Els for sharing his FASTA files 
 for use by this package. Thanks to Leonel Herrera-Alsina, Raphael Scherrer 
 and Giovanni Laudanno for their comments on this package and article.
+Thanks to Huw Ogilvie and one anonymous reviewer for reviewing this article.
 Thanks to rOpenSci, and especially Noam Ross, Guangchuang Yu and 

### 2018-05-02 article.tex
No glib description

@@
 BEAST2 (\cite{bouckaert2014beast}) is one of the most widely used ones.
-It creates a posterior of jointly estimated phylogenies and model parameters, 
-from one or more DNA, RNA or amino acid alignments (see figure \ref{fig:workflow} 
+It uses a Bayesian statistical framework to estimate 
+the joint posterior distribution of estimated phylogenies and model parameters, 
+from one or more DNA, RNA or amino acid alignments (see figure 1 
 for an overview of the workflow).
+
 It has a graphical and a command-line interface, 

### 2018-05-02 article.tex
Do not undersell

@@
 
-Currently, \verb;babette; does not replace all functionality in BEAUti,
-as it does not provide 3 out of 7 tree priors, nor does it support RNA
-alignments or use of morphological data. The many plug-ins of BEAUti
-are not yet supported by \verb;babette;. \verb;babette; does not support
-all command-line arguments of BEAST2, does not provide
-the more specialized Tracer analysis options, nor is it as feature-rich
-in plotting options as DensiTree. Up until now, the \verb;babette; features 
+Currently, \verb;babette; does not replace all functionality 
+in BEAUti, BEAST2 and their many plug-ins.
+This is reasonable, as these themselves also change in time.
+\verb;babette; provides the majority of default tree priors and works only on DNA data. 
+\verb;babette; supports the most important command-line arguments of BEAST2, provides
+the core Tracer analysis options, and has the most basic subset of 
+plotting options of DensiTree. Up until now, the \verb;babette; features 
 implemented are those requested by users. Further extension of \verb;babette; 

### 2018-05-02 article.tex
No empty line after listings
Describe installation and only exporting the BEAST2 config file

@@
 
-In R, the functions of a package need to be loaded in the global namespace first:
+\verb;babette; can be installed easily with the \verb;devtools; package (\cite{devtools}):
+
+\begin{lstlisting}[language=R, floatplacement=H]
+library(devtools)
+install_github("richelbilderbeek/babette")
+\end{lstlisting}
+To start using \verb;babette;, load its functions in the global namespace first:
 
@@
 \end{lstlisting}
-
 \verb;babette; also supports node dating. Like BEAUti, one
@@
 \end{lstlisting}
-
 \verb;babette; allows for the same core functionality as Tracer,
@@
 plot_densitree(phylos = out$anthus_aco_trees)
+\end{lstlisting}
+Instead of running the full pipeline, 
+\verb;babette; also allows to only create a BEAST2 configuration file.
+This file can be loaded and edited by BEAUti. To create a BEAST2 configuration
+file, with all settings to default, use:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+create_beast2_input_file(
+  input_filenames = "anthus_aco.fas",
+  output_filename = "my_beast2_input.xml"
+)
 \end{lstlisting}

### 2018-05-02 article.tex
Describe specifying BEAST2 output files location

@@
 \verb;babette; also allows to only create a BEAST2 configuration file.
-This file can be loaded and edited by BEAUti. To create a BEAST2 configuration
-file, with all settings to default, use:
+To create a BEAST2 configuration file, with all settings to default, use:
 
@@
 create_beast2_input_file(
-  input_filenames = "anthus_aco.fas",
-  output_filename = "my_beast2_input.xml"
+  input_filenames = babette::get_babette_path("anthus_aco.fas"),
+  output_filename = "beast2.xml"
 )
 \end{lstlisting}
+This file can then be loaded and edited by BEAUti, or run by BEAST2.
+\verb;babette; also allows to only run BEAST2 from a BEAST2 configuration
+file:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+run_beast2(
+  input_filename = "beast2.xml",
+  output_log_filename = "run.log",
+  output_trees_filenames = "posterior.trees",
+  output_state_filename = "final.xml.state"
+)
+\end{lstlisting}
+In this example, we specify the names of the desired BEAST2 output files.
+These output files can then be inspected with other tools, or to be used
+to continue a BEAST2 run. Also \verb;run; supports to specify these filenames,
+and these files are put in a temporary folder by default.
 

### 2018-05-02 response_letter/response_letter.md
Implemented feedback reviewers

Dear Editor,

...

Kind regards,

Richèl J.C. Bilderbeek and Rampal S. Etienne

### 2018-05-02 article.tex
EOD
Implemented feedback reviewers

@@
 There are many phylogenetics tools available to obtain an estimate 
-of the phylogenetic tree of a given set of species. 
+of the phylogeny of a given set of species. 
 BEAST2 (\cite{bouckaert2014beast}) is one of the most widely used ones.
@@
 Furthermore, \verb;babette; has 13 exported functions to run and help run BEAST2.
-One function is used to run BEAST2, others
-allow the user to check if a BEAST2 configuration file is indeed valid.
+One function is used to run BEAST2, another
+one installs BEAST2 to a default location.
 Finally, \verb;babette; has 21 exported function to parse the BEAST2 output
@@
 \end{lstlisting}
+For most convenience, let \verb;babette; install BEAST2 to a default location:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+install_beast2()
+\end{lstlisting}
 BEAUti, and likewise \verb;babette;, needs at least a FASTA filename
@@
 storing the posterior. These output
-files must be parsed by either Tracer of DensiTree.
+files must be parsed by either Tracer or DensiTree.
 In \verb;babette;, all this is achieved by:
@@
 from minus infinity to plus infinity. 
-This assumption implies that negative and positive birth rates are just as likely, 
-where a negative birth rate is biologically impossible (note that 
-in practice, this usually works out just fine).
-One may prefer an exponential distribution instead, 
-as this would assume only positive birth rates, 
-and makes high birth rates unlikely.
-To do this in \verb;babette;:
+One may prefer a different ddistribution instead. 
+Here is an example how to specify an exponential distribution for
+the birth rate in a Yule tree prior in \verb;babette;:
 
@@
 \end{lstlisting}
+\textbf{NOTE: suggest to remove this paragraph until node dating}
 Our initial motivation to create \verb;babette; 
-was that we wanted to fix the crown age of a phylogeny.
+was that we wanted to fix the crown age (the time of first divergence) of a phylogeny.
 BEAUti assumes that a phylogeny has a crown age that needs to be 
 jointly estimated with the phylogeny and other parameters. 
-It does not allow for fixing
-the crown age. Without \verb;babette;, one needs to manually edit the BEAST2 
-configuration file (\cite{fix_starting_tree}), which is tedious and prone to errors. 
-Fixing the crown ages is especially useful for theoretical experiments,
-as this allows for one less source of variation.
+It does not allow for fixing the crown age. 
+Without \verb;babette;, one needs to manually edit the BEAST2 
+configuration file, to remove all tree operators that change the height of the root node,
+which is tedious and prone to errors.
+Fixing the crown ages is useful when it is unnecessary 
+to accurately model the uncertainty of absolute divergence times.
 This is how to specify a fixed crown age with \verb;babette;:
@@
 
-\verb;babette; is free, libre and open source software available 
-from the official R package archive at 
-\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#babette}
+\verb;babette; is free, libre and open source software available at 
+\url{http://github.com/richelbilderbeek/babette}
 and is licensed under the GNU General Public License v3.0.
@@
 \end{document}
-\grid
-\grid
-\grid
-\grid
-\grid
-\grid

### 2018-05-04 response_letter/response_letter.md
Example response letter

@@
-Dear Editor,
+# Associate Editor
+# Comments to the Author:
 
-...
+I am now in receipt from of two referee reports for "Etienne et al.
+How reliably can we infer diversity-dependent diversification from phylogenies?".
+Both referees were extremely positive about the ms and only have minor issues to be addressed.
+I think this is a valuable contribution to MEE and encourage the authors to consider the referees’ comments carefully in a revised version.
 
-Kind regards,
+Thank you for these nice words.
+We have revised the ms in the light of these minor comments.
+In addition, we have rerun our analyses to check for a potential numerical inaccuracy.
+This changed our results quantitatively in some cases, but our qualitative conclusions remain practically unaltered.
 
-Richèl J.C. Bilderbeek and Rampal S. Etienne
+# Reviewer(s)' Comments to Author:
+# Reviewer: 1
+
+This is a nice technical paper on a topic of considerable interest in macroevolutionary modeling.
+I am unsurprised by the general findings that Type I error rates can be high -- we tried to address this via simulation in our 2008 Proc B paper -- but the general approach here is obviously a substantial improvement.
+I have one major comment that I'd lead to see the authors address.
+Given that all of these models are approximations of an underlying reality, and that we really have no clue how diversity-dependence might act, what is the benefit of using a formal diversity-dependent model?
+Would there be analytical advantages to going with an exponential decay process for speciation rate as function of time, which can at least do an acceptable job (in some areas of parameter space) at estimating rates under diversity-dependent processes?
+In BAMM, for example, I use an exponential approximation but it can still estimate mean rates of the process and branch-specific rates with some accuracy, even if it's the "wrong" model.
+I expect that there are some areas where the BAMM approximation would perform poorly -- especially for clades that have been at equilibrium for a long tim -- but perhaps not.
+
+We appreciate this comment.
+In fact, last year we already started a separate project studying whether a time-dependent model can be used as a proxy for the computationally more demanding diversity-dependent model.
+This turns out to be a very tricky issue that goes far beyond the focus of this ms which deals primarily with the question whether the presence or absence of diversity-dependence can be reliably detected.
+However, we certainly take the reviewer’s point that this merits some discussion.
+We have therefore added a paragraph in the Discussion section.
+
+The flip side of this issue is that true secular changes in diversification, for reasons that have nothing to do with diversity-dependence, will presumably lead to high Type I error rates using the procedure here.
+The DD model is going to soak up variation in rates through time, so rates through time -- for any reason -- can lead to spurious conclusions about diversity-dependence if assessed in a CR vs DD framework.
+
+We agree that spurious conclusions could be drawn about diversity-dependence in a CR vs DD framework.
+But this is a general philosophical issue: if one model is preferred over others, it only means that this model performs best in explaining the data, but it does not imply that the mechanism underlying the model is necessarily active.
+There are infinitely many other models that could explain the data.
+The appropriate test of time-dependence vs diversity-dependence is of course a TD vs DD framework, which is a study in its own right as we explained above.
+
+I do wonder whether the processes that lead to declining apparent speciation in phylogenies are separable and think it's still an open question.
+And even if you found support for (say), a linear time-dependent decline in speciation over the DD model, could we really reject diversity-dependence, given that the true process of diversity-dependence might not be well-approximated by the functional relationship in the logistic formulation?
+
+This is exactly the issue that we have already started to explore in the separate project explained above.
+In this project we aim to find a time-dependent function that matches the diversity-dependent relationship as much as possible, so that any difference found between their performances on data can really be attributed to time vs diversity-dependence.
+This is a very interesting point, but beyond the focus of this ms.
+
+Some expanded discussion of these important conceptual issues could help frame some key questions for future work in this area and for limits to our interpretation of whatever it is that is coming out of formal DD models.
+
+We have added a discussion of these important points.
+
+L177 - 184: Does this approach for conditioning -- integrating backwards to -Inf before the crown age -- yield appreciable differences when compared to simply conditioning on the crown age itself (if not, the latter could be preferable in the interest of computational tractability).
+
+Yes, it certainly does, as our results in Figure 1 show.
+
+L202 - 204: I don't follow why you can't do the forward simulations to fixed tree size. Does the Hartmann et al (Syst Biol, doi: 10.1093/sysbio/syq026) algorithm get around these issues?
+
+This method works IF one can easily simulate until extinction or a point where the process is not likely to get back to the predefined tree size.
+For diversity-dependent diversification extinction is the only possibility because the system is drawn towards the equilibrium when far away from equilibrium.
+And for the same reason, simulation until extinction may take a very long time.
+Of course, it may also be short when starting with 2 lineages, but then extinction happens early on and the predefined tree size has not been reached.
+We have added some sentences to this extent in the ms.
+
+L220 - 227: This is an interesting tradeoff in conditioning and I expect is not widely appreciated.
+
+Indeed, we agree that this underappreciated.
+
+L95: I have found that there are some communication issues when discussing these models, because people get hung up on the concept of "carrying capacity", even though it's being used phenomenologically here.
+I expect someone will read this and ask "what can we learn from this model if it's making this unrealistic assumption about the existence of a "carrying capacity" "?
+It might be useful to head off this possible misunderstanding by also noting that you can also view this model as a simple linear effect of species richness on speciation rate, basically the simplest model you can use to study how richness might affect diversification.
+Jim Mallet has an interesting paper addressing some of the ways that the K formulation of this model has led to misinterpretation in population ecology as well (Mallet, Evolutionary Ecology Research, 14:627, 2012).
+
+OK, point taken. We have noted this in the ms.
+
+# Reviewer: 2
+
+I very much liked this manuscript for two reasons: In the first place because it provides a much needed cautionary note concerning macroevolutionary inferences from phylogenies.
+Second, because many years ago I submitted a technical comment checking how useful likelihood ratio tests were in selecting models of diversification, and the reviewers thought it was a waste of time to check the performance of the well-established likelihood ratio test.
+So, it gave me some satisfaction to read the current manuscript!
+
+We believe that this reviewer was ahead of his time.
+
+A critical issue in studies like the present is whether simulation and estimation algorithms are correct.
+(One may get biased estimates and error rates because of incorrect simulation and/or estimation algorithms/equations).
+It is almost impossible for reviewers to check this.
+Because estimates are approximately unbiased under dual conditioning, I suppose the algorithms, and hence the results and conclusions presented, are correct.
+
+This ms was already an enormous computational effort for us, so one can hardly expect reviewers or readers to check this thoroughly.
+Nevertheless, we have made the code available in the R package DDD.
+We have also added the simulated trees for readers who would like to check our results or would like to additional analyses on them.
+
+Therefore, (for once) I do not have any major comments: the paper is well written (apart from a few minor issues listed below) and of suitable lengths. The figures are very informative.
+
+We thank the reviewer for his kind words.
+
+While I have no major comments, I do have a suggestion the authors might find useful to think about: what about confidence intervals?
+The likelihood ratio comparing a CR model to a density-dependent model evidently doesn't follow a Chi-square distribution, but what about the ratio of likelihoods of the same model given different parameter values?
+In other words, could it be that confidence intervals around parameters are reliable even if point estimates are biased?
+For me, this leads to the question whether Bayesian estimation would perform any better here.
+For the nested models here you could perhaps calculate Bayes' factor as the Savage-Dickey ratio (assuming any K>>N equals infinity), and hence compare models without relying on Wilk's theorem.
+
+The reviewer raises two points.
+First, a point about confidence intervals.
+We have addressed this issue already in the manuscript by suggesting parametric bootstrapping to obtain confidence intervals (and assessing bias).
+These are by construction reliable, because they tell us the spread in estimations from simulations with the maximum likelihood parameters.
+Second, the reviewer suggests that model selection using Bayes factor may perform better than a likelihood ratio test.
+Because the Bayes factor is simply the ratio of marginal likelihoods we do not expect that these perform better, and introduce another complication: one must specify priors.
+Using appropriate priors could result in better type I and II errors, but the appropriate priors may change from data set to data set.
+We have therefore chosen not to discuss this in the ms.
+
+Line 38: You haven't written what K is, not even what model of density-dependence you use, so the symbol K comes out of the blue sky here.
+
+Thank you for noting this. We have corrected this.
+
+Line 65 This is incorrect: the branches /branching time intervals are typically longer towards the root. Consider inserting “than expected under a constant-rates speciation-extinction model”
+
+We have rephrased this.
+
+Line 84. Is”1)” and “2)” really necessary here?
+
+We have removed these.
+
+Line 99 remove “deep”
+
+We have removed this.
+
+Line 101 you haven't defined K' yet, or explained why it measures the number of available niches. You also don't explain that further down, so this needs fixing.
+
+We have more clearly defined K and K’.
+
+Line 132 bootstrapping
+
+Done.
+
+210-211 It isn't obvious what “this” model is. Perhaps “the density-dependent model” would be clearer.
+
+We have rephrased this.
+
+210-227: I think you mean Fig1 when you wrote Fig2, and vice versa, in this section.
+
+Thank you. We have changed this.
+
+250 You cite Tekle, but it might be appropriate to cite also Wilk's original paper.
+The reason why the chi-square approximation isn't appropriate could be non-independence inherent in time series, in addition to the points you raise.
+
+We have inserted a citation to Wilk’s paper.
+
+227 What you say is that improper conditioning improves precision at the expense of accuracy. (Not unusual.) It might be helpful to summarize it that way.
+
+We have incorporated this suggestion.
+
+248 -272.
+I find the phrasing, especially the word “bootstrap” a bit too difficult here.
+The reason why the likelihood ratio test doesn't perform well is that the sampling distribution of the likelihood ratio is not the usual chi-square distribution.
+You don't need to mention regularity conditions here.
+What about the following: “The mismatch between our Type I error rate and the intended significance level occurs because the distribution of the likelihood ratio is not the expected Chi-square (for reasons we will discuss furher down).
+Therefore, we suggest to estimate the actual distribution of the likelihood ratio using simulations (Tekle et al.
+2015).” Steps 1-4 describe this procedure.
+One could use kernel density estimation instead of using the fraction LR>LR0 to reduce the number of simulations, but if you use the fraction, then use it properly (doi: 10.1086/341527 or some equivalent paper).
+(I'm not asking to fix the values in the ms, with 500 simulations it wouldn't make a real difference.
+However, I do think you should replace that sentence about the fraction (262) with the proper method from the doi above.)
+
+We have inserted this suggestion.
+
+338 You cite Lambert and Stadler 2013, but I believe this was already demonstrated clearly by Maddison et al 2007: Maddison, W.
+P., Midford, P.
+E., & Otto, S.
+P.
+(2007).
+Estimating a binary character’s effect on speciation and extinction.
+Systematic Biology, 56(5), 701–710.
+
+We have inserted this reference.
+
+343 “The failure of the chi 2 -likelihood ratio test is due to...” I wonder how you can be so sure what this is due to.
+Probably the K=infinity issue plays a role, but Wilk's theorem also assumes that data are idd, which seems violated here.
+
+We have rephrased this.
+
+355 differs
+
+Done.
+
+I liked the information-dense figures, and have only a few comments on the legends:
+
+Thank you for these kinds words.
+
+501-502 Perhaps a more effective phrasing would be “Note the discrepancy between Type I error rates and significance levels.”
+
+We have rephrased this.
+
+508 and further: you have logarithms of the likelihood ratio, not loglikelihood ratios.
+
+The reviewer is right (of course). We have rephrased this.

### 2018-05-04 response_letter/response_letter.md
First version response letter

--- 2018-05-02 response_letter/response_letter.md
@@
-Dear Editor,
+# Associate Editor Comments to Author:
+# Associate Editor
+# Comments to the Author:
 
-...
+> we have now received two very qualified reviews for your manuscript on babette. 
+> Overall, both reviews are very positive and consider your software and article worthy of publication in Methods in Ecology and Evolution.
+I agree with the reviewers' assessment.
+Nevertheless, before your manuscript can be accepted for publication, I ask you to follow the advice of the two reviewers carefully to address the minor issues raised by them.
 
-Kind regards,
+Thank you for these nice words. We are happy to inform you we took care of all these issues.
 
-Richèl J.C. Bilderbeek and Rampal S. Etienne
+> I agree with reviewer 2 that 
+> more flexible node dating would be an worthwhile feature 
+> to add to babette but that this addition could be left for future development. 
+> Nevertheless I would find it helpful if implemented options for node dating could be described 
+> in slightly more detail in the manuscript; 
+> e.g. is an age constraint on the root the only option for node dating, 
+> and can it be constrained by prior distributions, or only with a fixed age?
+
+We are happy to announce, that while this manuscript was under review, node dating has been
+added the package. Additionally, an example how to use this is added to the manuscript,
+where we constrain the crown age by a tight normal distribution. The way to do so, using what is called
+an MRCA prior, does have the option to specify monophyly, but we did not an example to demonstrate
+this feature.
+
+> In addition I suggest to rephrase line 190 as babette does not allow all the functionality of Tracer (as stated on line 101), 
+> and to fix a small error in the Acknowledgements, "for the sharing his FASTA files".
+
+Fully agree, we did as suggested.
+
+# Reviewer(s)' Comments to Author:
+# Reviewer: 1
+#
+# Comments to the Corresponding Author
+
+> Bilderbeek and Etienne have created a useful tool in babette, and have written a concise and informative paper describing what they have done and how it works.
+For this reason I am recommending acceptance with minor revisions, and would like to thank the authors for their contribution to phylogenetic software and the BEAST universe.
+
+We are happy to hear our work is appreciated, as great care was taken to make the
+article as short as possible, and the tool `babette` as useful as possible
+
+> Continuing the grand tradition of picking alliterative puns for BEAST program names, 
+> the authors have gone with "babette". 
+> I guess that this is in reference to one of the maids that cleans up after The Beast in the famous fairy tale. 
+> I think the name is logical and clever. 
+> However in the older Disney animated versions of the fairy tale the maid is a "sexy maid" stereotype, 
+> and the authors seem to have directly copied the babette logo from the animation. 
+> The authors should reconsider this, not only because of the notorious litigousness of Disney lawyers, 
+> but also because the optics of using a "sexy maid" logo for scientific software is bad, 
+> especially in 2018, especially from two male authors. 
+> Sorry if this point gets interpreted as not having a sense of humor, but I think it should be addressed.
+
+Thanks for mentioning this issue in such careful words. We thought it would be indeed a good idea
+to follow this advice. All logo's (`babette` and the packages it relies on) have been redesigned (by
+a girl actually) to be more neutral.
+
+> Page 3, line 29: "creates a posterior" is a bit of a glib description, 
+> and could be reworded as "it uses a Bayesian statistical framework to estimate 
+> the joint posterior distribution of estimated phylogenies and..."
+
+Agreed. We use your words to improve the accuracy of the original wording.
+
+> Page 4, lines 97-104: I think the authors are under-selling their own product here. 
+> Of course babette does not support everything BEAUTi does at the moment, 
+> but instead of highlighting all the things it cannot do, maybe focus more on what it can do. 
+> For example, elucidate the 3 prior priors that are supported, 
+> instead of saying that only 3 of 7 tree priors are not supported. 
+> BEAST2 is very dynamic, and new tree priors are added all the time, 
+> so it's likely that 7 will not be the correct number in the future. 
+> Likewise I imagine babette will be improved upon and that when someone reads the paper in the future, 
+> it may support more than 3 tree priors.
+
+Thanks for pointing this out! Upon a re-read, the original wording did sound rather pessimistic.
+The new wording specifies what has been done in a way that would still be correct for future readers.
+
+> Section 3, Usage: there should be some indiciation of how to install babette, 
+> or where to go to find out how to install it. 
+> There seems to be a minor bug in the installation script: 
+> when I installed babette using devtools as recommended, a bunch of dependencies were installed, 
+> but when I ran "run" it required an R package "testthat" which was not one of those dependencies. 
+> Also, is it possible to export the XML without running babette, 
+> or to export the trees after babette has finished running? 
+> Those would be two useful examples to include in this section.
+
+How to install `babette` and BEAST2 (to a default location to be found by `babette`) are
+added. The lack of `testthat` was embarassing, which proves that even a rigid testing
+scheme cannot catch all mistakes. An early adopter of `babette` already pointed out
+this error and it has been fixed. As, indeed, it is possible to only export the XML
+normally created by BEAUti, this has been added, as we expect more people to desire this.
+
+> Page 5, line 114: "run" is an extremely generic name for a function 
+> and is likely to result in namespace conflicts with other packages. 
+> Maybe there is a good reason to use this name that I am not aware of, 
+> but if not, consider a more informative name.
+
+We completely agree. The function has been renamed to `bbt_run`, following the tradition of `tidyverse` packages
+like `stringr`.
+
+> Also the "beast2_jar_path" default is hardcoded to "~/Programs/beast2/lib/beast.jar", 
+> which will be wrong for everyone except the authors of the program, 
+> so I suggest that this argument should be required rather than optional. 
+> At least here in "Usage" a value for this argument should be included.
+
+This point has been mentioned by the rOpenSci code reviewers and has already been
+addressed. Using the `rappdirs` package, folder names can be made paltform independent.
+Since then, `babette` is tested to build and pass all test under both Windows and Linux.
+
+> Page 6, lines 151-155: For parameters which are changed only using a scale operator, 
+> and not a random walk or uniform operator, values less than 0 are never proposed. 
+> So effectively the prior probability density for something like birth rate 
+> with an unbounded uniform prior is 0 to infinity, 
+> and having a non-zero probability on negative values is not a valid reason to use an exponential prior.
+
+We agree and wrote down that indeed this is an invalid 
+reason ('In practice, this [reasoning] does not matter'). As apparently we did not do a good enough job,
+we decided to remove the incorrect reasoning altogether and only demonstrate how to use a different
+prior distribution.
+
+> Page 7, line 182: Reference to the Bouckaert & Vaughan blog post 
+> doesn't seem relevant to this feature of babette. 
+> How does babette fix the crown age? 
+> Is it by scaling the root node of the tree to that age, 
+> and removing all operators that can change the height of the root node? 
+> However it is done, adding a brief explanation in the main text would be good.
+
+The reference to the blog post has been removed. As per this comment, we describe how `babette`
+fixes a phylogeny crown age, by -indeed- removing all operators that can change the height of the root node.
+
+> Page 7, lines 178-184: Fixing the crown age 
+> and estimating the clock is an alternative to fixing the clock 
+> and estimating the crown age. 
+> I would guess that for some studies this is a useful feature. 
+> But in either case the same number of parameters are estimated, 
+> so I don't think the overall variation across parameters will be reduced. 
+> Also "theoretical" experiments is too vague. 
+> Instead you could describe these experiments as 
+> "where it is unnecessary to accurately model the uncertainty of absolute divergence times".
+
+Agree. We added this superior wording to the manuscipt.
+
+> Again, I would like to thank Bilderbeek and Etienne for their software and paper. 
+> I am sure babette will be used by others researchers in the future, 
+> and they will find it a valuable program.
+> 
+> Sincerely,
+> 
+> Huw Ogilvie
+
+We would like to thank Ogilvie for his constructive feedback, that improved the
+manuscript in ways that will make it more useful for more readers.
+
+# Reviewer: 2
+# Comments to the Corresponding Author
+
+> As a user of both BEAST2 and R, 
+> I agree here is a need for an implementation of BEAST2 in R. 
+> My review is based solely on the documentation given by the authors, 
+> including the youtube videos, as neither link nor package is available 
+> and could therefore not be tested by me. 
+> The proposed package babette package combines the base features of BEAST2,
+> including standard models and priors, and the associates BEAUti and Tracer. 
+> My judgement is that babette appears to be a useful tool, 
+> especially when numerous replicates with slighly different settings are to be run.
+
+We are happy to hear the reviewer sees the utility to the package. The reason
+the link to CRAN did not work, is as it has not yet been accepted by CRAN. `babette` intends
+to be submitted to CRAN, but only after an rOpenSci code review. Such a code review will
+help the -overly busy- CRAN maintainers judge `babette` for its high-quality code.
+
+> Personally I would like to see 
+> node dating, 
+> the multispecies coalescent,
+> and ancestral state reconstruction implemented in babette,
+> but I suppose this is for future versions of the package.
+
+We are happy to announce, that while this manuscript was under review, node dating has been
+added the package. Additionally, an example how to use this is added to the manuscript,
+where we constrain the crown age by a tight normal distribution. The way to do so, using what is called
+an MRCA prior, does have the option to specify monophyly, but we did not an example to demonstrate
+this feature.
+
+The other features have been added as feature requests on the `babette` GitHub. Which features
+will first be added to `babette` is unsure, and will depend -as mentioned in the manuscript-
+on user requests. We expect to receive a peak in user requests after the publication of this
+manuscript, which will be the moment when a choice will be made what to implement next.
+
+> I did not understand the "fix crown age option". 
+> How exactly is the crown defined? 
+> From the output it seems that it is the root age that is fixed, which is confusing.
+
+We were unaware of the possibility of this confusion. 
+We improved the wording by defining the crown age as the first divergence time, we
+hope that resolves this matter. By our vocabulary, 
+the root age would be the time a first species is observed, which we would call the stem age.
+
+> Minor comments to the text:
+> 
+> L28. Tools exist for species phylogenies that are not trees as well, 
+> so substitute "phylogenetic tree" with "phylogeny".
+
+Agree. Fixed.
+
+> [x] L31. "Figure ??" ?
+
+Completely agree. Fixed.
+
+> [x] L91. Is this the equivalent of running BEAST2 with an empty alignment?
+
+No, that option mentioned was to validate a file to be valid (i.e. not corrupted or
+have an incorrect XML structure). We decided to remove mentioning file validation,
+as it would be only of minor interest to most. Instead, we mention the option
+of installing BEAST2 from R.
+
+> [x] L112. "or"
+
+Well spotted! Fixed.
+
+> [x] L227. Link to babette is not working.
+
+Correct. Updated to point to the GitHub of `babette`.

### 2018-05-04 article.tex
Feedback reviewers
Correct spelling
Do not mention future contributors here
Use 'bbt_run' instead of 'run'

@@
 \begin{lstlisting}[language=R, floatplacement=H]
-out <- run(fasta_filenames = "anthus_aco.fas")
+out <- bbt_run(fasta_filenames = "anthus_aco.fas")
 \end{lstlisting}
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-out <- run(
+out <- bbt_run(
   fasta_filenames = "anthus_aco.fas",
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-out <- run(
+out <- bbt_run(
   fasta_filenames = c(
@@
 \begin{lstlisting}[language=R, floatplacement=H]
-posterior <- run(
+out <- bbt_run(
   fasta_filenames = "anthus_aco.fas",
@@
 These output files can then be inspected with other tools, or to be used
-to continue a BEAST2 run. Also \verb;run; supports to specify these filenames,
+to continue a BEAST2 run. Also \verb;bbt_run; supports to specify these filenames,
 and these files are put in a temporary folder by default.
@@
 Thanks to Huw Ogilvie and one anonymous reviewer for reviewing this article.
-Thanks to rOpenSci, and especially Noam Ross, Guangchuang Yu and 
-David Winter for reviewing the package's source code.
+Thanks to rOpenSci, and especially Noam Ross and Guangchuang Yu for reviewing the package's source code.
 We would like to thank the Center for Information Technology of the University 
@@
 \hline
-\verb;run; & Run BEAST2 \\
+\verb;bbt_run; & Run BEAST2 \\
 \hline

### 2018-05-06 article.tex
Implemented feedback, thanks @rsetienne

@@
 plotting options and parsing of BEAST2 output files, but the plotting
-functions are too specific for general use, whilst the functions for parsing
-call those of \verb;babette;. rBEAST was developed to test a 
+functions are too specific for general use. rBEAST was developed to test a 
 particular biological hypothesis (\cite{ratmann2016}), 
@@
 \verb;babette; is written in the R programming language (\cite{R})
-and enables the full BEAST2 workflow from an R function call,
-in a similar way to what BEAUti, DensiTree and Tracer do.
-\verb;babette;'s main function is \verb;run;, which
+and enables the full BEAST2 workflow from a single R function call,
+in a similar way to what subsequent usage of BEAUti, DensiTree and Tracer would produce.
+\verb;babette;'s main function is \verb;bbt_run;, which
 configures BEAST2, runs it and parses its output. 
-\verb;run; needs at least the name of a 
+\verb;bbt_run; needs at least the name of a 
 FASTA file containing a DNA alignment. 
-The default settings for the other arguments of \verb;run; 
+The default settings for the other arguments of \verb;bbt_run; 
 are identical to BEAUti's and BEAST2's default settings.
@@
 a BEAST2 configuration file. 
-\verb;babette; can currently handle a majority of BEAUti use cases.
+\verb;babette; can currently handle the majority of BEAUti use cases.
 Because of BEAUti's high number of plugins, 
@@
 
-Currently, \verb;babette; does not replace all functionality 
-in BEAUti, BEAST2 and their many plug-ins.
-This is reasonable, as these themselves also change in time.
-\verb;babette; provides the majority of default tree priors and works only on DNA data. 
-\verb;babette; supports the most important command-line arguments of BEAST2, provides
+Currently, \verb;babette; does not contain all functionality 
+in BEAUti, BEAST2 and their many plug-ins, 
+because these tools themselves also change in time.
+\verb;babette; currently works only on DNA data,
+because this is the most common use case. 
+Nevertheless, \verb;babette; provides the majority of default tree priors and supports the most important command-line arguments of BEAST2, provides
 the core Tracer analysis options, and has the most basic subset of 
-plotting options of DensiTree. Up until now, the \verb;babette; features 
+plotting options of DensiTree. Up till now, the \verb;babette; features 
 implemented are those requested by users. Further extension of \verb;babette; 
@@
 
-\verb;babette; can be installed easily with the \verb;devtools; package (\cite{devtools}):
+\verb;babette; can be installed easily from CRAN \textbf{NOTE: This is not true yet: 
+we are still in the process of submitting to CRAN}:
 
 \begin{lstlisting}[language=R, floatplacement=H]
-library(devtools)
-install_github("richelbilderbeek/babette")
+install.packages("babette")
+\end{lstlisting}
+For the most up-to-date version, 
+one can download and install the package from \verb;babette;'s GitHub repository:
+
+\begin{lstlisting}[language=R, floatplacement=H]
+devtools::install_github("richelbilderbeek/babette")
 \end{lstlisting}
@@
 \end{lstlisting}
-For most convenience, let \verb;babette; install BEAST2 to a default location:
+Because babette calls BEAST2, BEAST2 must be installed. This can be done from R, using:
 
@@
 \end{lstlisting}
+This will install BEAST2 to the default user data folder, but a different path can be specified as well.
 BEAUti, and likewise \verb;babette;, needs at least a FASTA filename
@@
 has one shape parameter: its mean, which can be set to any
-value with \verb;BEAUti;. Within \verb;babette;, to set the 
+value with \verb;BEAUti;. To set the 
 mean value of the exponential distribution to a 
@@
 \end{lstlisting}
-\textbf{NOTE: suggest to remove this paragraph until node dating}
-Our initial motivation to create \verb;babette; 
-was that we wanted to fix the crown age (the time of first divergence) of a phylogeny.
-BEAUti assumes that a phylogeny has a crown age that needs to be 
-jointly estimated with the phylogeny and other parameters. 
-It does not allow for fixing the crown age. 
-Without \verb;babette;, one needs to manually edit the BEAST2 
-configuration file, to remove all tree operators that change the height of the root node,
-which is tedious and prone to errors.
-Fixing the crown ages is useful when it is unnecessary 
-to accurately model the uncertainty of absolute divergence times.
-This is how to specify a fixed crown age with \verb;babette;:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- bbt_run(
-  fasta_filenames = "anthus_aco.fas",
-  posterior_crown_age = 15
-)
-\end{lstlisting}
 \verb;babette; also supports node dating. Like BEAUti, one
@@
 normal distribution around the desired crown age. 
-Within \verb;babette;, this is achieved as such:
+With \verb;babette;, this is achieved as follows:
 
@@
 \end{lstlisting}
-\verb;babette; allows for the same core functionality as Tracer,
-in which it works on the values of the parameter estimates sampled
+Instead of using all taxa, any subset of taxa can be selected 
+to have a dated common ancestor.
+\verb;babette; allows for the same core functionality as Tracer to show the values of the parameter estimates sampled
 in the BEAST2 run. This is called the "trace" (hence the name).
-The start of the trace is usually discarded, as an MCMC 
+The start of the trace, called the "burn-in", is usually discarded, as an MCMC 
 algorithm (such as used by BEAST2) first has to converge to
-its equilibrium. The start of the trace, called the "burn-in", 
-will be removed, because its parameter estimates are not 
+its equilibrium and hence the parameter estimates are not 
 representative. By default, Tracer discards the first 10\% of all 
@@
 time scale, drawn one over one another, allowing to see the uncertainty in
-topology and branch lengths. Within the object \verb;out;, 
-the posterior phylogenies are stored as \verb;anthus_aco_trees;,
-and can be plotted as such:
+topology and branch lengths. 
+The posterior phylogenies are stored as \verb;anthus_aco_trees; in the object \verb;out;,
+and can be plotted as follows:
 
@@
 \end{lstlisting}
-This file can then be loaded and edited by BEAUti, or run by BEAST2.
-\verb;babette; also allows to only run BEAST2 from a BEAST2 configuration
-file:
+This file can then be loaded and edited by BEAUti, run by BEAST2, or run by \verb;babette;:
 
@@
 In this example, we specify the names of the desired BEAST2 output files.
-These output files can then be inspected with other tools, or to be used
-to continue a BEAST2 run. Also \verb;bbt_run; supports to specify these filenames,
-and these files are put in a temporary folder by default.
+These output files can then be inspected with other tools, or used
+to continue a BEAST2 run. \verb;bbt_run; supports specifying the folder and name of these files,
+which defaults to a temporary folder to keep
+the working directory clean of intermediate and
+temporary files.
 
@@
 using the Peregrine high performance computer cluster. 
-The scripts to do so are supplied with \verb;babette;.
+The test scripts are supplied with \verb;babette;.
 

### 2018-05-06 article.tex
Use MRCA prior on three random taxa, instead of on all taxa

@@
 including a distribution for the date of that ancestor.
-An application of such a prior is to specify a (close to) fixed
-crown age, by including all taxa and assuming a tight 
-normal distribution around the desired crown age. 
 With \verb;babette;, this is achieved as follows:
@@
   mrca_priors = create_mrca_prior(
-    taxa_names = get_taxa_names("anthus_aco.fas"),
+    taxa_names = sample(get_taxa_names("anthus_aco.fas"), size = 2),
     alignment_id = get_alignment_id("anthus_aco.fas"),
+    is_monophyletic = TRUE,
     mrca_distr = create_normal_distr(
       mean = create_mean_param(value = 15.0, estimate = FALSE),
-      sigma = create_sigma_param(value = 0.01, estimate = FALSE)
+      sigma = create_sigma_param(value = 0.025, estimate = FALSE)
     )
@@
 \end{lstlisting}
-Instead of using all taxa, any subset of taxa can be selected 
-to have a dated common ancestor.
+Instead of dating the ancestor of two random taxa, any subset of taxa can be selected,
+and multiple sets are allowed.
 \verb;babette; allows for the same core functionality as Tracer to show the values of the parameter estimates sampled

### 2018-05-06 response_letter/response_letter.md
Improved response letter, thanks @rsetienne

@@
 # Associate Editor Comments to Author:
-# Associate Editor
-# Comments to the Author:
 
@@
 
-We are happy to announce, that while this manuscript was under review, node dating has been
-added the package. Additionally, an example how to use this is added to the manuscript,
-where we constrain the crown age by a tight normal distribution. The way to do so, using what is called
-an MRCA prior, does have the option to specify monophyly, but we did not an example to demonstrate
-this feature.
+While this manuscript was under review, we already added node dating to the package. Additionally, an example how to use this is added to the manuscript,
+where we data the ancestor node of three random taxa assuming monophyly.
 
@@
 # Reviewer: 1
-#
-# Comments to the Corresponding Author
 
@@
 
-We are happy to hear our work is appreciated, as great care was taken to make the
-article as short as possible, and the tool `babette` as useful as possible
+We are happy to hear our work is appreciated.
 
@@
 to follow this advice. All logo's (`babette` and the packages it relies on) have been redesigned (by
-a girl actually) to be more neutral.
+a girl actually) to be more gender-neutral.
 
@@
 
-Thanks for pointing this out! Upon a re-read, the original wording did sound rather pessimistic.
+Thanks for pointing this out! Upon a re-read, the original wording did sound rather negative.
 The new wording specifies what has been done in a way that would still be correct for future readers.
@@
 
-How to install `babette` and BEAST2 (to a default location to be found by `babette`) are
-added. The lack of `testthat` was embarassing, which proves that even a rigid testing
-scheme cannot catch all mistakes. An early adopter of `babette` already pointed out
+We added text on how to install `babette` and BEAST2 (to a default location to be found by `babette`) are
+added. The missing `testthat` dependency in the DESCRIPTION file (under `Suggests`) was embarassing, which proves that even a rigid testing
+scheme cannot catch all mistakes. An early `babette` user already pointed out
 this error and it has been fixed. As, indeed, it is possible to only export the XML
-normally created by BEAUti, this has been added, as we expect more people to desire this.
+normally created by BEAUti, this has been added, as we expect more people to want this feature.
 
@@
 
-This point has been mentioned by the rOpenSci code reviewers and has already been
-addressed. Using the `rappdirs` package, folder names can be made paltform independent.
-Since then, `babette` is tested to build and pass all test under both Windows and Linux.
+This point was also mentioned by rOpenSci code reviewers and has been
+addressed. Using the `rappdirs` package, folder names can be made platform independent.
+Since then, `babette` has been tested to build and pass all tests under both Windows and Linux.
 
@@
 
-The reference to the blog post has been removed. As per this comment, we describe how `babette`
+The reference to the blog post has been removed. As per this comment, we described how `babette`
 fixes a phylogeny crown age, by -indeed- removing all operators that can change the height of the root node.
+We use the past tense here, as we decided to remove this paragraph althogether: the posteriors produced by BEAST2 have remarkably different branch length distributions, for unknown reasons.
+Using a dated note on the crown does give the regular branch length distributions.
 
@@
 
-Agree. We added this superior wording to the manuscipt.
+Agreed. We added this superior wording to the manuscipt, before removing the entire paragraph, as clarified above.
 
@@
 # Reviewer: 2
-# Comments to the Corresponding Author
 
@@
 
-We are happy to announce, that while this manuscript was under review, node dating has been
-added the package. Additionally, an example how to use this is added to the manuscript,
-where we constrain the crown age by a tight normal distribution. The way to do so, using what is called
-an MRCA prior, does have the option to specify monophyly, but we did not an example to demonstrate
-this feature.
+While this manuscript was under review, we added node dating and an example how to do so. As the first reviewer also suggested this feature, we refer to the comments there.
 
@@
 
-Agree. Fixed.
+Agreed. Fixed.
 
@@
 
-Completely agree. Fixed.
+We completely agree. Fixed.
 

### 2018-05-07 response_letter/response_letter.md
Implemented feedback response letter, thanks @rsetienne

@@
 
-While this manuscript was under review, we already added node dating to the package. Additionally, an example how to use this is added to the manuscript,
-where we data the ancestor node of three random taxa assuming monophyly.
+While this manuscript was under review, we already added node dating to the package. Additionally, we added an example how to to the manuscript,
+where we date the ancestral node of three random taxa assuming monophyly.
 
@@
 > but when I ran "run" it required an R package "testthat" which was not one of those dependencies.
+
+We added text on how to install `babette` and BEAST2 (to a default location to be found by `babette`) are
+added. The missing `testthat` dependency in the DESCRIPTION file (under `Suggests`) was embarassing, which proves that even a rigid testing
+scheme cannot catch all mistakes. An early `babette` user already pointed out
+this error and it has been fixed.
+
 > Also, is it possible to export the XML without running babette, 
@@
 
-We added text on how to install `babette` and BEAST2 (to a default location to be found by `babette`) are
-added. The missing `testthat` dependency in the DESCRIPTION file (under `Suggests`) was embarassing, which proves that even a rigid testing
-scheme cannot catch all mistakes. An early `babette` user already pointed out
-this error and it has been fixed. As, indeed, it is possible to only export the XML
+As, indeed, it is possible to only export the XML
 normally created by BEAUti, this has been added, as we expect more people to want this feature.
@@
 
-We agree and wrote down that indeed this is an invalid 
-reason ('In practice, this [reasoning] does not matter'). As apparently we did not do a good enough job,
-we decided to remove the incorrect reasoning altogether and only demonstrate how to use a different
+We agree and decided to remove the incorrect reasoning altogether and only demonstrate how to use a different
 prior distribution.
@@
 
-The reference to the blog post has been removed. As per this comment, we described how `babette`
+The reference to the blog post has been removed. Indeed, we described how `babette`
 fixes a phylogeny crown age, by -indeed- removing all operators that can change the height of the root node.
-We use the past tense here, as we decided to remove this paragraph althogether: the posteriors produced by BEAST2 have remarkably different branch length distributions, for unknown reasons.
-Using a dated note on the crown does give the regular branch length distributions.
+But, we decided to remove this paragraph althogether: the posteriors produced by BEAST2 with this setting have remarkably different branch length distributions, for unknown reasons.
+Using a dated node on the crown does give the regular branch length distributions.
 
@@
 
-Agreed. We added this superior wording to the manuscipt, before removing the entire paragraph, as clarified above.
+Agreed. We added this superior wording to the manuscipt, but eventuallt removed the entire paragraph, as clarified above.
 
@@
 
-We would like to thank Ogilvie for his constructive feedback, that improved the
+We would like to thank Huw Ogilvie for his constructive feedback, that improved the
 manuscript in ways that will make it more useful for more readers.
@@
 We are happy to hear the reviewer sees the utility to the package. The reason
-the link to CRAN did not work, is as it has not yet been accepted by CRAN. `babette` intends
-to be submitted to CRAN, but only after an rOpenSci code review. Such a code review will
+the link to CRAN did not work, is that it has not yet been accepted by CRAN.
+We intend to submit `babette` to CRAN, but only after an rOpenSci code review, which ends at May 18th.
+Such a code review will
 help the -overly busy- CRAN maintainers judge `babette` for its high-quality code.

### 2018-05-07 article_complete.tex
EOD
Build article correctly

--- 2018-03-06 article.tex
@@
 
-\begin{abstract}
-
-  \textbf{1. }
-    In the field of phylogenetics, 
-    BEAST2 is one of the most widely used software tools. 
-    It comes with the graphical user interfaces BEAUti 2, DensiTree and Tracer,
-    to create BEAST2 configuration files and to interpret BEAST2's output files. 
-    However, when many different alignments or model 
-    setups are required, a workflow of graphical user interfaces is cumbersome. \\
-  \textbf{2. }
-    Here, we present a free, libre and open-source package, \verb;babette;: 
-    'BEAUti 2, BEAST2 and Tracer for R', for the R programming language. 
-    \verb;babette; creates BEAST2 input files, runs BEAST2 and parses its results, 
-    all from an R function call. \\
-  \textbf{3. }
-    We describe \verb;babette;'s usage and the novel functionality it provides
-    compared to the original tools and we give some examples. \\
-  \textbf{4. }
-    As \verb;babette; is designed to be of high quality and extendable, 
-    we conclude by describing the further development of the package. \\
-\end{abstract}
-
-{\bf Keywords:} computational biology, evolution, phylogenetics, BEAST2, R
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Phylogenies are commonly used to explore evolutionary hypotheses.
-Not only can phylogenies show us how species (or other
-evolutionary units) are related to each other, 
-but we also estimate relevant parameters such as extinction and 
-speciation rates.
-There are many phylogenetics tools available to obtain an estimate 
-of the phylogenetic tree of a given set of species. 
-BEAST2 (\cite{bouckaert2014beast}) is one of the most widely used ones. 
-It creates a posterior of jointly estimated phylogenies and model parameters, 
-from one or more DNA, RNA or amino acid alignments (see figure \ref{fig:workflow} 
-for an overview of the workflow). 
-It has a graphical and a command-line interface, 
-that both need a configuration file containing 
-alignments and model parameters.
-BEAST2 is bundled with BEAUti 2 (\cite{drummond2012bayesian}) ('BEAUti' from now on), 
-a desktop application to create a BEAST2 configuration file.
-BEAUti has a user-friendly graphical user interface, with helpful
-default settings.
-As such, BEAUti is an attractive alternative 
-to manual and error-prone editing of BEAST2 configuration files.
-
-However, BEAUti cannot be called from a command-line script.
-This implies that when the user 
-wants to explore the consequences of various settings, this must be done manually.
-This is the managable workflow when using a few alignments and doing a superficial 
-analysis of sensitivity of the reconstructed tree to model settings. 
-For exploring many trees (for instance from simulations) and for
-more thorough sensitivity analysis, one would like to loop through 
-multiple (simulated) alignments, nucleotide substitution models, 
-clock models and tree priors. 
-One such tool to replace BEAUti is \verb;BEASTmasteR; (\cite{beastmaster}),
-which focuses on morphological traits and tip-dating, but also 
-supports DNA data. \verb;BEASTmasteR;, however, requires hundreds of
-lines of R code to setup the BEAST2 model configuration 
-and a Microsoft Excel file to specify alignment files.
-
-BEAST2 is also associated with Tracer (\cite{tracer}) and 
-DensiTree (\cite{DensiTree}). Both are desktop applications 
-to analyze the output of BEAST2, each with a user-friendly graphical user interface. 
-Tracer's purpose is to analyze the parameter estimates generated
-from a BEAST2 run. It shows, among
-others, the effective sample size (ESS) and time series ('the trace', 
-hence the name) of each variable in the MCMC run. Both ESS and trace
-are needed to assess the strength of the inference. 
-DensiTree visualizes the phylogenies of a BEAST2 posterior, with
-many options to improve the simultaneous display of many phylogenies.
-
-However, for exploring the output of many BEAST2 runs, one would like a
-script to collect all parameters' ESSes, parameter traces and posterior
-phylogenies. There is no single package that offers a complete solution,
-but examples of R packages that offer a partial solution are rBEAST
-(\cite{rBEAST_ratmann}) and RBeast (\cite{RBeast_faria}). RBeast provides some
-plotting options and parsing of BEAST2 output files, but the plotting
-functions are too specific for general use, whilst the functions for parsing
-call those of \verb;babette;. rBEAST was developed to test a 
-particular biological hypothesis (\cite{ratmann2016}), 
-and hence was not designed for general use.
-
-Here, we present \verb;babette;:
-’BEAUti 2, BEAST2 and Tracer for R’, 
-which creates BEAST2 (v.2.4.7) configuration files,
-runs BEAST2, and analyzes its results,
-all from an R function call. This
-will save time, tedious mouse clicking and 
-reduces the chances of errors in such repetitive actions.
-The interface of \verb;babette; mimics the tools it
-is based on. This
-familiarity helps both beginner and experienced BEAST2 users 
-to make the step from those tools to \verb;babette;.
-\verb;babette; enables the creation of a single-script 
-pipeline from sequence alignments to posterior analysis in R.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Description}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\verb;babette; is written in the R programming language (\cite{R})
-and enables the full BEAST2 workflow from an R function call,
-in a similar way to what BEAUti, DensiTree and Tracer do.
-\verb;babette;'s main function is \verb;run_beast2;, which
-configures BEAST2, runs it and parses its output. 
-\verb;run_beast2; needs at least the name of a 
-FASTA file containing a DNA alignment. 
-The default settings for the other arguments of \verb;run_beast2; 
-are identical to BEAUti's and BEAST2's default settings.
-Per alignment, a site model, clock model and tree prior can be chosen.
-Multiple alignments can be used, each with its own (unlinked) site model, 
-clock model and tree prior.
-
-\verb;babette; currently has 100 exported functions to set up  
-a BEAST2 configuration file. 
-\verb;babette; can currently handle a majority of BEAUti use cases.
-Because of BEAUti's high number of plugins, 
-\verb;babette; uses a software architecture that is designed to be extended.
-Furthermore, \verb;babette; has 12 exported functions to run and help run BEAST2.
-One function is used to run BEAST2, others
-allow the user to check if a BEAST2 configuration file is indeed valid.
-Finally, \verb;babette; has 21 exported function to parse the BEAST2 output
-files and analyze the created posterior. \verb;babette; gives the
-same ESSes and summary statistics as Tracer. The data is formatted
-such that it can easily be visualized using \verb;ggplot2; (for a trace,
-similar to Tracer) or \verb;phangorn; (\cite{phangorn}) (for 
-the phylogenies in a posterior, similar to DensiTree).
-
-Currently, \verb;babette; does not replace all functionality in BEAUti,
-as it does not provide 3 out of 7 tree priors, nor does it support RNA
-alignments or use of morphological data. The many plug-ins of BEAUti
-are not yet supported by \verb;babette;. \verb;babette; does not support
-all command-line arguments of BEAST2, does not provide
-the more specialized Tracer analysis options, nor is it as feature-rich
-in plotting options as DensiTree. Up until now, the \verb;babette; features 
-implemented are those requested by users. Further extension of \verb;babette; 
-will be based on future user requests.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Usage}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In R, the functions of a package need to be loaded in the global namespace first:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-library(babette)
-\end{lstlisting}
-BEAUti, and likewise \verb;babette;, needs at least a FASTA filename
-to produce a BEAST2 configuration file. 
-In BEAUti, this is achieved by loading a FASTA file, 
-then saving an output file using a common
-save file dialog. After this, BEAST2 needs to be applied to
-the created configuration file. It creates multiple files
-storing the posterior. These output
-files must be parsed by either Tracer of DensiTree.
-In \verb;babette;, all this is achieved by:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(fasta_filenames = "anthus_aco.fas")
-\end{lstlisting}
-This code will create a (temporary) BEAST2 configuration file,
-from the FASTA file with name \verb;anthus_aco.fas; (which
-is supplied with the package, from (\cite{VanEls2018})), 
-using the same default settings as BEAUti, which are, 
-among others, a Jukes-Cantor site model, a strict clock, and a Yule birth tree prior.
-\verb;babette; will then execute BEAST2 using that file, and
-parses the output. The returned data structure, named \verb;out;, 
-is a list of parameter estimates (called \verb;estimates;), posterior 
-phylogenies (called \verb;anthus_aco_trees;, named after
-the alignment's name) and MCMC operator performance (\verb;operators;).
-An example of using a different site model, clock model 
-and tree prior is:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(
-  fasta_filenames = "anthus_aco.fas",
-  site_models = create_hky_site_model(),
-  clock_models = create_rln_clock_model(),
-  tree_priors = create_bd_tree_prior()
-)
-\end{lstlisting}
-This code uses an HKY site model, a relaxed log-normal clock model and a 
-birth-death tree prior, each with their default settings in BEAUti.
-Table \ref{tab:functions} shows an overview of all functions to 
-create site models, clock models and tree priors.
-Note that the arguments' names \verb;site_models;, \verb;clock_models; 
-and \verb;tree_priors; are plural, as each of these
-can be (a list of) one or more elements. Each of these arguments must 
-have the same number of elements, so that each alignment has its
-own site model, clock model and tree prior. 
-An example of two alignments, each with its own site model, is:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(
-  fasta_filenames = c(
-    "anthus_aco.fas", 
-    "anthus_nd2.fas"
-  ),
-  site_models = list(
-    create_tn93_site_model(), 
-    create_gtr_site_model()
-  )
-)
-\end{lstlisting}
-\verb;babette; also uses the same default prior distributions as BEAUti 
-for each of the site models, clock models and tree priors. 
-For example, by default, a Yule tree prior assumes that the birth rate 
-follows a uniform distribution, 
-from minus infinity to plus infinity. 
-This assumption implies that negative and positive birth rates are just as likely, 
-where a negative birth rate is biologically impossible (note that 
-in practice, this usually works out just fine).
-One may prefer an exponential distribution instead, 
-as this would assume only positive birth rates, 
-and makes high birth rates unlikely.
-To do this in \verb;babette;:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(
-  fasta_filenames = "anthus_aco.fas",
-  tree_priors = create_yule_tree_prior(
-    birth_rate_distr = create_exp_distr()    
-  )
-)
-\end{lstlisting}
-In this same example, one may specify
-the initial shape parameters of the exponential distribution.
-In BEAST2's implementation, an exponential distribution 
-has one shape parameter: its mean, which can be set to any
-value with \verb;BEAUti;. Within \verb;babette;, to set the 
-mean value of the exponential distribution to a 
-fixed (non-estimated) value, do:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(
-  fasta_filenames = "anthus_aco.fas",
-  tree_priors = create_yule_tree_prior(
-    birth_rate_distr = create_exp_distr(
-      mean = create_mean_param(
-        value = 1.0, 
-        estimate = FALSE
-      )
-    )    
-  )
-)
-\end{lstlisting}
-Our initial motivation to create \verb;babette; 
-was that we wanted to fix the crown age of a phylogeny.
-BEAUti assumes that a phylogeny has a crown age that needs to be 
-jointly estimated with the phylogeny and other parameters. 
-It does not allow for fixing
-the crown age. Without \verb;babette;, one needs to manually edit the BEAST2 
-configuration file (\cite{fix_starting_tree}), which is tedious and prone to errors. 
-Fixing the crown ages is especially useful for theoretical experiments,
-as this allows for one less source of variation.
-This is how to specify a fixed crown age with \verb;babette;:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- run_beast2(
-  fasta_filenames = "anthus_aco.fas",
-  posterior_crown_age = 15
-)
-\end{lstlisting}
-\verb;babette; allows for the same functionality as Tracer.
-Tracer works on the values of the parameter estimates sampled
-in the BEAST2 run. This is called the "trace" (hence the name).
-The start of the trace is usually discarded, as an MCMC 
-algorithm (such as used by BEAST2) first has to converge to
-its equilibrium. The start of the trace, called the "burn-in", 
-will be removed, because its parameter estimates are not 
-representative. By default, Tracer discards the first 10\% of all 
-the parameter estimates. 
-To remove a 20\% burn-in from all parameter estimates 
-in \verb;babette;, the following code can be used:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-traces <- remove_burn_ins(
-  traces = out$estimates, 
-  burn_in_fraction = 0.2
-)
-\end{lstlisting}
-Tracer shows the ESSes of each posterior's variables.
-These ESSes are important to determine the strength of the
-inference. As a rule of thumb, an ESS of 200 is acceptable 
-for any parameter estimate.
-To calculate the effective sample sizes (of all estimated variables) in \verb;babette;:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-esses <- calc_esses(
-  traces = traces, 
-  sample_interval = 1000
-)
-\end{lstlisting}
-Tracer displays multiple summary statistics for each
-estimated variable: the mean and its standard error, standard deviation,
-variance, median, mode, geometric mean, 95\% highest posterior density interval, 
-auto-correlation time and effective sample size. It displays these statistics per
-variable. In \verb;babette;, these summary statistics are collected for
-all estimated parameters at once:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-sum_stats <- calc_summary_stats(
-  traces = traces, 
-  sample_interval = 1000
-)
-\end{lstlisting}
-\verb;babette; allows for the same functionality as DensiTree.
-DensiTree displays the phylogenies in a posterior at the same
-time scale, drawn one over one another, allowing to see the uncertainty in
-topology and branch lengths. Within the object \verb;out;, 
-the posterior phylogenies are stored as \verb;anthus_aco_trees;,
-and can be plotted as such:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-plot_densitree(phylos = out$anthus_aco_trees)
-\end{lstlisting}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{babette resources}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\verb;babette; is free, libre and open source software available 
-from the official R package archive at 
-\url{http://cran.r-project.org/src/contrib/PACKAGES.html\#babette}
-and is licensed under the GNU General Public License v3.0.
-\verb;babette; uses the Travis CI (\url{https://travis-ci.org})
-continuous integration service, which is known to significantly 
-increase the number of bugs exposed (\cite{vasilescu2015}) and increases
-the speed at which new features are added (\cite{vasilescu2015}).
-\verb;babette; has a 100\% code coverage, which correlates with 
-code quality (\cite{horgan1994,del1995correlation}). 
-\verb;babette; follows Hadley Wickham's style guide (\cite{style_guide}), 
-which improves software quality (\cite{fang2001}).
-\verb;babette; depends on multiple packages, which are 
-\verb;ape; (\cite{APE}), 
-\verb;beautier; (\cite{beautier}),
-\verb;beastier; (\cite{beastier}),
-\verb;devtools; (\cite{devtools}),
-\verb;geiger; (\cite{GEIGER}),
-\verb;ggplot2; (\cite{ggplot2}),
-\verb;knitr; (\cite{knitr}),
-\verb;phangorn; (\cite{phangorn}),
-\verb;rmarkdown; (\cite{rmarkdown}),
-\verb;seqinr; (\cite{seqinr}),
-\verb;stringr; (\cite{stringr}),
-\verb;testit; (\cite{testit}) and 
-\verb;tracerer; (\cite{tracerer}).
-We tested \verb;babette; to give a clean 
-error message for incorrect input, by
-calling \verb;babette; one million times
-with random or random sensible inputs, 
-using the Peregrine high performance computer cluster. 
-The scripts to do so are supplied with \verb;babette;.
-
-\verb;babette;'s development takes place on GitHub,
-\url{https://github.com/richelbilderbeek/babette}, 
-which accommodates collaboration (\cite{perez2016ten}) 
-and improves transparency (\cite{gorgolewski2016practical}).
-\verb;babette;'s GitHub facilitates feature requests and 
-has guidelines how to do so.
-
-\verb;babette;'s documentation is extensive. All functions are documented
-in the package's internal documentation. For quick use, 
-each exported function shows a minimal example. 
-For easy exploration, each exported function's documentation links to related functions.
-Additionally, \verb;babette; has a vignette that demonstrates extensively how
-to use it. There is documentation on the GitHub to get started, 
-with a dozen examples of BEAUti screenshots with equivalent \verb;babette; code.
-Finally, \verb;babette; has tutorial videos that can 
-be downloaded or viewed on YouTube, \url{https://goo.gl/weKaaU}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Citation of babette}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Scientists using \verb;babette; in a published paper can cite this
-article, and/or cite the \verb;babette; package 
-directly. To obtain this citation from within an R script, use:
-
-\begin{lstlisting}[language=R]
-> citation("babette")
-\end{lstlisting}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowledgements}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Thanks to Yacine Ben Chehida and Paul van Els for supplying their 
-BEAST2 use cases. Thanks again to Paul van Els for the sharing his FASTA files 
-for use by this package. Thanks to Leonel Herrera-Alsina, Raphael Scherrer 
-and Giovanni Laudanno for their comments on this package and article.
-We would like to thank the Center for Information Technology of the University 
-of Groningen for their support and for providing access to the Peregrine 
-high performance computing cluster.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Bibliography
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% MEE style
-\bibliographystyle{mee}
-\bibliography{article}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+\begin{figure}[h]
   \centering
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h]
-\centering
-\begin{tabular}{ | l | l | }
-\hline
-\textbf{Name} & \textbf{Description} \\
-\hline
-\verb;run_beast2; & Run BEAST2 \\
-\hline
-\verb;create_gtr_site_model; & Create a GTR site model \\
-\verb;create_hky_site_model; & Create an HKY site model \\
-\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
-\verb;create_tn93_site_model; & Create a TN93 site model \\
-\hline
-\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
-\verb;create_strict_clock_model; & Create a strict clock model \\
-\hline
-\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
-\verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
-\verb;create_ccp_tree_prior; & Create a coalescent constant-population tree prior \\
-\verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
-\verb;create_yule_tree_prior; & Create a Yule tree prior \\
-\hline
-\verb;create_beta_distr; & Create a beta distribution \\
-\verb;create_exp_distr; & Create an exponential distribution \\
-\verb;create_gamma_distr; & Create a gamma distribution \\
-\verb;create_inv_gamma_distr; & Create an inverse gamma distribution \\
-\verb;create_laplace_distr; & Create a Laplace distribution \\
-\verb;create_log_normal_distr; & Create a log-normal distribution \\
-\verb;create_normal_distr; & Create a normal distribution \\
-\verb;create_one_div_x_distr; & Create a 1/X distribution \\
-\verb;create_poisson_distr; & Create a Poisson distribution \\
-\verb;create_uniform_distr; & Create a uniform distribution \\
-\hline
-\end{tabular}
-\caption{babette's main functions}
-\label{tab:functions}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}
-\grid
-\grid
-\grid
-\grid

### 2018-05-07 response_letter/response_letter.md
Implemented feedback on response letter, thanks @rsetienne

@@
 
-Fully agree, we did as suggested.
+We fully agree, we did as suggested.
 
@@
 
-Agreed. We added this superior wording to the manuscipt, but eventuallt removed the entire paragraph, as clarified above.
+Agreed. We added this superior wording to the manuscipt, but eventually removed the entire paragraph, as clarified above.
 
@@
 have an incorrect XML structure). We decided to remove mentioning file validation,
-as it would be only of minor interest to most. Instead, we mention the option
-of installing BEAST2 from R.
+as it would be only of minor interest to most (it has been moved to a vignette). 
+Instead, we mention the option of installing BEAST2 from R.
 

### 2018-05-07 article.tex
Pretend that babette is already on CRAN, which will be true in the future
Implemented overlooked feedback, thanks @rsetienne

@@
 evolutionary units) are related to each other, 
-but we also estimate relevant parameters such as extinction and 
-speciation rates.
+but we can also estimate relevant parameters such as extinction and 
+speciation rates from them.
 There are many phylogenetics tools available to obtain an estimate 
@@
 It uses a Bayesian statistical framework to estimate 
-the joint posterior distribution of estimated phylogenies and model parameters, 
+the joint posterior distribution of phylogenies and model parameters, 
 from one or more DNA, RNA or amino acid alignments (see figure 1 
@@
 
-It has a graphical and a command-line interface, 
+BEAST2 has a graphical and a command-line interface, 
 that both need a configuration file containing 
@@
 
-\verb;babette; can be installed easily from CRAN \textbf{NOTE: This is not true yet: 
-we are still in the process of submitting to CRAN}:
+\verb;babette; can be installed easily from CRAN:
 
@@
 \end{lstlisting}
-This file can then be loaded and edited by BEAUti, run by BEAST2, or run by \verb;babette;:
+This file can then be loaded and edited by BEAUti, 
+run by BEAST2, or run by \verb;babette;:
 
@@
 \end{lstlisting}
-In this example, we specify the names of the desired BEAST2 output files.
-These output files can then be inspected with other tools, or used
-to continue a BEAST2 run. \verb;bbt_run; supports specifying the folder and name of these files,
-which defaults to a temporary folder to keep
-the working directory clean of intermediate and
-temporary files.
+\verb;run_beast2; is a function that only runs BEAST2, 
+and does not parse the output files (unlike \verb;bbt_run;). 
+In the example above, 
+we specify the names of the desired BEAST2 
+output files explicitly, and these will be created in the
+R working directory, after which thay can be inspected 
+with other tools, or used to continue a BEAST2 run.
+By default, both \verb;bbt_run; and \verb;run_beast2;
+put these files in the default temporary folder (as
+created by \verb;temp.dir();) to keep
+the working directory clean of intermediate files.
 
@@
 with random or random sensible inputs, 
-using the Peregrine high performance computer cluster. 
+using a high performance computer cluster. 
 The test scripts are supplied with \verb;babette;.
@@
 of Groningen for their support and for providing access to the Peregrine 
-high performance computing cluster.
+high performance computing cluster. We thank the Netherlands 
+Organization for Scientific Research (NWO) for financial support 
+through a VICI grant awarded to RSE.
 
@@
 \end{document}
+\grid
+\grid

### 2018-05-07 article.tex
Better wording

@@
 put these files in the default temporary folder (as
-created by \verb;temp.dir();) to keep
+obtained from \verb;temp.dir();) to keep
 the working directory clean of intermediate files.

### 2018-05-07 response_letter/response_letter.md
Implemented feedback, thanks @rsetienne

@@
 
-The reference to the blog post has been removed. Indeed, we described how `babette`
-fixes a phylogeny crown age, by -indeed- removing all operators that can change the height of the root node.
-But, we decided to remove this paragraph althogether: the posteriors produced by BEAST2 with this setting have remarkably different branch length distributions, for unknown reasons.
+The reference to the blog post has been removed. 
+Indeed, we described how `babette`
+fixes a phylogeny crown age, by -indeed- removing 
+all operators that can change the height of the root node. 
+But, we decided to remove this paragraph altogether, 
+because the posteriors produced by BEAST2 with this setting have remarkably different branch length distributions, for unknown reasons.
 Using a dated node on the crown does give the regular branch length distributions.
@@
 No, that option mentioned was to validate a file to be valid (i.e. not corrupted or
-have an incorrect XML structure). We decided to remove mentioning file validation,
+have an incorrect XML structure). We decided to remove 
+mentioning file validation in the manuscript,
 as it would be only of minor interest to most (it has been moved to a vignette). 

### 2018-05-07 article.tex
Implemented feedback, thanks @rsetienne

--- 2018-05-07 article.tex
@@
 output files explicitly, and these will be created in the
-R working directory, after which thay can be inspected 
+R working directory, after which they can be inspected 
 with other tools, or used to continue a BEAST2 run.
-By default, both \verb;bbt_run; and \verb;run_beast2;
+When the names of these files are not specified, 
+both \verb;bbt_run; and \verb;run_beast2;
 put these files in the default temporary folder (as
-created by \verb;temp.dir();) to keep
+obtained from \verb;temp.dir();) to keep
 the working directory clean of intermediate files.

### 2018-05-14 article.tex
Feedback final reviewer

@@
 analysis of sensitivity of the reconstructed tree to model settings. 
-For exploring many trees (for instance from simulations) and for
-more thorough sensitivity analysis, one would like to loop through 
-multiple (simulated) alignments, nucleotide substitution models, 
+For exploring many trees (for instance from simulations), when doing a sliding-window
+analysis, or for a more thorough sensitivity analysis, one would like to loop through 
+multiple (simulated or shortened) alignments, nucleotide substitution models, 
 clock models and tree priors. 
@@
 Tracer's purpose is to analyze the parameter estimates generated
-from a BEAST2 run. It shows, among
+from a (BEAST1 and) BEAST2 run. It shows, among
 others, the effective sample size (ESS) and time series ('the trace', 
@@
 from the FASTA file with name \verb;anthus_aco.fas; (which
-is supplied with the package, from (\cite{VanEls2018})), 
+is supplied with the package, from \cite{VanEls2018}), 
 using the same default settings as BEAUti, which are, 

### 2018-05-14 article.tex
Dutch abstract

@@
 
+\hyphenation{grafi-sche}
+\hyphenation{mo-ge-lijk-he-den}
+
 \begin{document}
@@
     we conclude by describing the further development of the package. \\
+\end{abstract}
+
+\begin{abstract}
+
+  \textbf{1. }
+    In het onderzoeksveld van de fylogenetica is BEAST2 een van de meest gebruikte 
+    hulpprogramma's. Het is gebundeld met de grafische gebruikers interface
+    BEAUti 2, DensiTree en Tracer, om BEAST2 configuratiebestanden te maken
+    en om BEAST2 output bestanden te interpreteren.
+    Echter, als veel verschillende aligneringen of modelopzetten nodig zijn,
+    is een werkvolgorde van meerdere grafische gebruiksinterfaces onhandig. \\
+  \textbf{2. }
+    Hier presenteren wij een gratis, vrij en open-source package, \verb;babette;:
+    'BEAUti 2, BEAST2 en Tracer voor R', voor de programmeertaal R. 
+    \verb;babette; schrijft BEAST2 configuratiebestanden, start BEAST2 and verwerkt de resultaten, 
+    alles met een enkele R functie-aanroep. \\
+  \textbf{3. }
+    Wij beschrijven hoe \verb;babette; te gebruiken is en de nieuwe mogelijkheden die het biedt
+    vergeleken met de originele programma's, begeleidt met enkele voorbeelden. \\
+  \textbf{4. }
+    Omdat \verb;babette; ontworpen is om van hoge kwaliteit en uitbreidbaar te zijn, 
+    sluiten wij af met het beschrijven van de verdere ontwikkeling van dit package. \\
 \end{abstract}

### 2018-05-14 article.tex
Added feedback, thanks @rsetienne

--- 2018-05-14 article.tex
@@
     we conclude by describing the further development of the package. \\
+\end{abstract}
+
+\begin{abstract}
+  \textbf{1. }
+    In de fylogenetica is BEAST2 een van de meest gebruikte hulpprogramma's. 
+    Het is gebundeld met de grafische gebruiksinterface BEAUti 2, DensiTree en Tracer, 
+    om BEAST2-configuratiebestanden te maken en om BEAST2-outputbestanden te interpreteren. 
+    Echter, als veel verschillende aligneringen of modelopzetten nodig zijn, 
+    is een werkvolgorde van meerdere grafische gebruiksinterfaces onhandig. \\
+  \textbf{2. }
+    Hier presenteren we een gratis, vrij en open-source package, \verb;babette;: 
+    'BEAUti 2, BEAST2 en Tracer voor R', voor de programmeertaal R. 
+    \verb;babette; schrijft BEAST2-configuratiebestanden, start BEAST2 and verwerkt de resultaten, 
+    alles met een enkele R functie-aanroep. \\
+  \textbf{3. }
+    We beschrijven hoe \verb;babette; te gebruiken is 
+    en de nieuwe mogelijkheden die het biedt vergeleken met de originele programma's, 
+    aan de hand van enkele voorbeelden. \\
+  \textbf{4. }
+    Omdat \verb;babette; ontworpen is voor uitbreidbaarheid en hoge kwaliteit, 
+    sluiten we af met het beschrijven van de verdere ontwikkeling van dit package. \\
 \end{abstract}
@@
 analysis of sensitivity of the reconstructed tree to model settings. 
-For exploring many trees (for instance from simulations), when doing a sliding-window
-analysis, or for a more thorough sensitivity analysis, one would like to loop through 
+For exploring many trees (for instance from simulations), 
+when doing when doing a sliding-window analysis on a genomic alignment, 
+or for a more thorough sensitivity analysis, one would like to loop through 
 multiple (simulated or shortened) alignments, nucleotide substitution models, 

### 2018-05-17 article/article.tex
Put manuscript in 'article' folder

--- 2018-05-14 article.tex
@@
     we conclude by describing the further development of the package. \\
-\end{abstract}
 
-\begin{abstract}
+  \begin{center}
+  \textbf{Samenvatting}
+  \end{center}
   \textbf{1. }
@@
 For exploring many trees (for instance from simulations), 
-when doing when doing a sliding-window analysis on a genomic alignment, 
+for a sliding-window analysis on a genomic alignment, 
 or for a more thorough sensitivity analysis, one would like to loop through 

### 2018-05-17 figures/figures.tex
No title at figures
Simplified

--- 2018-05-07 article_complete.tex
@@
-\documentclass{article}
+\documentclass[a3paper]{article}
 
-% Bibliography
-\usepackage{natbib}
-\bibpunct{(}{)}{;}{a}{}{;}
-
-% Use 'It was found that A is B (Name 1234)' style
-\setcitestyle{authoryear,open={},close={}}
-
-% Affiliations
-\usepackage{authblk}
-\title{babette: BEAUti 2, BEAST2 and Tracer for R}
-\author[1]{Rich\`el J.C. Bilderbeek}
-\author[1]{Rampal S. Etienne}
-\affil[1]{Groningen Institute for Evolutionary Life Sciences, University of Groningen, Groningen, The Netherlands}
-
-% Use double spacing
-\usepackage{setspace}
-\doublespacing
+% 300 DPI
 
@@
 \usetikzlibrary{arrows,automata}
-
-% Style of listings
-% From http://r.789695.n4.nabble.com/How-to-nicely-display-R-code-with-the-LaTeX-package-listings-tp4648110.html
-\usepackage{fancyvrb} 
-\definecolor{codegreen}{rgb}{0,0.6,0}
-\definecolor{codegray}{rgb}{0.5,0.5,0.5}
-\definecolor{codepurple}{rgb}{0.58,0,0.82}
-\definecolor{backcolor}{rgb}{0.95,0.95,0.92}
-\lstdefinestyle{mystyle}{
-  language=R,% set programming language
-  basicstyle=\ttfamily\small,% basic font style
-  commentstyle=\color{gray},% comment style
-  % numbers=left,% display line numbers on the left side
-  numberstyle=\scriptsize,% use small line numbers
-  numbersep=10pt,% space between line numbers and code
-  tabsize=2,% sizes of tabs
-  showstringspaces=false,% do not replace spaces in strings by a certain character
-  captionpos=b,% positioning of the caption below
-  breaklines=true,% automatic line breaking
-  escapeinside={(*}{*)},% escaping to LaTeX
-  fancyvrb=true,% verbatim code is typset by listings
-  extendedchars=false,% prohibit extended chars (chars of codes 128--255)
-  alsoletter={.<-},% becomes a letter
-  alsoother={$},% becomes other
-  otherkeywords={!=, ~, $, \&, \%/\%, \%*\%, \%\%, <-, <<-, /},% other keywords
-  deletekeywords={c}% remove keywords 
-}
-\lstset{style=mystyle}
-
-% Adds numbered lines
-\usepackage{lineno}
-\linenumbers
-
-% Rename 'Abstract' to 'Summary 
-\usepackage[english]{babel}
-\addto{\captionsenglish}{\renewcommand{\abstractname}{Summary}}
-
 \usetikzlibrary{calc}
@@
 \begin{document}
-
-\maketitle
 
@@
     \node[state] (B) [right of = A, rectangle] {
-      \includegraphics[height=0.15\textheight]{BeautiSiteModel.png}
+      \includegraphics[height=0.15\textheight]{beauti_site_model.png}
     };   

### 2018-05-22 article/article.tex
Thank Michael Matschiner
Added 'Data Accessibility' section
Add DOI for #12

@@
 and Giovanni Laudanno for their comments on this package and article.
-Thanks to Huw Ogilvie and one anonymous reviewer for reviewing this article.
+Thanks to Huw Ogilvie, Michael Matschiner and one anonymous reviewer for reviewing this article.
 Thanks to rOpenSci, and especially Noam Ross and Guangchuang Yu for reviewing the package's source code.
@@
 through a VICI grant awarded to RSE.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Data Accessibility}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+All code is archived at \url{http://github.com/richelbilderbeek/babette_article},
+with DOI \url{https://doi.org/10.5281/zenodo.1251203}.
 

### 2019-05-02 figures/figure_1.tex
Figures are in 'figures.tex' (standalone) and 'figure_1.tex' (only the figure)

--- 2018-05-07 article_complete.tex
@@
-\documentclass{article}
-
-% Bibliography
-\usepackage{natbib}
-\bibpunct{(}{)}{;}{a}{}{;}
-
-% Use 'It was found that A is B (Name 1234)' style
-\setcitestyle{authoryear,open={},close={}}
-
-% Affiliations
-\usepackage{authblk}
-\title{babette: BEAUti 2, BEAST2 and Tracer for R}
-\author[1]{Rich\`el J.C. Bilderbeek}
-\author[1]{Rampal S. Etienne}
-\affil[1]{Groningen Institute for Evolutionary Life Sciences, University of Groningen, Groningen, The Netherlands}
-
-% Use double spacing
-\usepackage{setspace}
-\doublespacing
-
-\usepackage{listings}
-\usepackage{hyperref}
-\usepackage{todonotes}
-\usepackage{verbatim}
-\usepackage{tikz}
-\usepackage{tkz-graph}
-\usepackage{pgf}
-\usepackage{bm}
-
-\usetikzlibrary{arrows,automata}
-
-% Style of listings
-% From http://r.789695.n4.nabble.com/How-to-nicely-display-R-code-with-the-LaTeX-package-listings-tp4648110.html
-\usepackage{fancyvrb} 
-\definecolor{codegreen}{rgb}{0,0.6,0}
-\definecolor{codegray}{rgb}{0.5,0.5,0.5}
-\definecolor{codepurple}{rgb}{0.58,0,0.82}
-\definecolor{backcolor}{rgb}{0.95,0.95,0.92}
-\lstdefinestyle{mystyle}{
-  language=R,% set programming language
-  basicstyle=\ttfamily\small,% basic font style
-  commentstyle=\color{gray},% comment style
-  % numbers=left,% display line numbers on the left side
-  numberstyle=\scriptsize,% use small line numbers
-  numbersep=10pt,% space between line numbers and code
-  tabsize=2,% sizes of tabs
-  showstringspaces=false,% do not replace spaces in strings by a certain character
-  captionpos=b,% positioning of the caption below
-  breaklines=true,% automatic line breaking
-  escapeinside={(*}{*)},% escaping to LaTeX
-  fancyvrb=true,% verbatim code is typset by listings
-  extendedchars=false,% prohibit extended chars (chars of codes 128--255)
-  alsoletter={.<-},% becomes a letter
-  alsoother={$},% becomes other
-  otherkeywords={!=, ~, $, \&, \%/\%, \%*\%, \%\%, <-, <<-, /},% other keywords
-  deletekeywords={c}% remove keywords 
-}
-\lstset{style=mystyle}
-
-% Adds numbered lines
-\usepackage{lineno}
-\linenumbers
-
-% Rename 'Abstract' to 'Summary 
-\usepackage[english]{babel}
-\addto{\captionsenglish}{\renewcommand{\abstractname}{Summary}}
-
-\usetikzlibrary{calc}
-\usetikzlibrary{arrows.meta}
-
-\begin{document}
-
-\maketitle
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Figures at the end
+% Figure 1
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \caption{
-    Workflow using GUI tools. From an alignment (1) and BEAUti (2), 
-    a BEAST2 configuration file (3) is created. BEAST2 (4) uses that file
-    to infer a posterior, storing it in multiple files (5). These results
-    are visualized using DensiTree (6) and Tracer (7). babette allows
-    for the same workflow, all from an R function call.
+    Workflow using GUI tools. 
+    From an alignment (1) and BEAUti (2), 
+    a BEAST2 configuration file (3) is created. 
+    BEAST2 (4) uses that file to infer a posterior, 
+    storing it in multiple files (5). These results are visualized using
+    DensiTree (6) and Tracer (7). \texttt{babette} allows for the same workflow, 
+    all from an R function call
   }
-  \label{fig:workflow}
+  \label{fig:babette_workflow}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}

### 2019-05-02 figures/figures.tex
Convert to high resolution
All images have a DPI of at least 300 (in this case: 600)
Figures are in 'figures.tex' (standalone) and 'figure_1.tex' (only the figure)

@@
-\documentclass[a3paper]{article}
+\documentclass[]{article}
 
-% 300 DPI
+% Bad idea
+%\usepackage{fullpage}
+
+%\documentclass[a0paper]{article}
+% Must be at least 300 DPI
+
+% No page numbering
+\pagenumbering{gobble}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Figures at the end
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h]
-  \centering
-  \resizebox {0.8\columnwidth} {!} {
-    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=6cm, semithick]   
-    \tikzstyle{every state}=[]
-    \node[state] (A) [rectangle] {
-      \includegraphics[width=0.2\textwidth]{alignment.png}
-    };   
-    \node[state] (AL) [above left=-0.25cm and -0.25cm of A, fill=white] {
-      1
-    };   
-    \node[state] (B) [right of = A, rectangle] {
-      \includegraphics[height=0.15\textheight]{beauti_site_model.png}
-    };   
-    \node[state] (BL) [above left=-0.25cm and -0.25cm of B, fill=white] {
-      2
-    };   
-    \node[state] (E) [below of=A, rectangle] {
-      \includegraphics[height=0.1\textheight]{file2.png}
-    };   
-    \node[state] (EL) [above left=-0.25cm and -0.25cm of E, fill=white] {
-      3
-    };   
-    \node[state] (C) [right of = E, rectangle] {
-      \includegraphics[width=0.3\textwidth]{beast_logo.png}
-    };   
-    \node[state] (CL) [above left=-0.25cm and -0.25cm of C, fill=white] {
-      4
-    };   
-    \node[state] (F) [rectangle, below of=E] {
-      \includegraphics[height=0.1\textheight]{file.png}
-    };
-    \node[state] (FL) [above left=-0.25cm and -0.25cm of F, fill=white] {
-      5
-    };   
-    \node[state] (H) [rectangle, below of=F] {
-      \includegraphics[width=0.3\textwidth]{DensiTreeExample2.jpg}
-    };
-    \node[state] (HL) [above left=-0.25cm and -0.25cm of H, fill=white] {
-      6
-    };   
-    \node[state] (I) [rectangle, right of=H] {
-      \includegraphics[width=0.6\textwidth]{tracer_example_output.png}
-    };
-    \node[state] (IL) [above left=-0.25cm and -0.25cm of I, fill=white] {
-      7
-    };   
-    \path 
-      (A) edge [anchor = west] node {} (E)
-      (E) edge [anchor = west] node {} (F)
-      (F) edge [anchor = west] node {} (H)
-      (F) edge [anchor = west] node {} (I)
-    ; 
-    \path [-o,draw] (B) -- ($ (A) !.5! (E) $);
-    \path [-o,draw] (C) -- ($ (E) !.5! (F) $);
-    \end{tikzpicture}
-  }
-  \caption{
-    Workflow using GUI tools. From an alignment (1) and BEAUti (2), 
-    a BEAST2 configuration file (3) is created. BEAST2 (4) uses that file
-    to infer a posterior, storing it in multiple files (5). These results
-    are visualized using DensiTree (6) and Tracer (7). babette allows
-    for the same workflow, all from an R function call.
-  }
-  \label{fig:workflow}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\include{figure_1}
 

### 2019-05-02 article/article.tex
EOD
Remove nonsense '\grid' at end
Put figures and article in one folder
Seperate content from text

--- 2018-05-14 article.tex
@@
 
+% TikZ drawing
+\usetikzlibrary{arrows,automata}
+\usetikzlibrary{calc}
+\usetikzlibrary{arrows.meta}
+
 % Adds numbered lines
@@
 
-\hyphenation{grafi-sche}
-\hyphenation{mo-ge-lijk-he-den}
-
 \begin{document}
 
-\maketitle
+\include{content}
 
-\begin{abstract}
-
-  \textbf{1. }
-    In the field of phylogenetics, 
-    BEAST2 is one of the most widely used software tools. 
-    It comes with the graphical user interfaces BEAUti 2, DensiTree and Tracer,
-    to create BEAST2 configuration files and to interpret BEAST2's output files. 
-    However, when many different alignments or model 
-    setups are required, a workflow of graphical user interfaces is cumbersome. \\
-  \textbf{2. }
-    Here, we present a free, libre and open-source package, \verb;babette;: 
-    'BEAUti 2, BEAST2 and Tracer for R', for the R programming language. 
-    \verb;babette; creates BEAST2 input files, runs BEAST2 and parses its results, 
-    all from an R function call. \\
-  \textbf{3. }
-    We describe \verb;babette;'s usage and the novel functionality it provides
-    compared to the original tools and we give some examples. \\
-  \textbf{4. }
-    As \verb;babette; is designed to be of high quality and extendable, 
-    we conclude by describing the further development of the package. \\
-\end{abstract}
-
-\begin{abstract}
-  \textbf{1. }
-    In de fylogenetica is BEAST2 een van de meest gebruikte hulpprogramma's. 
-    Het is gebundeld met de grafische gebruiksinterface BEAUti 2, DensiTree en Tracer, 
-    om BEAST2-configuratiebestanden te maken en om BEAST2-outputbestanden te interpreteren. 
-    Echter, als veel verschillende aligneringen of modelopzetten nodig zijn, 
-    is een werkvolgorde van meerdere grafische gebruiksinterfaces onhandig. \\
-  \textbf{2. }
-    Hier presenteren we een gratis, vrij en open-source package, \verb;babette;: 
-    'BEAUti 2, BEAST2 en Tracer voor R', voor de programmeertaal R. 
-    \verb;babette; schrijft BEAST2-configuratiebestanden, start BEAST2 and verwerkt de resultaten, 
-    alles met een enkele R functie-aanroep. \\
-  \textbf{3. }
-    We beschrijven hoe \verb;babette; te gebruiken is 
-    en de nieuwe mogelijkheden die het biedt vergeleken met de originele programma's, 
-    aan de hand van enkele voorbeelden. \\
-  \textbf{4. }
-    Omdat \verb;babette; ontworpen is voor uitbreidbaarheid en hoge kwaliteit, 
-    sluiten we af met het beschrijven van de verdere ontwikkeling van dit package. \\
-\end{abstract}
-
-{\bf Keywords:} computational biology, evolution, phylogenetics, BEAST2, R
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Phylogenies are commonly used to explore evolutionary hypotheses.
-Not only can phylogenies show us how species (or other
-evolutionary units) are related to each other, 
-but we can also estimate relevant parameters such as extinction and 
-speciation rates from them.
-There are many phylogenetics tools available to obtain an estimate 
-of the phylogeny of a given set of species. 
-BEAST2 (\cite{bouckaert2014beast}) is one of the most widely used ones.
-It uses a Bayesian statistical framework to estimate 
-the joint posterior distribution of phylogenies and model parameters, 
-from one or more DNA, RNA or amino acid alignments (see figure 1 
-for an overview of the workflow).
-
-BEAST2 has a graphical and a command-line interface, 
-that both need a configuration file containing 
-alignments and model parameters.
-BEAST2 is bundled with BEAUti 2 (\cite{drummond2012bayesian}) ('BEAUti' from now on), 
-a desktop application to create a BEAST2 configuration file.
-BEAUti has a user-friendly graphical user interface, with helpful
-default settings.
-As such, BEAUti is an attractive alternative 
-to manual and error-prone editing of BEAST2 configuration files.
-
-However, BEAUti cannot be called from a command-line script.
-This implies that when the user 
-wants to explore the consequences of various settings, this must be done manually.
-This is the managable workflow when using a few alignments and doing a superficial 
-analysis of sensitivity of the reconstructed tree to model settings. 
-For exploring many trees (for instance from simulations), 
-when doing when doing a sliding-window analysis on a genomic alignment, 
-or for a more thorough sensitivity analysis, one would like to loop through 
-multiple (simulated or shortened) alignments, nucleotide substitution models, 
-clock models and tree priors. 
-One such tool to replace BEAUti is \verb;BEASTmasteR; (\cite{beastmaster}),
-which focuses on morphological traits and tip-dating, but also 
-supports DNA data. \verb;BEASTmasteR;, however, requires hundreds of
-lines of R code to setup the BEAST2 model configuration 
-and a Microsoft Excel file to specify alignment files.
-
-BEAST2 is also associated with Tracer (\cite{tracer}) and 
-DensiTree (\cite{DensiTree}). Both are desktop applications 
-to analyze the output of BEAST2, each with a user-friendly graphical user interface. 
-Tracer's purpose is to analyze the parameter estimates generated
-from a (BEAST1 and) BEAST2 run. It shows, among
-others, the effective sample size (ESS) and time series ('the trace', 
-hence the name) of each variable in the MCMC run. Both ESS and trace
-are needed to assess the strength of the inference. 
-DensiTree visualizes the phylogenies of a BEAST2 posterior, with
-many options to improve the simultaneous display of many phylogenies.
-
-However, for exploring the output of many BEAST2 runs, one would like a
-script to collect all parameters' ESSes, parameter traces and posterior
-phylogenies. There is no single package that offers a complete solution,
-but examples of R packages that offer a partial solution are rBEAST
-(\cite{rBEAST_ratmann}) and RBeast (\cite{RBeast_faria}). RBeast provides some
-plotting options and parsing of BEAST2 output files, but the plotting
-functions are too specific for general use. rBEAST was developed to test a 
-particular biological hypothesis (\cite{ratmann2016}), 
-and hence was not designed for general use.
-
-Here, we present \verb;babette;:
-’BEAUti 2, BEAST2 and Tracer for R’, 
-which creates BEAST2 (v.2.4.7) configuration files,
-runs BEAST2, and analyzes its results,
-all from an R function call. This
-will save time, tedious mouse clicking and 
-reduces the chances of errors in such repetitive actions.
-The interface of \verb;babette; mimics the tools it
-is based on. This
-familiarity helps both beginner and experienced BEAST2 users 
-to make the step from those tools to \verb;babette;.
-\verb;babette; enables the creation of a single-script 
-pipeline from sequence alignments to posterior analysis in R.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Description}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\verb;babette; is written in the R programming language (\cite{R})
-and enables the full BEAST2 workflow from a single R function call,
-in a similar way to what subsequent usage of BEAUti, DensiTree and Tracer would produce.
-\verb;babette;'s main function is \verb;bbt_run;, which
-configures BEAST2, runs it and parses its output. 
-\verb;bbt_run; needs at least the name of a 
-FASTA file containing a DNA alignment. 
-The default settings for the other arguments of \verb;bbt_run; 
-are identical to BEAUti's and BEAST2's default settings.
-Per alignment, a site model, clock model and tree prior can be chosen.
-Multiple alignments can be used, each with its own (unlinked) site model, 
-clock model and tree prior.
-
-\verb;babette; currently has 108 exported functions to set up  
-a BEAST2 configuration file. 
-\verb;babette; can currently handle the majority of BEAUti use cases.
-Because of BEAUti's high number of plugins, 
-\verb;babette; uses a software architecture that is designed to be extended.
-Furthermore, \verb;babette; has 13 exported functions to run and help run BEAST2.
-One function is used to run BEAST2, another
-one installs BEAST2 to a default location.
-Finally, \verb;babette; has 21 exported function to parse the BEAST2 output
-files and analyze the created posterior. \verb;babette; gives the
-same ESSes and summary statistics as Tracer. The data is formatted
-such that it can easily be visualized using \verb;ggplot2; (for a trace,
-similar to Tracer) or \verb;phangorn; (\cite{phangorn}) (for 
-the phylogenies in a posterior, similar to DensiTree).
-
-Currently, \verb;babette; does not contain all functionality 
-in BEAUti, BEAST2 and their many plug-ins, 
-because these tools themselves also change in time.
-\verb;babette; currently works only on DNA data,
-because this is the most common use case. 
-Nevertheless, \verb;babette; provides the majority of default tree priors and supports the most important command-line arguments of BEAST2, provides
-the core Tracer analysis options, and has the most basic subset of 
-plotting options of DensiTree. Up till now, the \verb;babette; features 
-implemented are those requested by users. Further extension of \verb;babette; 
-will be based on future user requests.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Usage}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\verb;babette; can be installed easily from CRAN:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-install.packages("babette")
-\end{lstlisting}
-For the most up-to-date version, 
-one can download and install the package from \verb;babette;'s GitHub repository:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-devtools::install_github("richelbilderbeek/babette")
-\end{lstlisting}
-To start using \verb;babette;, load its functions in the global namespace first:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-library(babette)
-\end{lstlisting}
-Because babette calls BEAST2, BEAST2 must be installed. This can be done from R, using:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-install_beast2()
-\end{lstlisting}
-This will install BEAST2 to the default user data folder, but a different path can be specified as well.
-BEAUti, and likewise \verb;babette;, needs at least a FASTA filename
-to produce a BEAST2 configuration file. 
-In BEAUti, this is achieved by loading a FASTA file, 
-then saving an output file using a common
-save file dialog. After this, BEAST2 needs to be applied to
-the created configuration file. It creates multiple files
-storing the posterior. These output
-files must be parsed by either Tracer or DensiTree.
-In \verb;babette;, all this is achieved by:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- bbt_run(fasta_filenames = "anthus_aco.fas")
-\end{lstlisting}
-This code will create a (temporary) BEAST2 configuration file,
-from the FASTA file with name \verb;anthus_aco.fas; (which
-is supplied with the package, from \cite{VanEls2018}), 
-using the same default settings as BEAUti, which are, 
-among others, a Jukes-Cantor site model, a strict clock, and a Yule birth tree prior.
-\verb;babette; will then execute BEAST2 using that file, and
-parses the output. The returned data structure, named \verb;out;, 
-is a list of parameter estimates (called \verb;estimates;), posterior 
-phylogenies (called \verb;anthus_aco_trees;, named after
-the alignment's name) and MCMC operator performance (\verb;operators;).
-An example of using a different site model, clock model 
-and tree prior is:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- bbt_run(
-  fasta_filenames = "anthus_aco.fas",
-  site_models = create_hky_site_model(),
-  clock_models = create_rln_clock_model(),
-  tree_priors = create_bd_tree_prior()
-)
-\end{lstlisting}
-This code uses an HKY site model, a relaxed log-normal clock model and a 
-birth-death tree prior, each with their default settings in BEAUti.
-Table \ref{tab:functions} shows an overview of all functions to 
-create site models, clock models and tree priors.
-Note that the arguments' names \verb;site_models;, \verb;clock_models; 
-and \verb;tree_priors; are plural, as each of these
-can be (a list of) one or more elements. Each of these arguments must 
-have the same number of elements, so that each alignment has its
-own site model, clock model and tree prior. 
-An example of two alignments, each with its own site model, is:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- bbt_run(
-  fasta_filenames = c(
-    "anthus_aco.fas", 
-    "anthus_nd2.fas"
-  ),
-  site_models = list(
-    create_tn93_site_model(), 
-    create_gtr_site_model()
-  )
-)
-\end{lstlisting}
-\verb;babette; also uses the same default prior distributions as BEAUti 
-for each of the site models, clock models and tree priors. 
-For example, by default, a Yule tree prior assumes that the birth rate 
-follows a uniform distribution, 
-from minus infinity to plus infinity. 
-One may prefer a different ddistribution instead. 
-Here is an example how to specify an exponential distribution for
-the birth rate in a Yule tree prior in \verb;babette;:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- bbt_run(
-  fasta_filenames = "anthus_aco.fas",
-  tree_priors = create_yule_tree_prior(
-    birth_rate_distr = create_exp_distr()    
-  )
-)
-\end{lstlisting}
-In this same example, one may specify
-the initial shape parameters of the exponential distribution.
-In BEAST2's implementation, an exponential distribution 
-has one shape parameter: its mean, which can be set to any
-value with \verb;BEAUti;. To set the 
-mean value of the exponential distribution to a 
-fixed (non-estimated) value, do:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- bbt_run(
-  fasta_filenames = "anthus_aco.fas",
-  tree_priors = create_yule_tree_prior(
-    birth_rate_distr = create_exp_distr(
-      mean = create_mean_param(
-        value = 1.0, 
-        estimate = FALSE
-      )
-    )    
-  )
-)
-\end{lstlisting}
-\verb;babette; also supports node dating. Like BEAUti, one
-can specify Most Recent Common Ancestor ('MRCA') priors.
-An MRCA prior allows to specify taxa having a common ancestor,
-including a distribution for the date of that ancestor.
-With \verb;babette;, this is achieved as follows:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-out <- bbt_run(
-  fasta_filenames = "anthus_aco.fas",
-  mrca_priors = create_mrca_prior(
-    taxa_names = sample(get_taxa_names("anthus_aco.fas"), size = 2),
-    alignment_id = get_alignment_id("anthus_aco.fas"),
-    is_monophyletic = TRUE,
-    mrca_distr = create_normal_distr(
-      mean = create_mean_param(value = 15.0, estimate = FALSE),
-      sigma = create_sigma_param(value = 0.025, estimate = FALSE)
-    )
-  )
-)
-\end{lstlisting}
-Instead of dating the ancestor of two random taxa, any subset of taxa can be selected,
-and multiple sets are allowed.
-\verb;babette; allows for the same core functionality as Tracer to show the values of the parameter estimates sampled
-in the BEAST2 run. This is called the "trace" (hence the name).
-The start of the trace, called the "burn-in", is usually discarded, as an MCMC 
-algorithm (such as used by BEAST2) first has to converge to
-its equilibrium and hence the parameter estimates are not 
-representative. By default, Tracer discards the first 10\% of all 
-the parameter estimates. 
-To remove a 20\% burn-in from all parameter estimates 
-in \verb;babette;, the following code can be used:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-traces <- remove_burn_ins(
-  traces = out$estimates, 
-  burn_in_fraction = 0.2
-)
-\end{lstlisting}
-Tracer shows the ESSes of each posterior's variables.
-These ESSes are important to determine the strength of the
-inference. As a rule of thumb, an ESS of 200 is acceptable 
-for any parameter estimate.
-To calculate the effective sample sizes (of all estimated variables) in \verb;babette;:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-esses <- calc_esses(
-  traces = traces, 
-  sample_interval = 1000
-)
-\end{lstlisting}
-Tracer displays multiple summary statistics for each
-estimated variable: the mean and its standard error, standard deviation,
-variance, median, mode, geometric mean, 95\% highest posterior density interval, 
-auto-correlation time and effective sample size. It displays these statistics per
-variable. In \verb;babette;, these summary statistics are collected for
-all estimated parameters at once:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-sum_stats <- calc_summary_stats(
-  traces = traces, 
-  sample_interval = 1000
-)
-\end{lstlisting}
-\verb;babette; allows for the same functionality as DensiTree.
-DensiTree displays the phylogenies in a posterior at the same
-time scale, drawn one over one another, allowing to see the uncertainty in
-topology and branch lengths. 
-The posterior phylogenies are stored as \verb;anthus_aco_trees; in the object \verb;out;,
-and can be plotted as follows:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-plot_densitree(phylos = out$anthus_aco_trees)
-\end{lstlisting}
-Instead of running the full pipeline, 
-\verb;babette; also allows to only create a BEAST2 configuration file.
-To create a BEAST2 configuration file, with all settings to default, use:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-create_beast2_input_file(
-  input_filenames = babette::get_babette_path("anthus_aco.fas"),
-  output_filename = "beast2.xml"
-)
-\end{lstlisting}
-This file can then be loaded and edited by BEAUti, 
-run by BEAST2, or run by \verb;babette;:
-
-\begin{lstlisting}[language=R, floatplacement=H]
-run_beast2(
-  input_filename = "beast2.xml",
-  output_log_filename = "run.log",
-  output_trees_filenames = "posterior.trees",
-  output_state_filename = "final.xml.state"
-)
-\end{lstlisting}
-\verb;run_beast2; is a function that only runs BEAST2, 
-and does not parse the output files (unlike \verb;bbt_run;). 
-In the example above, 
-we specify the names of the desired BEAST2 
-output files explicitly, and these will be created in the
-R working directory, after which they can be inspected 
-with other tools, or used to continue a BEAST2 run.
-When the names of these files are not specified, 
-both \verb;bbt_run; and \verb;run_beast2;
-put these files in the default temporary folder (as
-obtained from \verb;temp.dir();) to keep
-the working directory clean of intermediate files.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{babette resources}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\verb;babette; is free, libre and open source software available at 
-\url{http://github.com/richelbilderbeek/babette}
-and is licensed under the GNU General Public License v3.0.
-\verb;babette; uses the Travis CI (\url{https://travis-ci.org})
-continuous integration service, which is known to significantly 
-increase the number of bugs exposed (\cite{vasilescu2015}) and increases
-the speed at which new features are added (\cite{vasilescu2015}).
-\verb;babette; has a 100\% code coverage, which correlates with 
-code quality (\cite{horgan1994,del1995correlation}). 
-\verb;babette; follows Hadley Wickham's style guide (\cite{style_guide}), 
-which improves software quality (\cite{fang2001}).
-\verb;babette; depends on multiple packages, which are 
-\verb;ape; (\cite{APE}), 
-\verb;beautier; (\cite{beautier}),
-\verb;beastier; (\cite{beastier}),
-\verb;devtools; (\cite{devtools}),
-\verb;geiger; (\cite{GEIGER}),
-\verb;ggplot2; (\cite{ggplot2}),
-\verb;knitr; (\cite{knitr}),
-\verb;phangorn; (\cite{phangorn}),
-\verb;rmarkdown; (\cite{rmarkdown}),
-\verb;seqinr; (\cite{seqinr}),
-\verb;stringr; (\cite{stringr}),
-\verb;testit; (\cite{testit}) and 
-\verb;tracerer; (\cite{tracerer}).
-We tested \verb;babette; to give a clean 
-error message for incorrect input, by
-calling \verb;babette; one million times
-with random or random sensible inputs, 
-using a high performance computer cluster. 
-The test scripts are supplied with \verb;babette;.
-
-\verb;babette;'s development takes place on GitHub,
-\url{https://github.com/richelbilderbeek/babette}, 
-which accommodates collaboration (\cite{perez2016ten}) 
-and improves transparency (\cite{gorgolewski2016practical}).
-\verb;babette;'s GitHub facilitates feature requests and 
-has guidelines how to do so.
-
-\verb;babette;'s documentation is extensive. All functions are documented
-in the package's internal documentation. For quick use, 
-each exported function shows a minimal example. 
-For easy exploration, each exported function's documentation links to related functions.
-Additionally, \verb;babette; has a vignette that demonstrates extensively how
-to use it. There is documentation on the GitHub to get started, 
-with a dozen examples of BEAUti screenshots with equivalent \verb;babette; code.
-Finally, \verb;babette; has tutorial videos that can 
-be downloaded or viewed on YouTube, \url{https://goo.gl/weKaaU}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Citation of babette}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Scientists using \verb;babette; in a published paper can cite this
-article, and/or cite the \verb;babette; package 
-directly. To obtain this citation from within an R script, use:
-
-\begin{lstlisting}[language=R]
-> citation("babette")
-\end{lstlisting}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Acknowledgements}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Thanks to Yacine Ben Chehida and Paul van Els for supplying their 
-BEAST2 use cases. Thanks again to Paul van Els for sharing his FASTA files 
-for use by this package. Thanks to Leonel Herrera-Alsina, Raphael Scherrer 
-and Giovanni Laudanno for their comments on this package and article.
-Thanks to Huw Ogilvie and one anonymous reviewer for reviewing this article.
-Thanks to rOpenSci, and especially Noam Ross and Guangchuang Yu for reviewing the package's source code.
-We would like to thank the Center for Information Technology of the University 
-of Groningen for their support and for providing access to the Peregrine 
-high performance computing cluster. We thank the Netherlands 
-Organization for Scientific Research (NWO) for financial support 
-through a VICI grant awarded to RSE.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Authors' contributions}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-RJCB and RSE conceived the idea for the package. RJCB created and tested the package, and wrote the first draft of the manuscript. RSE contributed substantially to revisions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Bibliography
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% MEE style
-\bibliographystyle{mee}
-\bibliography{article}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h]
-\centering
-\begin{tabular}{ | l | l | }
-\hline
-\textbf{Name} & \textbf{Description} \\
-\hline
-\verb;bbt_run; & Run BEAST2 \\
-\hline
-\verb;create_gtr_site_model; & Create a GTR site model \\
-\verb;create_hky_site_model; & Create an HKY site model \\
-\verb;create_jc69_site_model; & Create a Jukes-Cantor site model \\
-\verb;create_tn93_site_model; & Create a TN93 site model \\
-\hline
-\verb;create_rln_clock_model; & Create a relaxed log-normal clock model \\
-\verb;create_strict_clock_model; & Create a strict clock model \\
-\hline
-\verb;create_bd_tree_prior; & Create a birth-death tree prior \\
-\verb;create_cbs_tree_prior; & Create a coalescent Bayesian skyline tree prior \\
-\verb;create_ccp_tree_prior; & Create a coalescent constant-population tree prior \\
-\verb;create_cep_tree_prior; & Create a coalescent exponential-population tree prior \\
-\verb;create_yule_tree_prior; & Create a Yule tree prior \\
-\hline
-\verb;create_beta_distr; & Create a beta distribution \\
-\verb;create_exp_distr; & Create an exponential distribution \\
-\verb;create_gamma_distr; & Create a gamma distribution \\
-\verb;create_inv_gamma_distr; & Create an inverse gamma distribution \\
-\verb;create_laplace_distr; & Create a Laplace distribution \\
-\verb;create_log_normal_distr; & Create a log-normal distribution \\
-\verb;create_normal_distr; & Create a normal distribution \\
-\verb;create_one_div_x_distr; & Create a 1/X distribution \\
-\verb;create_poisson_distr; & Create a Poisson distribution \\
-\verb;create_uniform_distr; & Create a uniform distribution \\
-\hline
-\end{tabular}
-\caption{babette's main functions}
-\label{tab:functions}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\include{figure_1}
 
 \end{document}
-\grid
-\grid
-\grid

### 2019-05-02 article/content.tex
Seperate content from text

--- 2018-05-14 article.tex
@@
-\documentclass{article}
-
-% Bibliography
-\usepackage{natbib}
-\bibpunct{(}{)}{;}{a}{}{;}
-
-% Use 'It was found that A is B (Name 1234)' style
-\setcitestyle{authoryear,open={},close={}}
-
-% Affiliations
-\usepackage{authblk}
-\title{babette: BEAUti 2, BEAST2 and Tracer for R}
-\author[1]{Rich\`el J.C. Bilderbeek}
-\author[1]{Rampal S. Etienne}
-\affil[1]{Groningen Institute for Evolutionary Life Sciences, University of Groningen, Groningen, The Netherlands}
-
-% Use double spacing
-\usepackage{setspace}
-\doublespacing
-
-\usepackage{listings}
-\usepackage{hyperref}
-\usepackage{todonotes}
-\usepackage{verbatim}
-\usepackage{pgf}
-\usepackage{bm}
-
-% Style of listings
-% From http://r.789695.n4.nabble.com/How-to-nicely-display-R-code-with-the-LaTeX-package-listings-tp4648110.html
-\usepackage{fancyvrb} 
-\definecolor{codegreen}{rgb}{0,0.6,0}
-\definecolor{codegray}{rgb}{0.5,0.5,0.5}
-\definecolor{codepurple}{rgb}{0.58,0,0.82}
-\definecolor{backcolor}{rgb}{0.95,0.95,0.92}
-\lstdefinestyle{mystyle}{
-  language=R,% set programming language
-  basicstyle=\ttfamily\small,% basic font style
-  commentstyle=\color{gray},% comment style
-  % numbers=left,% display line numbers on the left side
-  numberstyle=\scriptsize,% use small line numbers
-  numbersep=10pt,% space between line numbers and code
-  tabsize=2,% sizes of tabs
-  showstringspaces=false,% do not replace spaces in strings by a certain character
-  captionpos=b,% positioning of the caption below
-  breaklines=true,% automatic line breaking
-  escapeinside={(*}{*)},% escaping to LaTeX
-  fancyvrb=true,% verbatim code is typset by listings
-  extendedchars=false,% prohibit extended chars (chars of codes 128--255)
-  alsoletter={.<-},% becomes a letter
-  alsoother={$},% becomes other
-  otherkeywords={!=, ~, $, \&, \%/\%, \%*\%, \%\%, <-, <<-, /},% other keywords
-  deletekeywords={c}% remove keywords 
-}
-\lstset{style=mystyle}
-
-% Adds numbered lines
-\usepackage{lineno}
-\linenumbers
-
-% Rename 'Abstract' to 'Summary 
-\usepackage[english]{babel}
-\addto{\captionsenglish}{\renewcommand{\abstractname}{Summary}}
-
-\hyphenation{grafi-sche}
-\hyphenation{mo-ge-lijk-he-den}
-
-\begin{document}
-
 \maketitle
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Data Accessibility}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+All code is archived at \url{http://github.com/richelbilderbeek/babette_article},
+with DOI \url{https://doi.org/10.5281/zenodo.1251203}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Authors' contributions}
@@
 
-RJCB and RSE conceived the idea for the package. RJCB created and tested the package, and wrote the first draft of the manuscript. RSE contributed substantially to revisions.
+RJCB and RSE conceived the idea for the package. 
+RJCB created and tested the package, and wrote the first draft of the manuscript. 
+RSE contributed substantially to revisions.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}
-\grid
-\grid
-\grid

### 2020-03-30 article/create_article.sh
Use 'babette_', allowing inclusion in thesis

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+pdflatex babette_article.tex --shell-escape
+bibtex babette_article.aux
+pdflatex babette_article.tex --shell-escape
+pdflatex babette_article.tex --shell-escape
+
+# pdfunite babette_article.pdf ../figures/figures.pdf article_full.pdf

### 2020-03-30 article/create_figures.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+# Run twice for labels
+pdflatex babette_figures.tex --shell-escape
+pdflatex babette_figures.tex --shell-escape

### 2020-03-30 article/clean.sh
Update clean script, renamed to 'clean.sh'

@@ -1,0 +1,15 @@
+#!/bin/bash
+
+# All except the tex, bst and bib file
+rm *.aux
+rm *.bbl
+rm *.bcf
+rm *.blg
+rm *.doc
+rm *.docx
+rm *.log
+rm *.out
+rm *.pdf
+rm *.rtf
+rm *.run.xml
+rm *.txt

### 2020-03-30 article/create_article.sh
Use 'babette_article' as main file, that is, where the content is

@@ -1,8 +1,9 @@
 #!/bin/bash
 
-pdflatex babette_article.tex --shell-escape
-bibtex babette_article.aux
-pdflatex babette_article.tex --shell-escape
-pdflatex babette_article.tex --shell-escape
+pdflatex babette_header --shell-escape
+bibtex babette_header
+pdflatex babette_header --shell-escape
+pdflatex babette_header --shell-escape
+mv babette_header.pdf babette_article.pdf
 
 # pdfunite babette_article.pdf ../figures/figures.pdf article_full.pdf

### 2020-04-17 article/view.sh
Use Makefile

@@ -1,0 +1,9 @@
+#!/bin/bash
+#
+# View the article's PDF
+#
+# Usage:
+#
+#   ./view.sh
+#
+qpdfview babette_article.pdf

### 2020-04-17 article/clean.sh
'clean.sh' is silent

@@ -1,15 +1,10 @@
 #!/bin/bash
-
+#
+# Removes intermediate files
+#
+# Usage:
+#
+#   ./clean.sh
+#
 # All except the tex, bst and bib file
-rm *.aux
-rm *.bbl
-rm *.bcf
-rm *.blg
-rm *.doc
-rm *.docx
-rm *.log
-rm *.out
-rm *.pdf
-rm *.rtf
-rm *.run.xml
-rm *.txt
+rm -f *.aux *.bbl *.bcf *.blg *.doc *.docx *.log *.out *.pdf *.rtf *.run.xml *.txt

### 2020-04-17 article/view.sh
Create 'article.pdf' again

@@ -6,4 +6,4 @@
 #
 #   ./view.sh
 #
-qpdfview babette_article.pdf
+qpdfview article.pdf

### 2020-04-17 article/count_words.sh
Count words correctly

@@ -1,0 +1,11 @@
+#!/bin/bash
+#
+# Count the words in the article
+#
+# Usage:
+#
+#   ./count_words
+#
+cat babette_article.tex | sed 's/\$/x/g' > tmp.tex
+texcount tmp.tex
+rm tmp.tex

### 2020-04-17 article/babette_article.tex
Use 'babette_', allowing inclusion in thesis
Add spellcheck

--- 2018-05-22 article/article.tex
@@
-\documentclass{article}
-
-% Bibliography
-\usepackage{natbib}
-\bibpunct{(}{)}{;}{a}{}{;}
-
-% Use 'It was found that A is B (Name 1234)' style
-\setcitestyle{authoryear,open={},close={}}
-
-% Affiliations
-\usepackage{authblk}
-\title{babette: BEAUti 2, BEAST2 and Tracer for R}
-\author[1]{Rich\`el J.C. Bilderbeek}
-\author[1]{Rampal S. Etienne}
-\affil[1]{Groningen Institute for Evolutionary Life Sciences, University of Groningen, Groningen, The Netherlands}
-
-% Use double spacing
-\usepackage{setspace}
-\doublespacing
-
-\usepackage{listings}
-\usepackage{hyperref}
-\usepackage{todonotes}
-\usepackage{verbatim}
-\usepackage{pgf}
-\usepackage{bm}
-
-% Style of listings
-% From http://r.789695.n4.nabble.com/How-to-nicely-display-R-code-with-the-LaTeX-package-listings-tp4648110.html
-\usepackage{fancyvrb} 
-\definecolor{codegreen}{rgb}{0,0.6,0}
-\definecolor{codegray}{rgb}{0.5,0.5,0.5}
-\definecolor{codepurple}{rgb}{0.58,0,0.82}
-\definecolor{backcolor}{rgb}{0.95,0.95,0.92}
-\lstdefinestyle{mystyle}{
-  language=R,% set programming language
-  basicstyle=\ttfamily\small,% basic font style
-  commentstyle=\color{gray},% comment style
-  % numbers=left,% display line numbers on the left side
-  numberstyle=\scriptsize,% use small line numbers
-  numbersep=10pt,% space between line numbers and code
-  tabsize=2,% sizes of tabs
-  showstringspaces=false,% do not replace spaces in strings by a certain character
-  captionpos=b,% positioning of the caption below
-  breaklines=true,% automatic line breaking
-  escapeinside={(*}{*)},% escaping to LaTeX
-  fancyvrb=true,% verbatim code is typset by listings
-  extendedchars=false,% prohibit extended chars (chars of codes 128--255)
-  alsoletter={.<-},% becomes a letter
-  alsoother={$},% becomes other
-  otherkeywords={!=, ~, $, \&, \%/\%, \%*\%, \%\%, <-, <<-, /},% other keywords
-  deletekeywords={c}% remove keywords 
-}
-\lstset{style=mystyle}
-
-% Adds numbered lines
-\usepackage{lineno}
-\linenumbers
-
-% Rename 'Abstract' to 'Summary 
-\usepackage[english]{babel}
-\addto{\captionsenglish}{\renewcommand{\abstractname}{Summary}}
-
-\hyphenation{grafi-sche}
-\hyphenation{mo-ge-lijk-he-den}
-
-\begin{document}
-
-\maketitle
-
 \begin{abstract}
@@
 wants to explore the consequences of various settings, this must be done manually.
-This is the managable workflow when using a few alignments and doing a superficial 
+This is the manageable workflow when using a few alignments and doing a superficial 
 analysis of sensitivity of the reconstructed tree to model settings. 
@@
 birth-death tree prior, each with their default settings in BEAUti.
-Table \ref{tab:functions} shows an overview of all functions to 
+Table \ref{tab:babette_functions} shows an overview of all functions to 
 create site models, clock models and tree priors.
@@
 from minus infinity to plus infinity. 
-One may prefer a different ddistribution instead. 
+One may prefer a different distribution instead. 
 Here is an example how to specify an exponential distribution for
@@
 % MEE style
-\bibliographystyle{mee}
-\bibliography{article}
+\bibliographystyle{babette_mee}
+\bibliography{babette_article}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \caption{babette's main functions}
-\label{tab:functions}
+\label{tab:babette_functions}
 \end{table}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}
-\grid
-\grid
-\grid

### 2020-04-17 article/clean.sh
Clean

@@ -7,4 +7,5 @@
 #   ./clean.sh
 #
 # All except the tex, bst and bib file
-rm -f *.aux *.bbl *.bcf *.blg *.doc *.docx *.log *.out *.pdf *.rtf *.run.xml *.txt
+rm -f *.aux *.bbl *.bcf *.blg *.doc *.docx *.log *.out *.pdf *.rtf *.run.xml *.txt *.bak
+

### 2020-04-17 article/spell_check.sh
Do proper spell-check

@@ -1,0 +1,21 @@
+#!/bin/bash
+#
+# Spell-check the TeX.
+#
+# Will ignore:
+#   * Text in `\verb;[here];`, as this is code
+#   * Text in listings, as this is code
+#   * Text in 'Samenvatting', as this is Dutch
+#
+# Usage:
+#
+#   ./spell_check.sh
+#
+
+# Remove '\verb;[here];'
+
+cat babette_article.tex | sed 's/\\verb;.*;//g' > tmp.tex
+
+cat tmp.tex | egrep "verb"
+#aspell -t -c babette_article.tex
+

### 2020-04-24 article/babette_article.tex
Nice URL (but still...) display

@@
 \verb;babette; is free, libre and open source software available at 
-\url{http://github.com/richelbilderbeek/babette}
+\begin{sloppypar}\url{http://github.com/richelbilderbeek/babette}\end{sloppypar}
 and is licensed under the GNU General Public License v3.0.
@@
 \verb;babette;'s development takes place on GitHub,
-\url{https://github.com/richelbilderbeek/babette}, 
+\begin{sloppypar}\url{https://github.com/richelbilderbeek/babette},\end{sloppypar}
 which accommodates collaboration (\cite{perez2016ten}) 
